---
title: "SEA: Selection coefficients analysis based on allele freuquency of K13 mutations"
output: html_document
date: "2024-04-17"
---

# This file estimates the selection coefficient using a Bayesian GLM model using
# the K13 allele frequency estimates in SEA

```{r}
library(Matrix)
library(lme4)
library(nlme)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(scales)
library(tidyverse)
library(cowplot)
library(tabulizer)
library(RColorBrewer)
library(tidyverse) # ggplot2, dplyr, tidyr, readr, purrr, tibble
library(rnaturalearth)
library(rnaturalearthdata)
library(sf) #see ubuntu issues here: https://rtask.thinkr.fr/installation-of-r-4-0-on-ubuntu-20-04-lts-and-tips-for-spatial-packages/
library(ggspatial)
library(scatterpie)
library(scales)
library (ggforce)
library (ggmap)
library(rstan)
library(gt)
## install.packages("rstan", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))
```

#Load function
```{r}
source("GLM_model_s_functions.R")
source("SEA_analysis_selection_coef.R")
source("SEA_preprocessing_selection_coef.R")
source("SEA_selection_coef_estimate.R")
```

# Load data
```{r}
fileLocManuscript_pfK7 <- "figures/"

#load data
pfk7_data_unfiltered <- read.table("data/data-derived/pfk7_allele_frequency.txt") %>% 
  filter(Locus != "other_K13") 

#set the limit of number of observations
numofobs <- 2

pfk7_data_filtered <- pfk7_data_unfiltered %>% 
  filter(!(Locus == "K13" & District == "Binh Phuoc" & year == 2005)) %>%
  group_by(Locus, District) %>%
  filter(min_year <= 2010,
         year >= min_year & year <= min_year + 4, #filter for the first five years,
         nobs > numofobs) %>%
  arrange(Locus, District, year)
```

# Bayesian GMM with slopes and intercepts
```{r}
C580Y <- GLM_model_mutant(pfk7_data_filtered, "C580Y", numofobs = 2)
c580y_stanmod <- C580Y$glmer
ranef_c580y_stanmod <- C580Y$ranef

R539T <- GLM_model_mutant(pfk7_data_filtered, "R539T", numofobs = 2)
r539t_stanmod <- R539T$glmer
ranef_r539t_stanmod <- R539T$ranef

K13 <- GLM_model_mutant(pfk7_data_filtered, "K13", numofobs = 2)
K13_stanmod <- K13$glmer
ranef_K13_stanmod <- K13$ranef
``` 

#Calculate selection coefficient
```{r}
pfk7_data_filtered <- selection_coef_estimate(pfk7_data_filtered, c580y_stanmod, r539t_stanmod, k13_stanmod)
```

# SFigure5: Plot allele frequency for all mutations
## Preprocessing
```{r}
# add other SEAn sites to show general allele frequency across SE Asia
other_districts <- pfk7_data_unfiltered %>% 
  filter(District == "Bago" | District == "Bac Lieu" | District == "Mandalay" | District == "Ninh Thuan")
  # filter(! District %in% unique(pfk7_data_filtered$District)) %>%
  # filter(!District %in% c("Champasak", "Salavan", "Sekong", "Kayin", "Rakhine", "Dak Lak", "Dak Nong", "Gia Lai", "Stueng Traeng"))
```

## Supplement Plot
```{r}
allele_freq_model_fit <- pfk7_data_filtered %>%
  ggplot(aes(year, freq, group = Locus, color = Locus)) +
  geom_point(aes(size = n/2, group = Locus, color = Locus)) +
  geom_line(data = pfk7_data_filtered %>% filter(nobs > numofobs, is.finite(lrsmed)), aes(year, predict_stan_prev, color = Locus, group = Locus), size = 1) +
  geom_ribbon(data = pfk7_data_filtered %>% filter(nobs > numofobs, is.finite(lrsmed)), aes(ymin = conf.low_prev, ymax = conf.high_prev, color = Locus, fill = Locus), alpha = 0.2,  show.legend = FALSE) +
  geom_point(data = other_districts, aes(size = n/2, x = year, y = freq, group = Locus, color = Locus)) + 
  facet_wrap(~country + District) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  scale_color_manual(
    values = c("#56B4E9", "#E69F00", "#009E73"),
    name = "Mutations",
    labels = c("580Y", "K13", "539T")
  ) +
  scale_fill_manual(values = c("#56B4E9", "#E69F00", "#009E73")) +
  ylab("Allele Freq") +
  xlab("Year") +
  #ylim(-0.01, 1.01)+
  ggpubr::theme_pubclean(base_size = 12)+
  scale_x_continuous(limits = c(2002, 2014), 
                     breaks = seq(2002, 2014, 4),
                     minor_breaks = seq(2002, 2014, 2)) +
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.position = "right",
    legend.box = "vertial"
  )
```

## Saving plots
```{r}
ggsave(
  "figures/supplement/Figure5_SEA_Prevalence/SEA_posterior_allele_freq.png",
  allele_freq_model_fit,
  width = 8,
  height = 8,
  dpi = 700
)
ggsave(
  "figures/supplement/Figure5_SEA_Prevalence/SEA_posterior_allele_freq.pdf",
  allele_freq_model_fit,
  width = 8,
  height = 8,
  dpi = 700
)
```

# Plot selection coefficient 
## Preprocessing
```{r}
selection_coef_result <- preprocessing_selection_coef(c580y_stanmod, r539t_stanmod, K13_stanmod)
rownames(selection_coef_result) <- NULL
```

## Figure S6: Plot
```{r}
selection_coef_plot <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_pointrange(data = selection_coef_result, 
                  aes(x = estimate, y = mutation, xmin = conf.low, xmax = conf.high, color = District),
                  position=position_dodge(width = 0.5), shape = selection_coef_result$s, size = selection_coef_result$sizes) +
  scale_y_discrete(labels = c("539T", "580Y", "K13")) +
  ylab("Mutation") +
  xlab("Selection Coefficient") +
  xlim(-2.5,3) +
  scale_color_manual(values=c("#4477AA",
                              "#66CCEE",
                              "#228833",
                              "#CCBB44",
                              "black",
                              "#EE7733")) +
  theme_bw() +
  theme(
    legend.title = element_blank(),
    axis.line = element_line(),
    legend.position = "right",
    plot.title = element_text(hjust = 0.5, size = 20),
    axis.text = element_text(size = 14),
    axis.title = element_text(size = 16),
    legend.text = element_text(size = 10)
  )

selection_coef_summary <- selection_coef_result %>% 
  relocate(District, mutation) %>% 
  select(!(s:sizes)) %>% 
  mutate(conf.low = round(conf.low, 3), conf.high = round(conf.high, 3), estimate = round(estimate, 3)) 
```

### Saving plots
```{r}
ggsave(
  "figures/Figure3_selection_coefficient/SEA/Figure3_SEA_selecton_coef_allelefreq.png",
  selection_coef_plot,
  width = 8,
  height = 5.5,
  dpi = 700
)
ggsave(
  "figures/Figure3_selection_coefficient/SEA/Figure3_SEA_selecton_coef_allelefreq.pdf",
  selection_coef_plot,
  width = 8,
  height = 5.5,
  dpi = 700
)
write.csv(
  selection_coef_summary,
  "figures/Figure3_selection_coefficient/SEA/SEA_selection_coef_allelefreq_summary.csv",
  row.names = F,
  quote = F
)
```

### Statistical analysis of selection coefficients
```{r}
selec_ceof_stats <- analysis_selection_coef(selection_coef_result)
write.csv(
  selec_ceof_stats,
  "figures/Figure3_selection_coefficient/SEA/SEA_selection_coef_allelefreq_stats.csv",
  row.names = F,
  quote = F
)
```
