---
title: "Kelch PfK7 Selection Coefficient Modeling - MANUSCRIPT"
output: html_document
date: "2024-04-17"
---

# This file estimates the selection coefficient using a Bayesian GLM model using
# the K13 prevalence relative to WT

```{r}
library(Matrix)
library(lme4)
library(nlme)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(scales)
library(tidyverse)
library(cowplot)
library(tabulizer)
library(RColorBrewer)
library(tidyverse) # ggplot2, dplyr, tidyr, readr, purrr, tibble
library(rnaturalearth)
library(rnaturalearthdata)
library(sf) #see ubuntu issues here: https://rtask.thinkr.fr/installation-of-r-4-0-on-ubuntu-20-04-lts-and-tips-for-spatial-packages/
library(ggspatial)
library(scatterpie)
library(scales)
library (ggforce)
library (ggmap)
library(rstan)
library(gt)
## install.packages("rstan", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))
```
#Load function
```{r}
source("~/Dropbox (Brown)/Brown/PhD/JeffBaileyLab/Kelch_Uganda_Modeling/selmar/analysis/GLM_model_s_functions.R")
```

# Load data
```{r}
fileLocManuscript_pfK7 <- "figures/"

#load data
pfk7_data <- read.table("data/data-derived/pfk7_data_WT.txt") %>% 
  filter(Locus != "other_K13") 

#set the limit of number of observations
numofobs <- 2

pfk7_data2 <- pfk7_data %>% 
  filter(!(Locus == "K13" & District == "Binh Phuoc" & year == 2005)) %>%
  group_by(Locus, District) %>%
  mutate(min_year = min(year[x>0]))

pfk7_data <- pfk7_data2 %>% 
  group_by(Locus, District) %>%
  filter(min_year <= 2010,
         year >= min_year & year <= min_year + 4, #filter for the first five years,
         nobs > numofobs) %>%
  arrange(Locus, District, year)
```

# Bayesian GMM with slopes and intercepts
```{r}
C580Y <- GLM_model_mutant(pfk7_data_prev_WT, "C580Y")
c580y_stanmod <- C580Y$glmer
ranef_c580y_stanmod <- C580Y$ranef

R539T <- GLM_model_mutant(pfk7_data_prev_WT, "R539T")
r539t_stanmod <- R539T$glmer
ranef_r539t_stanmod <- R539T$ranef

K13 <- GLM_model_mutant(pfk7_data_prev_WT, "K13")
K13_stanmod <- K13$glmer
ranef_K13_stanmod <- K13$ranef

ranef_stanmod_prev <- rbind(ranef_c580y_stanmod, ranef_r539t_stanmod, ranef_K13_stanmod)
ranef_stanmod_prev$site <- str_replace_all(rownames(ranef_stanmod_prev), "\\[|\\]", "")
ranef_stanmod_prev$site <- str_replace_all(ranef_stanmod_prev$site, "\\s*\\([^\\)]+\\)", "")
ranef_stanmod_prev$site <- str_remove(ranef_stanmod_prev$site, "b District:")
ranef_stanmod_prev$site <- str_remove(ranef_stanmod_prev$site, "1")
``` 
#Calculate selection coefficient
```{r}
pfk7_data <- selection_ceof_estimate(df, c580y_stanmod, r539t_stanmod, k13_stanmod)
```

# SFigure5: Plot prevalence relative to WT for all mutations
## Preprocessing
```{r}
prev_df2 <- pfk7_data %>% filter(nobs > numofobs)
prev_df <- rbind(prev_df2, pfk7_data %>% filter(District == "Bago" | District == "Bac Lieu" | District == "Mandalay" | District == "Ninh Thuan")) ## added these sites to show general prevalence relative to WT across SE Asia
```

## Supplement Plot
```{r}
prev_plot <- prev_df  %>%
  ggplot(aes(year, prev, group = Locus, color = Locus)) +
  geom_point(aes(size = n/2, group = Locus, color = Locus)) +
  facet_wrap(~country + District) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  geom_line(data = prev_df %>% filter(nobs > numofobs, is.finite(lrsmed)), aes(year, predict_stan_prev, color = Locus, group = Locus), size = 1) +
  geom_ribbon(data = prev_df %>% filter(nobs > numofobs, is.finite(lrsmed)), aes(ymin = conf.low_prev, ymax = conf.high_prev, color = Locus, fill = Locus), alpha = 0.2,  show.legend = FALSE) +
  scale_color_manual(
    values = c("#56B4E9", "#E69F00", "#009E73"),
    name = "Mutations",
    labels = c("580Y", "K13", "539T")
  ) +
  scale_fill_manual(values = c("#56B4E9", "#E69F00", "#009E73")) +
  ylab("Allele prev") +
  xlab("Year") +
  #ylim(-0.01, 1.01)+
  ggpubr::theme_pubclean(base_size = 12)+
  scale_x_continuous(limits = c(2002, 2014), 
                     breaks = seq(2002, 2014, 4),
                     minor_breaks = seq(2002, 2014, 2)) +
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.position = "right",
    legend.box = "vertial"
  )
```

## Saving plots
```{r}
ggsave(
  #paste0(fileLocManuscript_pfK7, "/supplement/Figure5-SEAsiaPrevalence/SEAsia_posterior_prev_WR.png"),
  paste0(fileLocManuscript_pfK7, "REVISION/SEAsia_posterior_prev_WT.png"),
  prev_plot,
  width = 8,
  height = 8,
  dpi = 700
)
# ggsave(
#   paste0(fileLocManuscript_pfK7, "/supplement/Figure5-SEAsiaPrevalence/SEAsia_posterior_prev_WR.pdf"),
#   allele_plot,
#   width = 8,
#   height = 8,
#   dpi = 700
# )
```

# Plot selection coefficient 
## Preprocessing
```{r}
# Plot the effect sizes
stan_eff <- as.data.frame(t(data.frame(c580y_stanmod$stan_summary[2, c("2.5%", "50%","97.5%")]))) %>%
mutate(method = "Bayesian (Intercept + Slope)") %>%
setNames(c("conf.low", "estimate", "conf.high", "method"))

effect_size <- stan_eff %>% mutate(mutation = "C580Y")

stan_eff <- as.data.frame(t(data.frame(r539t_stanmod$stan_summary[2, c("2.5%", "50%","97.5%")]))) %>%
mutate(method = "Bayesian (Intercept + Slope)") %>%
setNames(c("conf.low", "estimate", "conf.high", "method"))

effect_size <- rbind(effect_size, stan_eff %>% mutate(mutation = "R539T"))

stan_eff <- as.data.frame(t(data.frame(K13_stanmod$stan_summary[2, c("2.5%", "50%","97.5%")]))) %>%
mutate(method = "Bayesian (Intercept + Slope)") %>%
setNames(c("conf.low", "estimate", "conf.high", "method"))

effect_size <- rbind(effect_size, stan_eff %>% mutate(mutation = "K13"))

#confidence interval per site and mutation
stan_eff_c580y <- as.data.frame(c580y_stanmod$stan_summary[grep("year District", rownames(c580y_stanmod$stan_summary)),]) %>%
  select(c("2.5%","97.5%")) %>% 
  setNames(c("conf.low", "conf.high")) %>% 
  slice(1:(n()-1))
stan_eff_r539t <- as.data.frame(r539t_stanmod$stan_summary[grep("year District", rownames(r539t_stanmod$stan_summary)),]) %>%
  select(c("2.5%","97.5%")) %>% 
  setNames(c("conf.low", "conf.high")) %>% 
  slice(1:(n()-1))
stan_eff_K13 <- as.data.frame(K13_stanmod$stan_summary[grep("year District", rownames(K13_stanmod$stan_summary)),]) %>% 
  select(c("2.5%","97.5%")) %>% 
  setNames(c("conf.low", "conf.high")) %>%
  slice(1:(n()-1))

coef_c580y <- ranef(c580y_stanmod)$District %>% 
  mutate(District = rownames(ranef(c580y_stanmod)$District), 
         mutation = "C580Y", 
         estimate = ranef(c580y_stanmod)$District$adj_year, 
         conf.low = stan_eff_c580y$conf.low, 
         conf.high = stan_eff_c580y$conf.high) %>% 
  select(conf.low, estimate, conf.high, mutation, District) %>% 
  remove_rownames()

coef_r539t <- ranef(r539t_stanmod)$District %>% 
  mutate(District = rownames(ranef(r539t_stanmod)$District), 
         mutation = "R539T", 
         estimate = ranef(r539t_stanmod)$District$adj_year, 
         conf.low = stan_eff_r539t$conf.low, 
         conf.high = stan_eff_r539t$conf.high) %>% 
  select(conf.low, estimate, conf.high, mutation, District) %>% 
  remove_rownames()

coef_K13 <- ranef(K13_stanmod)$District %>% 
  mutate(District = rownames(ranef(K13_stanmod)$District), 
         mutation = "K13", 
         estimate = ranef(K13_stanmod)$District$adj_year, 
         conf.low = stan_eff_K13$conf.low, 
         conf.high = stan_eff_K13$conf.high) %>% 
  select(conf.low, estimate, conf.high, mutation, District) %>% 
  remove_rownames()

selec_coef <- rbind(coef_c580y, coef_r539t, coef_K13)

# plot the effect sizes for the mutation
effect_size_bay <- effect_size %>% 
  filter(method == "Bayesian (Intercept + Slope)") %>% 
  mutate(District = "Southeast Asia") %>% 
  select(conf.low, estimate, conf.high, mutation, District)

selec_coef$estimate[selec_coef$mutation == "C580Y"] <- selec_coef$estimate[selec_coef$mutation == "C580Y"] + effect_size_bay$estimate[effect_size_bay$mutation == "C580Y"]
selec_coef$estimate[selec_coef$mutation == "R539T"] <- selec_coef$estimate[selec_coef$mutation == "R539T"] + effect_size_bay$estimate[effect_size_bay$mutation == "R539T"]
selec_coef$estimate[selec_coef$mutation == "K13"] <- selec_coef$estimate[selec_coef$mutation == "K13"] + effect_size_bay$estimate[effect_size_bay$mutation == "K13"]

selec_coef$conf.low[selec_coef$mutation == "C580Y"] <- selec_coef$conf.low[selec_coef$mutation == "C580Y"] + effect_size_bay$conf.low[effect_size_bay$mutation == "C580Y"]
selec_coef$conf.low[selec_coef$mutation == "R539T"] <- selec_coef$conf.low[selec_coef$mutation == "R539T"] + effect_size_bay$conf.low[effect_size_bay$mutation == "R539T"]
selec_coef$conf.low[selec_coef$mutation == "K13"] <- selec_coef$conf.low[selec_coef$mutation == "K13"] + effect_size_bay$conf.low[effect_size_bay$mutation == "K13"]

selec_coef$conf.high[selec_coef$mutation == "C580Y"] <- selec_coef$conf.high[selec_coef$mutation == "C580Y"] + effect_size_bay$conf.high[effect_size_bay$mutation == "C580Y"]
selec_coef$conf.high[selec_coef$mutation == "R539T"] <- selec_coef$conf.high[selec_coef$mutation == "R539T"] + effect_size_bay$conf.high[effect_size_bay$mutation == "R539T"]
selec_coef$conf.high[selec_coef$mutation == "K13"] <- selec_coef$conf.high[selec_coef$mutation == "K13"] + effect_size_bay$conf.high[effect_size_bay$mutation == "K13"]

effect_size_bay$s <- 18
effect_size_bay$sizes <- 1.1
selec_coef$s <- 19
selec_coef$sizes <- 0.5

stan_eff_bay_overall <- effect_size_bay %>% 
  mutate(method = "Baysian") %>% 
  relocate(District, conf.low, estimate, conf.high, method, mutation, s, sizes)
rownames(stan_eff_bay_overall) <- NULL

# selec_coef_bay <- selec_coef %>% mutate(method = "Baysian") %>% relocate(District, conf.low, estimate, conf.high, method, mutation, s, sizes)

effect_size_bay <- rbind(selec_coef, effect_size_bay)

effect_size_bay <- effect_size_bay %>% 
  mutate(mutation = replace(mutation, mutation == "C580Y", "580Y"), 
         mutation = replace(mutation, mutation == "R539T", "539T")) 
```

## Figure3: Plot
```{r}
selection_coef_bay <- ggplot() +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_pointrange(data = effect_size_bay, 
                  aes(x = estimate, y = mutation, xmin = conf.low, xmax = conf.high, color = District),
                  position=position_dodge(width = 0.5), shape = effect_size_bay$s, size = effect_size_bay$sizes) +
  scale_y_discrete(labels = c("539T", "580Y", "K13")) +
  ylab("Mutation") +
  xlab("Selection Coefficient") +
  xlim(-2.5,4) +
  scale_color_manual(values=c("#4477AA",
                              "#66CCEE",
                              "#228833",
                              "#CCBB44",
                              "black",
                              "#EE7733")) +
  theme_bw() +
  theme(
    legend.title = element_blank(),
    axis.line = element_line(),
    legend.position = "right",
    plot.title = element_text(hjust = 0.5, size = 20),
    axis.text = element_text(size = 14),
    axis.title = element_text(size = 16),
    legend.text = element_text(size = 10)
  )

effect_size_bay2 <- effect_size_bay %>% 
  relocate(District, mutation) %>% 
  select(!(s:sizes)) %>% 
  mutate(conf.low = round(conf.low, 3), conf.high = round(conf.high, 3), estimate = round(estimate, 3)) 
```

### Saving plots
```{r}
ggsave(
  paste0(fileLocManuscript_pfK7, "/Figure3-SelectionCeof/Figure3_SEAsia_Effectsize_prev_WT.png"),
  selection_coef_bay,
  width = 8,
  height = 5.5,
  dpi = 700
)
# ggsave(
#   paste0(fileLocManuscript_pfK7, "/Figure3-SelectionCeof/Figure3_SEAsia_Effectsize.pdf"),
#   selection_coef_bay,
#   width = 8,
#   height = 5.5,
#   dpi = 700
# )
write.csv(
  effect_size_bay2,
  paste0(fileLocManuscript_pfK7, "/Figure3-SelectionCeof/SEAsia_selectioncoefficients_prev_WT.csv"),
  row.names = F,
  quote = F
)
```

### Statistical analysis of selection coefficients
```{r}
selec_ceof_stats <- data.frame(matrix(ncol = 5, nrow = 3))
min_580Y <- min(effect_size_bay %>% filter(mutation == "580Y" & District != "Southeast Asia") %>% pull(estimate))
max_580Y <- max(effect_size_bay %>% filter(mutation == "580Y" & District != "Southeast Asia") %>% pull(estimate))
selec_ceof_stats[1, ] <- cbind("580Y", 
                               round(min_580Y, 3), 
                               effect_size_bay[which(effect_size_bay$estimate == min_580Y),][5], 
                               round(max_580Y, 3), 
                               effect_size_bay[which(effect_size_bay$estimate == max_580Y),][5])

min_539T <- min(effect_size_bay %>% filter(mutation == "539T" & District != "Southeast Asia") %>% pull(estimate))
max_539T <- max(effect_size_bay %>% filter(mutation == "539T" & District != "Southeast Asia") %>% pull(estimate))
selec_ceof_stats[2, ] <- cbind("539T", 
                               round(min_539T, 3),
                               effect_size_bay[which(effect_size_bay$estimate == min_539T),][5], 
                               round(max_539T, 3), 
                               effect_size_bay[which(effect_size_bay$estimate == max_539T),][5])

min_K13 <- min(effect_size_bay %>% filter(mutation == "K13" & District != "Southeast Asia") %>% pull(estimate))
max_K13 <- max(effect_size_bay %>% filter(mutation == "K13" & District != "Southeast Asia") %>% pull(estimate))
selec_ceof_stats[3, ] <- cbind("K13", 
                               round(min_K13, 3), 
                               effect_size_bay[which(effect_size_bay$estimate == min_K13),][5], 
                               round(max_K13, 3), 
                               effect_size_bay[which(effect_size_bay$estimate == max_K13),][5])

colnames(selec_ceof_stats) <- c("Mutation", "Min", "District", "Max", "District")
write.csv(
  selec_ceof_stats,
  paste0(fileLocManuscript_pfK7, "/Figure3-SelectionCeof/SEAsia_selectioncoefficients_stats_prev_WT.csv"),
  row.names = F,
  quote = F
)
```
