---
title: "Pf7 Forecasting per district"
output: html_document
date: "2023-05-16"
---

```{r setup, include=FALSE}
library(lme4)
library(nlme)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(scales)
library(tidyverse)
library(cowplot)
library(tabulizer)
library(RColorBrewer)
library(tidyverse) # ggplot2, dplyr, tidyr, readr, purrr, tibble
library(rnaturalearth)
library(rnaturalearthdata)
library(sf) #see ubuntu issues here: https://rtask.thinkr.fr/installation-of-r-4-0-on-ubuntu-20-04-lts-and-tips-for-spatial-packages/
library(ggspatial)
library(scatterpie)
library(scales)
library (ggforce)
library (ggmap)
library(rstan)
library(gt)
## install.packages("rstan", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))

```

# Load data
```{r}
#set the limit of number of observations
numofobs <- 2
#load data
pfk7_data <- read.table("data/data-derived/NEW_pfk7_data.txt") %>% filter(Locus != "other_PfK13")
```

# Bayesian GMM with slopes and intercepts
```{r}
# Have a read through rstanarm vignettes and guides on how it works in comparison to lme4
# ---- Model for c580y -----
c580y_stanmod <- rstanarm::stan_glmer(
  lrsmed ~ adj_year + (1 + adj_year | District),
  data = pfk7_data %>% filter(Locus == "C580Y", nobs > numofobs),
  weights = wt_med, 
  adapt_delta = 0.9975
)

vals <- summary(c580y_stanmod$stanfit)$summary[, 1]
vals <- vals[grep("^b", names(vals))]
ranef_c580y_stanmod <-
  data.frame("Intercepts" = vals[seq(1, length(vals), 2)],
             "Slopes" = vals[seq(2, length(vals), 2)])
ranef_c580y_stanmod$mutation <- rep("C580Y", dim(ranef_c580y_stanmod)[1])

# ---- Model for r539t -----

r539t_stanmod <- rstanarm::stan_glmer(
  lrsmed ~ adj_year + (1 + adj_year | District),
  data = pfk7_data %>% filter(Locus == "R539T", nobs > numofobs),
  weights = wt_med, 
  adapt_delta = 0.9975
)

vals <- summary(r539t_stanmod$stanfit)$summary[, 1]
vals <- vals[grep("^b", names(vals))]
ranef_r539t_stanmod <-
  data.frame("Intercepts" = vals[seq(1, length(vals), 2)],
             "Slopes" = vals[seq(2, length(vals), 2)])
ranef_r539t_stanmod$mutation <- rep("R539T", dim(ranef_r539t_stanmod)[1])

# ---- Model for combined kelch -----

all_kelch_stanmod <- rstanarm::stan_glmer(
  lrsmed ~ adj_year + (1 + adj_year | District),
  data = pfk7_data %>% filter(Locus == "PfK13", nobs > numofobs),
  weights = wt_med, 
  adapt_delta = 0.9975
)

vals <- summary(all_kelch_stanmod$stanfit)$summary[, 1]
vals <- vals[grep("^b", names(vals))]
ranef_all_kelch_stanmod <-
  data.frame("Intercepts" = vals[seq(1, length(vals), 2)],
             "Slopes" = vals[seq(2, length(vals), 2)])
ranef_all_kelch_stanmod$mutation <- rep("PfK13", dim(ranef_all_kelch_stanmod)[1])

ranef_stanmod <-
  rbind(ranef_c580y_stanmod,
        ranef_all_kelch_stanmod,
        ranef_r539t_stanmod)
ranef_stanmod$site <- str_replace_all(rownames(ranef_stanmod), "\\[|\\]", "")
ranef_stanmod$site <- str_replace_all(ranef_stanmod$site, "\\s*\\([^\\)]+\\)", "")
ranef_stanmod$site <- str_remove(ranef_stanmod$site, "b District:")
ranef_stanmod$site <- str_remove(ranef_stanmod$site, "1")
``` 
## Posterior of the model
```{r}
#  get model predictions for plotting
pfk7_data$predict_stan <- NA

pfk7_data$predict_stan[is.finite(pfk7_data$lrsmed) & pfk7_data$Locus == "C580Y" & pfk7_data$nobs > numofobs] <-  rstanarm::posterior_predict(c580y_stanmod, type = "response") %>% colMeans
pfk7_data$predict_stan[is.finite(pfk7_data$lrsmed) & pfk7_data$Locus == "R539T" & pfk7_data$nobs > numofobs] <-  rstanarm::posterior_predict(r539t_stanmod, type = "response") %>% colMeans
pfk7_data$predict_stan[is.finite(pfk7_data$lrsmed) & pfk7_data$Locus == "PfK13" & pfk7_data$nobs > numofobs] <-  rstanarm::posterior_predict(all_kelch_stanmod, type = "response") %>% colMeans
```

## Confidence interval of and posterior of posterior for each mutation
```{r}
#  get model predictions for plotting
pfk7_data$conf.low <- NA
pfk7_data$conf.high <- NA

c580y_conf <- rstanarm::posterior_predict(c580y_stanmod, type = "response") %>% apply(2, quantile, prob = (c(0.025, 0.975)))
r539t_conf <- rstanarm::posterior_predict(r539t_stanmod, type = "response") %>% apply(2, quantile, prob = (c(0.025, 0.975)))
all_kelch_conf <- rstanarm::posterior_predict(all_kelch_stanmod, type = "response") %>% apply(2, quantile, prob = (c(0.025, 0.975)))

# here just add predictions  for the c469Y rows
pfk7_data$conf.low[is.finite(pfk7_data$lrsmed) & pfk7_data$Locus == "C580Y" & pfk7_data$nobs > numofobs] <- c580y_conf[1,]
pfk7_data$conf.low[is.finite(pfk7_data$lrsmed) & pfk7_data$Locus == "R539T" & pfk7_data$nobs > numofobs] <- r539t_conf[1,]
pfk7_data$conf.low[is.finite(pfk7_data$lrsmed) & pfk7_data$Locus == "PfK13" & pfk7_data$nobs > numofobs] <- all_kelch_conf[1,]

pfk7_data$conf.high[is.finite(pfk7_data$lrsmed) & pfk7_data$Locus == "C580Y" & pfk7_data$nobs > numofobs] <- c580y_conf[2,]
pfk7_data$conf.high[is.finite(pfk7_data$lrsmed) & pfk7_data$Locus == "R539T" & pfk7_data$nobs > numofobs] <- r539t_conf[2,]
pfk7_data$conf.high[is.finite(pfk7_data$lrsmed) & pfk7_data$Locus == "PfK13" & pfk7_data$nobs > numofobs] <- all_kelch_conf[2,]
```

## Prevalence scale
```{r}
# Plot the predictions in each site with only Bayesian
#convert to prevalence scale
pfk7_data$predict_stan_prev <- NA

pfk7_data$predict_stan_prev <- exp(pfk7_data$predict_stan)*100/(1+exp(pfk7_data$predict_stan))
pfk7_data$conf.high_prev <- exp(pfk7_data$conf.high)*100/(1+exp(pfk7_data$conf.high))
pfk7_data$conf.low_prev <- exp(pfk7_data$conf.low)*100/(1+exp(pfk7_data$conf.low))
```

# Forecasting Selection 
## No filtering based on the first 2, 3, and 4 years 
```{r}
pred_year <- c(2, 3, 4)

for (i in pred_year) {
  #------ Model prediction for C580Y ------
  c580y_pred <- rstanarm::stan_glmer(
    lrsmed ~ adj_year + (1 + adj_year | District),
    data = pfk7_data %>% filter(
      Locus == "C580Y",
      nobs > numofobs,
      year >= min_year & year <= min_year + i,
      adj_year >= 0
    ),
    weights = wt_med,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs > numofobs, is.finite(pfk7_data$lrsmed)) %>% 
    mutate(Locus = "C580Y") %>%
    group_by(District, Locus) %>%
    complete(year = seq(min(min_year) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, District, country, min_year, Locus) %>%
    mutate(min_year = replace(min_year, is.na(min_year), 0)) %>%
    ungroup
  
  new_data <- new_data %>%
    group_by(District, Locus) %>%
    mutate(min_year = max(min_year),
      adj_year = year - min_year,
      country = unique(na.omit(country))) %>%
    arrange(Locus, country, District, year) %>%
    ungroup %>%
    group_by(Locus, District, year) %>%
    distinct(year, .keep_all = TRUE) %>%
    ungroup
  
  predictions <-
    rstanarm::posterior_predict(c580y_pred, type = "response", newdata = new_data) %>% colMeans
  new_data <- new_data %>% 
    mutate(predict = predictions) 
  df_predict <- new_data
  
  #------ Model prediction for R539T ------
  
  r539t_pred <- rstanarm::stan_glmer(
    lrsmed ~ adj_year + (1 + adj_year | District),
    data = pfk7_data %>% filter(
      Locus == "R539T",
      nobs > numofobs,
      year >= min_year & year <= min_year + i,
      adj_year >= 0
    ),
    weights = wt_med,
    adapt_delta = 0.9975
  )
  
  #forecasting
  new_data <- pfk7_data %>%
    filter(nobs > numofobs, is.finite(pfk7_data$lrsmed)) %>%
    mutate(Locus = "R539T") %>%
    group_by(District, Locus) %>%
    complete(year = seq(min(min_year) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, District, country, min_year, Locus) %>%
    mutate(min_year = replace(min_year, is.na(min_year), 0)) %>%
    ungroup

new_data <- new_data %>%
    group_by(District, Locus) %>%
    mutate(min_year = max(min_year),
      adj_year = year - min_year,
      country = unique(na.omit(country))) %>%
    arrange(Locus, country, District, year) %>%
    ungroup %>%
    group_by(Locus, District, year) %>%
    distinct(year, .keep_all = TRUE) %>%
    ungroup
  
  predictions <-
    rstanarm::posterior_predict(r539t_pred, type = "response", newdata = new_data) %>% colMeans
  new_data <- new_data %>% 
    mutate(predict = predictions) 
  
  df_predict <- rbind(df_predict, new_data)
  
  #------ Model prediction for combined PfK13 mutations ------
  
  all_kelch_pred <- rstanarm::stan_glmer(
    lrsmed ~ adj_year + (1 + adj_year | District),
    data = pfk7_data %>% filter(
      Locus == "PfK13",
      nobs > numofobs,
      year >= min_year & year <= min_year + i,
      adj_year >= 0
    ),
    weights = wt_med,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs > numofobs, is.finite(pfk7_data$lrsmed)) %>% 
    mutate(Locus = "PfK13") %>%
    group_by(District, Locus) %>% 
    complete(year = seq(min(min_year) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, District, country, min_year, Locus) %>%
    mutate(min_year = replace(min_year, is.na(min_year), 0)) %>%
    ungroup
  
  new_data <- new_data %>%
    group_by(District, Locus) %>%
    mutate(min_year = max(min_year),
      adj_year = year - min_year,
      country = unique(na.omit(country))) %>%
    arrange(Locus, country, District, year) %>%
    ungroup %>%
    group_by(Locus, District, year) %>%
    distinct(year, .keep_all = TRUE) %>%
    ungroup
  
  predictions <-
    rstanarm::posterior_predict(all_kelch_pred, type = "response", newdata = new_data) %>% colMeans
  new_data <- new_data %>% 
    mutate(predict = predictions) %>% 
    rename(adj_year = adj_year)
  df_predict <- rbind(df_predict, new_data)
  
  df_predict <- df_predict %>% 
    group_by(District, Locus) %>% 
    mutate(min_year = replace_na(min_year, 0), min_year = max(min_year)) %>% 
    mutate(label = paste0(i, "year"),  pred_y = i) %>%
    ungroup
  
  #Assigning df_predict to variables
  var_name <- paste0("df_predict_", i, "year")
  assign(var_name, df_predict)
}

#combine forecasting predictions for all years
df_predict_allyear <- rbind(df_predict_2year, df_predict_3year, df_predict_4year)
```

### Ploting forecasting of predictions for the first 2, 3, and 4 years
```{r}
################ PLOT FOR C580Y ################
ex <- pfk7_data %>% filter(is.finite(lrsmed), nobs > numofobs, Locus == "C580Y")
ex_pt <- pfk7_data %>% filter(nobs > numofobs, Locus == "C580Y") %>%
  mutate(point_col = case_when(year >= min_year & year <= min_year + 2 ~ "#E69F00",
                               year > min_year + 2 & year <= min_year + 3 ~ "#56B4E9",
                               year > min_year + 3 & year <= min_year + 4 ~ "#0072B2",
                               year > min_year + 4 ~ "black",
                               year < min_year ~ "black")) 
df_pred <- df_predict_allyear %>% 
  filter(District %in% unique(ex$District), year >= min_year + pred_y, Locus == "C580Y")
prev_c580y_plot <- 
  ggplot() +
  geom_line(data=ex, aes(year, predict_stan_prev, color = "true"), linewidth = 1) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev*100), color = ex_pt$point_col) +
  labs(shape="Mutations") +
  theme_bw() +
  facet_wrap(~District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    labels = c("2 years", "3 years", "4 years", "true")
  ) + 
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.direction = "vertical",
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)
  ) +  labs(color = NULL)

################ PLOT FOR R539T ################
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed), nobs > numofobs, Locus == "R539T")
ex_pt <- pfk7_data %>% 
  filter(nobs > numofobs, Locus == "R539T") %>%
  mutate(point_col = case_when(year >= min_year & year <= min_year + 2 ~ "#E69F00",
                               year > min_year + 2 & year <= min_year + 3 ~ "#56B4E9",
                               year > min_year + 3 & year <= min_year + 4 ~ "#0072B2",
                               year > min_year + 4 ~ "black",
                               year < min_year ~ "black")) 
df_pred <- df_predict_allyear %>% 
  filter(District %in% unique(ex$District), year >= min_year +  pred_y, Locus == "R539T")

prev_r539t_plot <- 
  ggplot() +
  geom_line(data=ex, aes(year, predict_stan_prev, color = "true")) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label, color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev*100), color = ex_pt$point_col) +
  labs(shape="Mutations") +
  theme_bw() +
  facet_wrap(~District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    labels = c("2 years", "3 years", "4 years", "true")
  ) +
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.direction = "vertical",
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)
  ) +  labs(color = NULL)


################ PLOT FOR ALL KELCH MUTATIONS ################
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed), nobs > numofobs, Locus == "PfK13")
ex_pt <- pfk7_data %>% 
  filter(nobs > numofobs, Locus == "PfK13") %>%
  mutate(point_col = case_when(year >= min_year & year <= min_year + 2 ~ "#E69F00",
                               year > min_year + 2 & year <= min_year + 3 ~ "#56B4E9",
                               year > min_year + 3 & year <= min_year + 4 ~ "#0072B2",
                               year > min_year + 4 ~ "black",
                               year < min_year ~ "black"))  
df_pred <- df_predict_allyear %>% 
  filter(District %in% unique(ex$District), year >= min_year +  pred_y, Locus == "PfK13")  
prev_all_kelch_plot <- 
  ggplot() +
  geom_line(data=ex, aes(year, predict_stan_prev, color = "true")) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev*100), color = ex_pt$point_col) +
  labs(shape="Mutations") +
  theme_bw() +
  facet_wrap(~District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    labels = c("2 years", "3 years", "4 years", "true")
  ) +
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.direction = "vertical",
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)
  ) +  labs(color = NULL)
```

### Saving plots
```{r}
################ PLOT FOR C580Y ################
ggsave(
  "figures/predictions/SE_Asia/per_district/SEAsia_pred_C580Y_pred.png",
  prev_c580y_plot,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  "figures/predictions/SE_Asia/per_district/SEAsia_pred_C580Y_pred.pdf",
  prev_c580y_plot,
  width = 8,
  height = 5,
  dpi = 700
)

################ PLOT FOR R539T ################
ggsave(
  "figures/predictions/SE_Asia/per_district/SEAsia_pred_R539T_pred.png",
  prev_r539t_plot,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  "figures/predictions/SE_Asia/per_district/SEAsia_pred_R539T_pred.pdf",
  prev_r539t_plot,
  width = 8,
  height = 5,
  dpi = 700
)

################ PLOT FOR ALL KELCH MUTATIONS ################
ggsave(
  "figures/predictions/SE_Asia/per_district/SEAsia_pred_Pfk13_pred.png",
  prev_all_kelch_plot,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  "figures/predictions/SE_Asia/per_district/SEAsia_pred_Pfk13_pred.pdf",
  prev_all_kelch_plot,
  width = 8,
  height = 5,
  dpi = 700
)

write.table(df_predict_allyear, paste0(
    "figures/predictions/SE_Asia/per_district/SEAsia_pred_C580Y_predict_allyears.txt"))
```

## First year 50% cutoff based on the first 2, 3, and 4 years 
```{r}
pred_year <- c(2, 3, 4)
prev_cutoff <- 0.5

for (i in pred_year) {
  #------ Model prediction for C580Y ------
  data_c580y <- pfk7_data %>% 
    filter(
      Locus == "C580Y",
      nobs > numofobs,
      year >= min_year & year <= min_year + i) 
  
  selected_district <- data_c580y %>% 
    group_by(Locus, country, District) %>%
    filter(adj_year == min(adj_year),
           prev <= prev_cutoff) %>%
    ungroup %>%
    select(District)
  
  selected_district <- array(t(selected_district)) #check if the prevalence in the first year observed is less than cutoff
  
  data_c580y <- data_c580y %>% 
    filter(District %in% selected_district) #keep only the district that satisfy filtering
  
  c580y_pred <- rstanarm::stan_glmer(
    lrsmed ~ adj_year + (1 + adj_year | District),
    data = data_c580y,
    weights = wt_med,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs > numofobs, 
           is.finite(pfk7_data$lrsmed),
           District %in% selected_district,
           Locus == "C580Y") %>%
    group_by(District, Locus) %>%
    complete(year = seq(min(min_year) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, District, country, min_year, Locus) %>%
    mutate(min_year = replace(min_year, is.na(min_year), 0)) 
  
  new_data <- new_data %>%
    group_by(District, Locus) %>%
    mutate(min_year = max(min_year),
      adj_year = year - min_year,
      country = unique(na.omit(country))) %>%
    arrange(Locus, District, year) %>%
    ungroup %>%
    group_by(Locus, District, year) %>%
    distinct(year, .keep_all = TRUE) %>%
    ungroup
  
  predictions <-
    rstanarm::posterior_predict(c580y_pred, type = "response", newdata = new_data) %>% colMeans
  new_data <- new_data %>% 
    mutate(predict = predictions)
  
  df_predict <- new_data
  
  #------ Model prediction for R539T ------
  data_r539t <- pfk7_data %>% 
    filter(
      Locus == "R539T",
      nobs > numofobs, 
      year >= min_year & year <= min_year + i)

  selected_district <- data_r539t %>% 
    group_by(Locus, country, District) %>%
    filter(adj_year == min(adj_year),
           prev <= prev_cutoff) %>%
    ungroup %>%
    select(District)
  
  selected_district <- array(t(selected_district)) #check if the prevalence in the first year observed is less than cutoff
  
  data_r539t <- data_r539t %>% 
    filter(District %in% selected_district)
  
  r539t_pred <- rstanarm::stan_glmer(
    lrsmed ~ adj_year + (1 + adj_year | District),
    data = data_r539t,
    weights = wt_med,
    adapt_delta = 0.9975
  )
  
  new_data <- pfk7_data %>%
    filter(nobs > numofobs, 
           is.finite(pfk7_data$lrsmed), 
           District %in% selected_district,
           Locus == "R539T") %>%
    group_by(District, Locus) %>%
    complete(year = seq(min(min_year) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, District, country, min_year, Locus) %>%
    mutate(min_year = replace(min_year, is.na(min_year), 0))

  new_data <- new_data %>%
      group_by(District, Locus) %>%
      mutate(min_year = max(min_year),
        adj_year = year - min_year,
        country = unique(na.omit(country))) %>%
      arrange(Locus, District, year) %>%
      ungroup %>%
    group_by(Locus, District, year) %>%
    distinct(year, .keep_all = TRUE) %>%
    ungroup
  
  predictions <-
    rstanarm::posterior_predict(r539t_pred, type = "response", newdata = new_data) %>% colMeans
  new_data <- new_data %>% 
    mutate(predict = predictions)

  df_predict <- rbind(df_predict, new_data)
  
  #------ Model prediction for combined PfK13 mutations ------
  data_all_kelch <- pfk7_data %>% 
    filter(
      Locus == "PfK13",
      nobs > numofobs, 
      year >= min_year & year <= min_year + i)

  selected_district <- data_all_kelch %>% 
    group_by(Locus, country, District) %>%
    filter(adj_year == min(adj_year),
           prev <= prev_cutoff) %>%
    ungroup %>%
    select(District)
  
  selected_district <- array(t(selected_district)) #check if the prevalence in the first year observed is less than cutoff
  
  data_all_kelch <- data_all_kelch %>% 
    filter(District %in% selected_district)
  
  all_kelch_pred <- rstanarm::stan_glmer(
    lrsmed ~ adj_year + (1 + adj_year | District),
    data = data_all_kelch,
    weights = wt_med,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs > numofobs, 
           is.finite(pfk7_data$lrsmed),
           District %in% selected_district,
           Locus == "PfK13") %>%
    group_by(District, Locus) %>% 
    complete(year = seq(min(min_year) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, country, District, min_year, Locus) %>%
    mutate(min_year = replace(min_year, is.na(min_year), 0))
  
  new_data <- new_data %>%
    group_by(District, Locus) %>%
    mutate(min_year = max(min_year),
      adj_year = year - min_year,
      country = unique(na.omit(country))) %>%
    arrange(Locus, country, District, year) %>%
    ungroup %>%
    group_by(Locus, District, year) %>%
    distinct(year, .keep_all = TRUE) %>%
    ungroup
  
  predictions <-
    rstanarm::posterior_predict(all_kelch_pred, type = "response", newdata = new_data) %>% colMeans
  new_data <- new_data %>% 
    mutate(predict = predictions)
  
  df_predict <- rbind(df_predict, new_data)
  
  df_predict <- df_predict %>% 
    group_by(District, Locus) %>% 
    mutate(min_year = replace_na(min_year, 0), 
           min_year = max(min_year),
           label = paste0(i, "year"),  
           pred_y = i)
  
  #Assigning df_predict to variables
  var_name <- paste0("df_predict_cutoff_", i, "year")
  assign(var_name, df_predict)
}

#combine forecasting predictions for all years
df_predict_cutoff_allyear <- rbind(df_predict_cutoff_2year, df_predict_cutoff_3year, df_predict_cutoff_4year)
```

 ### Plotting forecasting of predictions for the first 2, 3, and 4 years with prevalence cut off
#### Point sized based on sample size
```{r}
################ PLOT FOR C580Y ################
prev_cutoff_perc <- prev_cutoff *100
df_pred <- df_predict_cutoff_allyear %>% 
  filter(year >= min_year + pred_y, Locus == "C580Y") 
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed), nobs > numofobs, District %in% unique(df_pred$District), Locus == "C580Y")
ex_pt <- pfk7_data %>% 
  filter(nobs > numofobs, District %in% unique(df_pred$District), Locus == "C580Y") %>% #, year >= min_year & year <= min_year+4
  mutate(point_col = case_when(year >= min_year & year <= min_year + 2 ~ "#E69F00",
                               year > min_year + 2 & year <= min_year + 3 ~ "#56B4E9",
                               year > min_year + 3 & year <= min_year + 4 ~ "#0072B2",
                               year > min_year + 4 ~ "black",
                               year < min_year ~ "black")) 
## PLOT FOR C580Y
prev_cutoff_c580y_plot <- 
  ggplot() +
  geom_line(data=ex, aes(year, predict_stan_prev, color = "true"), linewidth = 1) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev*100, size = N), color = ex_pt$point_col) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    labels = c("2 years", "3 years", "4 years", "true"),
    guide = "none"
  ) + 
  theme(
      axis.line = element_line(),
      axis.text = element_text(size = 6),
      axis.title = element_text(size = 10),
      strip.text.x = element_text(size = 10),
      legend.title = element_text(size = 10),
      legend.text = element_text(size = 8),
      legend.position = "right",
      panel.spacing = unit(0.2, "lines")
    )

################ PLOT FOR R539T ################
df_pred <- df_predict_cutoff_allyear %>% 
  filter(year >= min_year +  pred_y, Locus == "R539T")  
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed), nobs > numofobs, District %in% unique(df_pred$District), Locus == "R539T")
ex_pt <- pfk7_data %>% 
  filter(nobs > numofobs, District %in% unique(df_pred$District), Locus == "R539T") %>% #, year >= min_year & year <= min_year+4
  mutate(point_col = case_when(year >= min_year & year <= min_year + 2 ~ "#E69F00",
                               year > min_year + 2 & year <= min_year + 3 ~ "#56B4E9",
                               year > min_year + 3 & year <= min_year + 4 ~ "#0072B2",
                               year > min_year + 4 ~ "black",
                               year < min_year ~ "black")) 
prev_cutoff_r539t_plot <- 
  ggplot() +
  geom_line(data=ex, aes(year, predict_stan_prev, color = "true")) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev*100, size = N), color = ex_pt$point_col) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    labels = c("2 years", "3 years", "4 years", "true"),
    guide = "none"
  ) + 
  theme(
      axis.line = element_line(),
      axis.text = element_text(size = 6),
      axis.title = element_text(size = 10),
      strip.text.x = element_text(size = 10),
      legend.title = element_text(size = 10),
      legend.text = element_text(size = 8),
      legend.position = "right",
      panel.spacing = unit(0.2, "lines")
    )

################ PLOT FOR ALL KELCH ################
df_pred <- df_predict_cutoff_allyear %>% 
  filter(year >= min_year +  pred_y, Locus == "PfK13")  
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed), nobs > numofobs, District %in% unique(df_pred$District), Locus == "PfK13")
ex_pt <- pfk7_data %>% 
  filter(nobs > numofobs, District %in% unique(df_pred$District), Locus == "PfK13") %>% #, year >= min_year & year <= min_year+4
  mutate(point_col = case_when(year >= min_year & year <= min_year + 2 ~ "#E69F00",
                               year > min_year + 2 & year <= min_year + 3 ~ "#56B4E9",
                               year > min_year + 3 & year <= min_year + 4 ~ "#0072B2",
                               year > min_year + 4 ~ "black",
                               year < min_year ~ "black")) 
 prev_cutoff_all_kelch_plot <- ggplot() +
  geom_line(data=ex, aes(year, predict_stan_prev, color = "true")) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev*100, size = N), color = ex_pt$point_col) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    labels = c("2 years", "3 years", "4 years", "true"),
    guide = "none"
  ) + 
  theme(
      axis.line = element_line(),
      axis.text = element_text(size = 6),
      axis.title = element_text(size = 10),
      strip.text.x = element_text(size = 10),
      legend.title = element_text(size = 10),
      legend.text = element_text(size = 8),
      legend.position = "right",
      panel.spacing = unit(0.2, "lines")
    )
```

##### Saving plots
```{r}
################ PLOT FOR C580Y ################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/SEAsia_cutoff_pred_C580Y_",
    prev_cutoff_perc,
    "prev_pred.png"
  ),
  prev_cutoff_c580y_plot,
  width = 6,
  height = 4,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/SEAsia_cutoff_pred_C580Y_",
    prev_cutoff_perc,
    "prev_pred.pdf"
  ),
  prev_cutoff_c580y_plot,
  width = 6,
  height = 4,
  dpi = 700
)

################ PLOT FOR R539T ################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/SEAsia_cutoff_pred_R539T_",
    prev_cutoff_perc,
    "prev_pred.png"
  ),
  prev_cutoff_r539t_plot,
  width = 6,
  height = 2.7,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/SEAsia_cutoff_pred_R539T_",
    prev_cutoff_perc,
    "prev_pred.pdf"
  ),
  prev_cutoff_r539t_plot,
  width = 6,
  height = 2.7,
  dpi = 700
)

################ PLOT FOR ALL KELCH ################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/SEAsia_cutoff_pred_PfK13_",
    prev_cutoff_perc,
    "prev_pred.png"
  ),
  prev_cutoff_all_kelch_plot,
  width = 6,
  height = 4,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/SEAsia_cutoff_pred_PfK13_",
    prev_cutoff_perc,
    "prev_pred.pdf"
  ),
  prev_cutoff_all_kelch_plot,
  width = 6,
  height = 4,
  dpi = 700
)

write.table(df_predict_cutoff_allyear, paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/SEAsia_cutoff_pred_C580Y_",
    prev_cutoff_perc,
    "predict_cutoff_allyears.txt"))
```

#### No point sizing
```{r}
################ PLOT FOR C580Y ################
prev_cutoff_perc <- prev_cutoff *100
df_pred <- df_predict_cutoff_allyear %>% 
  filter(year >= min_year + pred_y, Locus == "C580Y") 
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed), nobs > numofobs, District %in% unique(df_pred$District), Locus == "C580Y")
ex_pt <- pfk7_data %>% 
  filter(nobs > numofobs, District %in% unique(df_pred$District), Locus == "C580Y") %>% #, year >= min_year & year <= min_year+4
  mutate(point_col = case_when(year >= min_year & year <= min_year + 2 ~ "#E69F00",
                               year > min_year + 2 & year <= min_year + 3 ~ "#56B4E9",
                               year > min_year + 3 & year <= min_year + 4 ~ "#0072B2",
                               year > min_year + 4 ~ "black",
                               year < min_year ~ "black")) 
## PLOT FOR C580Y
prev_cutoff_c580y_plot <- 
  ggplot() +
  geom_line(data=ex, aes(year, predict_stan_prev, color = "true"), linewidth = 1) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev*100), color = ex_pt$point_col) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    labels = c("2 years", "3 years", "4 years", "true")
  ) + 
  theme(
      axis.line = element_line(),
      axis.text = element_text(size = 6),
      axis.title = element_text(size = 10),
      strip.text.x = element_text(size = 10),
      legend.title = element_text(size = 10),
      legend.text = element_text(size = 8),
      legend.position = "right",
      panel.spacing = unit(0.2, "lines")
    )

################ PLOT FOR R539T ################
df_pred <- df_predict_cutoff_allyear %>% 
  filter(year >= min_year +  pred_y, Locus == "R539T")  
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed), nobs > numofobs, District %in% unique(df_pred$District), Locus == "R539T")
ex_pt <- pfk7_data %>% 
  filter(nobs > numofobs, District %in% unique(df_pred$District), Locus == "R539T") %>% #, year >= min_year & year <= min_year+4
  mutate(point_col = case_when(year >= min_year & year <= min_year + 2 ~ "#E69F00",
                               year > min_year + 2 & year <= min_year + 3 ~ "#56B4E9",
                               year > min_year + 3 & year <= min_year + 4 ~ "#0072B2",
                               year > min_year + 4 ~ "black",
                               year < min_year ~ "black")) 
prev_cutoff_r539t_plot <- 
  ggplot() +
  geom_line(data=ex, aes(year, predict_stan_prev, color = "true")) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev*100), color = ex_pt$point_col) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    labels = c("2 years", "3 years", "4 years", "true")
  ) + 
  theme(
      axis.line = element_line(),
      axis.text = element_text(size = 6),
      axis.title = element_text(size = 10),
      strip.text.x = element_text(size = 10),
      legend.title = element_text(size = 10),
      legend.text = element_text(size = 8),
      legend.position = "right",
      panel.spacing = unit(0.2, "lines")
    )

################ PLOT FOR ALL KELCH ################
df_pred <- df_predict_cutoff_allyear %>% 
  filter(year >= min_year +  pred_y, Locus == "PfK13")  
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed), nobs > numofobs, District %in% unique(df_pred$District), Locus == "PfK13")
ex_pt <- pfk7_data %>% 
  filter(nobs > numofobs, District %in% unique(df_pred$District), Locus == "PfK13") %>% #, year >= min_year & year <= min_year+4
  mutate(point_col = case_when(year >= min_year & year <= min_year + 2 ~ "#E69F00",
                               year > min_year + 2 & year <= min_year + 3 ~ "#56B4E9",
                               year > min_year + 3 & year <= min_year + 4 ~ "#0072B2",
                               year > min_year + 4 ~ "black",
                               year < min_year ~ "black")) 
 prev_cutoff_all_kelch_plot <- ggplot() +
  geom_line(data=ex, aes(year, predict_stan_prev, color = "true")) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev*100), color = ex_pt$point_col) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    labels = c("2 years", "3 years", "4 years", "true")
  ) + 
  theme(
      axis.line = element_line(),
      axis.text = element_text(size = 6),
      axis.title = element_text(size = 10),
      strip.text.x = element_text(size = 10),
      legend.title = element_text(size = 10),
      legend.text = element_text(size = 8),
      legend.position = "right",
      panel.spacing = unit(0.2, "lines")
    )
```

##### Saving plots
```{r}
################ PLOT FOR C580Y ################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/no_point_sizing/SEAsia_cutoff_pred_C580Y_",
    prev_cutoff_perc,
    "prev_pred.png"
  ),
  prev_cutoff_c580y_plot,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/no_point_sizing/SEAsia_cutoff_pred_C580Y_",
    prev_cutoff_perc,
    "prev_pred.pdf"
  ),
  prev_cutoff_c580y_plot,
  width = 8,
  height = 5,
  dpi = 700
)

################ PLOT FOR R539T ################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/no_point_sizing/SEAsia_cutoff_pred_R539T_",
    prev_cutoff_perc,
    "prev_pred.png"
  ),
  prev_cutoff_r539t_plot,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/no_point_sizing/SEAsia_cutoff_pred_R539T_",
    prev_cutoff_perc,
    "prev_pred.pdf"
  ),
  prev_cutoff_r539t_plot,
  width = 8,
  height = 5,
  dpi = 700
)

################ PLOT FOR ALL KELCH ################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/no_point_sizing/SEAsia_cutoff_pred_PfK13_",
    prev_cutoff_perc,
    "prev_pred.png"
  ),
  prev_cutoff_all_kelch_plot,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/no_point_sizing/SEAsia_cutoff_pred_PfK13_",
    prev_cutoff_perc,
    "prev_pred.pdf"
  ),
  prev_cutoff_all_kelch_plot,
  width = 8,
  height = 5,
  dpi = 700
)
```

# Comparison to raw data
## Data preprocessing
```{r}
inital_true <- pfk7_data %>% 
  filter(nobs > numofobs)

corr_df_cutoff <- NULL
for(l in unique(df_predict_cutoff_allyear$label)) {
  #filter forecasting based on year (label)
  pred <- df_predict_cutoff_allyear %>%
    filter(label == l) %>%
    mutate(val = paste0(year, District, Locus, min_year)) %>%
    arrange(val) %>%
    rename(p_pred = predict) 
  #filter data points in true that are also in forecasted
  true <- inital_true
  true <- true %>%
    mutate(val = paste0(year, District, Locus, min_year)) %>%
    arrange(val) %>%
    filter(val %in% pred$val)
  #make sure districts match between true and forecasted
  pred <- pred %>% filter(val %in% true$val)
  df <- cbind(true, pred$p_pred, pred$label, pred$pred_y)
  colnames(df)[ncol(df)-2] <- "p_pred"
  colnames(df)[ncol(df)-1] <- "label"
  colnames(df)[ncol(df)] <- "pred_y"
  corr_df_cutoff <- rbind(corr_df_cutoff, df) %>% 
    filter(year >= min_year + pred_y)
}

corr_df_cutoff <- corr_df_cutoff %>% 
  mutate(p_pred_prev = exp(p_pred) * 100 / (1 + exp(p_pred))) %>% 
  rename(t_pred_prev = prev) %>%
  group_by(country, District, label)
```                                            

## Plotting per district
```{r}
## Correlation plot for 50% cutoff in first year
for (mu in unique(corr_df_cutoff$Locus)){
  correlation_raw_plot_cutoff <- corr_df_cutoff %>% filter(Locus == mu) %>%
    ggplot(aes(x = t_pred_prev, y = p_pred_prev, color = label, group = label)) +
    geom_point() +
    geom_smooth(method=lm, se=FALSE) +
    geom_abline(slope = 1, intercept = 0, color = "grey") +
    facet_wrap(~ District) +
    theme_bw() +
    xlab("True") +
    ylab("Predicted") +
    # scale_y_continuous(limits=c(-10,105), breaks = c(0, 25, 50, 75, 100)) +
    # scale_x_continuous(limits=c(-10,105), breaks = c(0, 25, 50, 75, 100)) +
    scale_color_manual(
      values = c("#E69F00", "#56B4E9", "#0072B2"),
      labels = c("2 years", "3 years", "4 years")
    ) + 
    theme_bw() +
    ggpubr::theme_pubclean(base_size = 12) +
    theme(
      axis.line = element_line(),
      axis.text = element_text(size = 6),
      axis.title = element_text(size = 10),
      strip.text.x = element_text(size = 10),
      legend.position = "none",
      panel.spacing = unit(0.2, "lines")
    ) +  labs(color = NULL)
  
  #Assigning df_predict to variables
  var_name <- paste0(mu, "_correlation_raw_plot_cutoff")
  assign(var_name, correlation_raw_plot_cutoff)
}
```

### Saving plots
```{r}
################# C580Y #################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/correlation/SEAsia_cutoff_raw_C580Y_correlation_raw_",
    prev_cutoff_perc,
    "cutoff_prev.png"
  ),
  C580Y_correlation_raw_plot_cutoff,
  width = 6,
  height = 4,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/correlation/SEAsia_cutoff_raw_C580Y_correlation_raw_",
    prev_cutoff_perc,
    "cutoff_prev.pdf"
  ),
  C580Y_correlation_raw_plot_cutoff,
  width = 6,
  height = 4,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/correlation/large/SEAsia_cutoff_raw_large_C580Y_correlation_raw_",
    prev_cutoff_perc,
    "cutoff_prev.pdf"
  ),
  C580Y_correlation_raw_plot_cutoff,
  width = 8,
  height = 5,
  dpi = 700
)

################# R539T #################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/correlation/SEAsia_cutoff_raw_R539T_correlation_raw_",
    prev_cutoff_perc,
    "cutoff_prev.png"
  ),
  R539T_correlation_raw_plot_cutoff,
  width = 6,
  height = 2.7,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/correlation/SEAsia_cutoff_raw_R539T_correlation_raw_",
    prev_cutoff_perc,
    "cutoff_prev.pdf"
  ),
  R539T_correlation_raw_plot_cutoff,
  width = 6,
  height = 2.7,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/correlation/large/SEAsia_cutoff_raw_large_R539T_correlation_raw_",
    prev_cutoff_perc,
    "cutoff_prev.pdf"
  ),
  R539T_correlation_raw_plot_cutoff,
  width = 8,
  height = 5,
  dpi = 700
)

################# PfK13 #################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/correlation/SEAsia_cutoff_raw_PfK13_correlation_raw_",
    prev_cutoff_perc,
    "cutoff_prev.png"
  ),
  PfK13_correlation_raw_plot_cutoff,
  width = 6,
  height = 4,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/correlation/SEAsia_cutoff_raw_PfK13_correlation_raw_",
    prev_cutoff_perc,
    "cutoff_prev.pdf"
  ),
  PfK13_correlation_raw_plot_cutoff,
  width = 6,
  height = 4,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_firstobs/correlation/large/SEAsia_cutoff_raw_large_PfK13_correlation_raw_",
    prev_cutoff_perc,
    "cutoff_prev.pdf"
  ),
  PfK13_correlation_raw_plot_cutoff,
  width = 8,
  height = 5,
  dpi = 700
)
```

## Combined District: plotting for avg
```{r}
## Correlation plot for 50% avg
for (mu in unique(corr_df_cutoff$Locus)){
  correlation_raw_plot_cutoff <- corr_df_cutoff %>% 
    filter(Locus == mu) %>% 
    rename("Mutation" = "Locus") %>%
  ggplot(aes(x = t_pred_prev, y = p_pred_prev, color = label, shape = District)) +
  geom_point() +
  geom_smooth(method=lm, se=FALSE, linetype = "dashed") +
  geom_abline(slope = 1, intercept = 0, color = "grey", linetype = "dashed") +
  theme_bw() +
  ggpubr::theme_pubclean(base_size = 12) +
  xlab("True") +
  ylab("Predicted") +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2"),
    labels = c("2 years", "3 years", "4 years"),
    name = ""
  ) + 
  labs(shape = "") +
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 10),
    strip.text.x = element_text(size = 10),
    legend.position = "right"
  )
  
    #Assigning df_predict to variables
  var_name <- paste0(mu, "_comb_dist_correlation_raw_plot_cutoff")
  assign(var_name, correlation_raw_plot_cutoff)
}
```

### Saving
```{r}
################# C580Y #################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff/correlation/Combined-District/SEAsia_cutoff_raw_C580Y_correlation_raw_",
    prev_cutoff_perc,
    "cutoff_prev.png"
  ),
  C580Y_comb_dist_correlation_raw_plot_cutoff,
  width = 6,
  height = 3,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff/correlation/Combined-District/SEAsia_cutoff_raw_C580Y_correlation_raw_",
    prev_cutoff_perc,
    "cutoff_prev.pdf"
  ),
  C580Y_comb_dist_correlation_raw_plot_cutoff,
  width = 6,
  height = 3,
  dpi = 700
)

################# R539T #################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff/correlation/Combined-District/SEAsia_cutoff_raw_R539T_correlation_raw_",
    prev_cutoff_perc,
    "cutoff_prev.png"
  ),
  R539T_comb_dist_correlation_raw_plot_cutoff,
  width = 6,
  height = 3,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff/correlation/Combined-District/SEAsia_cutoff_raw_R539T_correlation_raw_",
    prev_cutoff_perc,
    "cutoff_prev.pdf"
  ),
  R539T_comb_dist_correlation_raw_plot_cutoff,
  width = 6,
  height = 3,
  dpi = 700
)

################# PfK13 #################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff/correlation/Combined-District/SEAsia_cutoff_raw_PfK13_correlation_raw_",
    prev_cutoff_perc,
    "cutoff_prev.png"
  ),
  PfK13_comb_dist_correlation_raw_plot_cutoff,
  width = 6,
  height = 3,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff/correlation/Combined-District/SEAsia_cutoff_raw_PfK13_correlation_raw_",
    prev_cutoff_perc,
    "cutoff_prev.pdf"
  ),
  PfK13_comb_dist_correlation_raw_plot_cutoff,
  width = 6,
  height = 3,
  dpi = 700
)
```

# Supplement Figure 

## Figure 4 (A): Binh Phuoc - Model
### Preprocessing
```{r}
prev_Ratanakiri <- pfk7_data %>% 
  select(country, District, year, Locus, x, n, N, nobs, lrsmed, prev, predict_stan_prev, conf.low_prev, conf.high_prev) %>% 
  filter(District == "Ratanakiri", Locus == "C580Y", nobs > numofobs)
```

### Ploting
```{r}
df_Ratanakiri_pred <- df_predict_cutoff_allyear %>% 
  filter(year <= min_year + pred_y, 
         Locus == "C580Y", 
         District == "Ratanakiri") %>%
  mutate(predict_prev = exp(predict)*100/(1+exp(predict))) 
ex_pt <- pfk7_data %>% 
  filter(nobs > numofobs, District == "Ratanakiri", Locus == "C580Y") %>%
  mutate(point_col = case_when(year >= min_year & year <= min_year + 2 ~ "#E69F00",
                               year > min_year + 2 & year <= min_year + 3 ~ "#56B4E9",
                               year > min_year + 3 & year <= min_year + 4 ~ "#0072B2",
                               year > min_year + 4 ~ "black",
                               year < min_year ~ "black")) 
prev_Ratanakiri_plot <- ggplot() +
  geom_line(data = df_Ratanakiri_pred, aes(year, predict_prev, group = label, color = label)) +
  geom_point(data = ex_pt, aes(x=year, y=prev*100, size = N), color = ex_pt$point_col) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  scale_x_continuous(breaks = seq(min(ex_pt$year), max(ex_pt$year), by = 2)) +
  scale_color_manual(
    values=c("#E69F00", "#56B4E9", "#0072B2"), 
    name = "Mutations", 
    labels = c("580Y", "combined PfK13", "539T")) + 
  ylab("Prevalence") +
  xlab("Year") +
  ylim(-1, 101)+
  ggpubr::theme_pubclean(base_size = 12)+
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8),
    legend.text = element_text(size = 8),
    strip.text.x = element_text(size = 8),
    legend.title = element_text(size = 8),
    legend.position = "none"
  )
```

### Saving
```{r}
ggsave("figures/Figure4_Ratanakiri_model.png",
  prev_Ratanakiri_plot,
  width = 4.5,
  height = 3,
  dpi = 700
)
ggsave("figures/Figure4_Ratanakiri_model.pdf",
  prev_Ratanakiri_plot,
  width = 4.5,
  height = 3,
  dpi = 700
)
```

## Figure 4 (B): Binh Phuoc - Avg Forecasting 
### Preprocessing
```{r}
df_pred <- df_predict_cutoff_allyear %>% 
  filter(year >= min_year + pred_y, Locus == "C580Y", District == "Ratanakiri", Locus == "C580Y") %>%
  mutate(predicted_prev = exp(predict)*100/(1+exp(predict)))
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed), nobs > numofobs, District %in% unique(df_pred$District), Locus == "C580Y")
ex_pt <- pfk7_data %>% 
  filter(nobs > numofobs, 
         District %in% unique(df_pred$District), 
         Locus == "C580Y") %>%
  mutate(point_col = case_when(year >= min_year & year <= min_year + 2 ~ "#E69F00",
                               year > min_year + 2 & year <= min_year + 3 ~ "#56B4E9",
                               year > min_year + 3 & year <= min_year + 4 ~ "#0072B2",
                               year > min_year + 4 ~ "black",
                               year < min_year ~ "black")) 
```

### Plotting
```{r}
prev_cutoff_c580y_Ratanakiri_plot <- 
  ggplot() +
  geom_line(data=ex, aes(year, predict_stan_prev, color = "true"), linewidth = 1) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label, color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev*100, size = N), color = ex_pt$point_col) +
  labs(shape="Mutations", size = "Sample Size") +
  scale_x_continuous(breaks = seq(min(ex_pt$year), max(df_pred$year), by = 2)) +
  theme_bw() +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    labels = c("2 years", "3 years", "4 years", "true")
  ) + 
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8),
    strip.text.x = element_text(size = 8),
    legend.position = "none",
  ) +  labs(color = NULL)
```

### Saving
```{r}
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_Ratanakiri/SEAsia_cutoff_pred_C580Y_Ratanakiri_",
    prev_cutoff_perc,
    "avg_prev_pred.png"
  ),
  prev_cutoff_c580y_Ratanakiri_plot,
  width = 2.7,
  height = 3,
  dpi = 700
)

ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_district/50_cutoff_Ratanakiri/SEAsia_cutoff_pred_C580Y_Ratanakiri_",
    prev_cutoff_perc,
    "avg_prev_pred.pdf"
  ),
  prev_cutoff_c580y_Ratanakiri_plot,
  width = 2.7,
  height = 3.5,
  dpi = 700
)
```
