---
title: "Kelch PfK7 Prediction for 2,3,4 years"
output: html_document
date: "2023-03-16"
---

```{r setup, include=FALSE}
library(lme4)
library(nlme)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(scales)
library(tidyverse)
library(cowplot)
library(tabulizer)
library(RColorBrewer)
library(tidyverse) # ggplot2, dplyr, tidyr, readr, purrr, tibble
library(rnaturalearth)
library(rnaturalearthdata)
library(sf) #see ubuntu issues here: https://rtask.thinkr.fr/installation-of-r-4-0-on-ubuntu-20-04-lts-and-tips-for-spatial-packages/
library(ggspatial)
library(scatterpie)
library(scales)
library (ggforce)
library (ggmap)
library(rstan)
library(gt)
## install.packages("rstan", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))

```

# Load data
```{r}
#load data
pfk7_data <- read.table("data/data-derived/pfk7_country_data.txt")
#set the limit of number of observations
numofobs <- 2

pfk7_data <- pfk7_data %>%
  group_by(country) %>%
  mutate(min_year_c580y = min(year[c580y>0]), 
         min_year_r539t = min(year[r539t>0]), 
         min_year_all_kelch = min(year[all_kelch>0])) %>%
  ungroup 
```

# Bayesian GMM with slopes and intercepts
```{r}
# Have a read through rstanarm vignettes and guides on how it works in comparison to lme4
# ---- Model for c580y -----
c580y_stanmod <- rstanarm::stan_glmer(
  lrsmed_580y ~ adj_year + (1 + adj_year | country),
  data = pfk7_data %>% filter(nobs_c580y > numofobs),
  weights = wt_med_580y,
  adapt_delta = 0.9975
)

vals <- summary(c580y_stanmod$stanfit)$summary[, 1]
vals <- vals[grep("^b", names(vals))]
ranef_c580y_stanmod <-
  data.frame("Intercepts" = vals[seq(1, length(vals), 2)],
             "Slopes" = vals[seq(2, length(vals), 2)])
ranef_c580y_stanmod$mutation <- rep("c580y", dim(ranef_c580y_stanmod)[1])

# ---- Model for r539t -----

r539t_stanmod <- rstanarm::stan_glmer(
  lrsmed_539t ~ adj_year + (1 + adj_year | country),
  data = pfk7_data %>% filter(nobs_r539t > numofobs),
  weights = wt_med_539t,
  adapt_delta = 0.9975
)

vals <- summary(r539t_stanmod$stanfit)$summary[, 1]
vals <- vals[grep("^b", names(vals))]
ranef_r539t_stanmod <-
  data.frame("Intercepts" = vals[seq(1, length(vals), 2)],
             "Slopes" = vals[seq(2, length(vals), 2)])
ranef_r539t_stanmod$mutation <-
  rep("r539t", dim(ranef_r539t_stanmod)[1])

# ---- Model for combined kelch -----

all_kelch_stanmod <- rstanarm::stan_glmer(
  lrsmed_all_kelch ~ adj_year + (1 + adj_year | country),
  data = pfk7_data %>% filter(nobs_kelch > numofobs),
  weights = wt_med_all_kelch,
  adapt_delta = 0.9975
)

vals <- summary(all_kelch_stanmod$stanfit)$summary[, 1]
vals <- vals[grep("^b", names(vals))]
ranef_all_kelch_stanmod <-
  data.frame("Intercepts" = vals[seq(1, length(vals), 2)],
             "Slopes" = vals[seq(2, length(vals), 2)])
ranef_all_kelch_stanmod$mutation <-
  rep("all_kelch", dim(ranef_all_kelch_stanmod)[1])

ranef_stanmod <-
  rbind(ranef_c580y_stanmod,
        ranef_all_kelch_stanmod,
        ranef_r539t_stanmod)
ranef_stanmod$site <- str_replace_all(rownames(ranef_stanmod), "\\[|\\]", "")
ranef_stanmod$site <- str_replace_all(ranef_stanmod$site, "\\s*\\([^\\)]+\\)", "")
ranef_stanmod$site <- str_remove(ranef_stanmod$site, "b country:")
ranef_stanmod$site <- str_remove(ranef_stanmod$site, "1")
``` 
## GMM posterior
```{r}
#  get model predictions for plotting
pfk7_data$predict_stan_c580y <- NA
pfk7_data$predict_stan_r539t <- NA
pfk7_data$predict_stan_all_kelch <- NA

pfk7_data$predict_stan_c580y[is.finite(pfk7_data$lrsmed_580y) & pfk7_data$nobs_c580y > numofobs] <-  rstanarm::posterior_predict(c580y_stanmod, type = "response") %>% colMeans
pfk7_data$predict_stan_r539t[is.finite(pfk7_data$lrsmed_539t) & pfk7_data$nobs_r539t > numofobs] <-  rstanarm::posterior_predict(r539t_stanmod, type = "response") %>% colMeans
pfk7_data$predict_stan_all_kelch[is.finite(pfk7_data$lrsmed_all_kelch) & pfk7_data$nobs_kelch > numofobs] <-  rstanarm::posterior_predict(all_kelch_stanmod, type = "response") %>% colMeans
```

## Obtain confidence interval of and posterior of posterior for each mutation
```{r}
#  get model predictions for plotting
pfk7_data$conf.low_c580y <- NA
pfk7_data$conf.high_c580y <- NA
pfk7_data$conf.low_r539t <- NA
pfk7_data$conf.high_r539t <- NA
pfk7_data$conf.low_all_kelch <- NA
pfk7_data$conf.high_all_kelch <- NA

c580y_conf <- rstanarm::posterior_predict(c580y_stanmod, type = "response") %>% apply(2, quantile, prob = (c(0.025, 0.975)))
r539t_conf <- rstanarm::posterior_predict(r539t_stanmod, type = "response") %>% apply(2, quantile, prob = (c(0.025, 0.975)))
all_kelch_conf <- rstanarm::posterior_predict(all_kelch_stanmod, type = "response") %>% apply(2, quantile, prob = (c(0.025, 0.975)))

# here just add predictions  for the c469Y rows
pfk7_data$conf.low_c580y[is.finite(pfk7_data$lrsmed_580y) & pfk7_data$nobs_c580y > numofobs] <- c580y_conf[1,]
pfk7_data$conf.low_r539t[is.finite(pfk7_data$lrsmed_539t) & pfk7_data$nobs_r539t > numofobs] <- r539t_conf[1,]
pfk7_data$conf.low_all_kelch[is.finite(pfk7_data$lrsmed_all_kelch) & pfk7_data$nobs_kelch > numofobs] <- all_kelch_conf[1,]

pfk7_data$conf.high_c580y[is.finite(pfk7_data$lrsmed_580y) & pfk7_data$nobs_c580y > numofobs] <- c580y_conf[2,]
pfk7_data$conf.high_r539t[is.finite(pfk7_data$lrsmed_539t) & pfk7_data$nobs_r539t > numofobs] <- r539t_conf[2,]
pfk7_data$conf.high_all_kelch[is.finite(pfk7_data$lrsmed_all_kelch) & pfk7_data$nobs_kelch > numofobs] <- all_kelch_conf[2,]
```

## Obtain GMM posterior for each mutation on prevalence scale
```{r}
pfk7_data$predict_stan_prev_c580y <- NA
pfk7_data$predict_stan_prev_r539t <- NA
pfk7_data$predict_stan_prev_all_kelch <- NA

pfk7_data$predict_stan_prev_c580y <- exp(pfk7_data$predict_stan_c580y)*100/(1+exp(pfk7_data$predict_stan_c580y))
pfk7_data$predict_stan_prev_r539t <- exp(pfk7_data$predict_stan_r539t)*100/(1+exp(pfk7_data$predict_stan_r539t))
pfk7_data$predict_stan_prev_all_kelch <- exp(pfk7_data$predict_stan_all_kelch)*100/(1+exp(pfk7_data$predict_stan_all_kelch))

pfk7_data$conf.high_prev_c580y <- exp(pfk7_data$conf.high_c580y)*100/(1+exp(pfk7_data$conf.high_c580y))
pfk7_data$conf.high_prev_r539t <- exp(pfk7_data$conf.high_r539t)*100/(1+exp(pfk7_data$conf.high_r539t))
pfk7_data$conf.high_prev_all_kelch <- exp(pfk7_data$conf.high_all_kelch)*100/(1+exp(pfk7_data$conf.high_all_kelch))

pfk7_data$conf.low_prev_c580y <- exp(pfk7_data$conf.low_c580y)*100/(1+exp(pfk7_data$conf.low_c580y))
pfk7_data$conf.low_prev_r539t <- exp(pfk7_data$conf.low_r539t)*100/(1+exp(pfk7_data$conf.low_r539t))
pfk7_data$conf.low_prev_all_kelch <- exp(pfk7_data$conf.low_all_kelch)*100/(1+exp(pfk7_data$conf.low_all_kelch))
```

# Forecasting Selection 

## Based on the first 2, 3, and 4 years
```{r}
pred_year <- c(2, 3, 4)

for (i in pred_year) {
  #------ Model prediction for C580Y ------
  c580y_pred <- rstanarm::stan_glmer(
    lrsmed_580y ~ adj_year + (1 + adj_year | country),
    data = pfk7_data %>% filter(
      nobs_c580y > numofobs,
      year >= min_year_c580y & year <= min_year_c580y + i
    ),
    weights = wt_med_580y,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs_c580y > numofobs, is.finite(pfk7_data$lrsmed_580y)) %>% 
    mutate(Locus = "C580Y") %>%
    group_by(country, Locus) %>%
    complete(year = seq(min(min_year_c580y) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, country, min_year_c580y, Locus) %>% 
    mutate(min_year_c580y = replace(min_year_c580y, is.na(min_year_c580y), 0)) %>%
    group_by(country) %>%
    distinct(year, .keep_all = TRUE)
  
  new_data <- new_data %>%
    group_by(country, Locus) %>%
    mutate(adj_year = year - max(min_year_c580y),
           min_year = min_year_c580y) %>%
    select(!min_year_c580y) %>% 
    arrange(year)
  
  predictions <-
    rstanarm::posterior_predict(c580y_pred, type = "response", newdata = new_data) %>% colMeans
  new_data$predict <- predictions
  df_predict <- new_data
  
  #------ Model prediction for R539T ------
  
  r539t_pred <- rstanarm::stan_glmer(
    lrsmed_539t ~ adj_year + (1 + adj_year | country),
    data = pfk7_data %>% filter(
      nobs_r539t > numofobs,
      year >= min_year_r539t & year <= min_year_r539t + i
    ),
    weights = wt_med_539t,
    adapt_delta = 0.9975
  )
  
  #forecasting
  new_data <- pfk7_data %>%
    filter(nobs_r539t > numofobs, is.finite(pfk7_data$lrsmed_539t)) %>%
    mutate(Locus = "R539T") %>%
    group_by(country, Locus) %>%
    complete(year = seq(min(min_year_r539t) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, country, min_year_r539t, Locus) %>%
    mutate(min_year_r539t = replace(min_year_r539t, is.na(min_year_r539t), 0)) %>%
    group_by(country) %>%
    distinct(year, .keep_all = TRUE)
  
  new_data <- new_data %>%
    group_by(country, Locus) %>%
    mutate(adj_year = year - max(min_year_r539t),
           min_year = min_year_r539t) %>%
    select(!min_year_r539t) %>% 
    arrange(year)
  
  predictions <-
    rstanarm::posterior_predict(r539t_pred, type = "response", newdata = new_data) %>% colMeans
  new_data$predict <- predictions
  
  df_predict <- rbind(df_predict, new_data)
  
  #------ Model prediction for combined PfK13 mutations ------
  
  all_kelch_pred <- rstanarm::stan_glmer(
    lrsmed_all_kelch ~ adj_year + (1 + adj_year | country),
    data = pfk7_data %>% filter(
      nobs_kelch > numofobs,
      year >= min_year_all_kelch & year <= min_year_all_kelch + i
    ),
    weights = wt_med_all_kelch,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs_kelch > numofobs, is.finite(pfk7_data$lrsmed_all_kelch)) %>% 
    mutate(Locus = "all_kelch") %>%
    group_by(country, Locus) %>% 
    complete(year = seq(min(min_year_all_kelch) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, country, min_year_all_kelch, Locus) %>% 
    mutate(min_year_all_kelch = replace(min_year_all_kelch, is.na(min_year_all_kelch), 0)) %>%
    group_by(country) %>%
    distinct(year, .keep_all = TRUE)
    
  new_data <- new_data %>%
    group_by(country, Locus) %>%
    mutate(adj_year = year - max(min_year_all_kelch),
           min_year = min_year_all_kelch) %>%
    select(!min_year_all_kelch) %>% 
    arrange(year)
  
  predictions <-
    rstanarm::posterior_predict(all_kelch_pred, type = "response", newdata = new_data) %>% colMeans
  new_data$predict <- predictions
  df_predict <- rbind(df_predict, new_data)
  
  df_predict <- df_predict %>% 
    group_by(country, Locus) %>% 
    mutate(min_year = replace_na(min_year, 0), min_year = max(min_year)) %>% 
    mutate(label = paste0(i, "year"),  pred_y = i)
  
  #Assigning df_predict to variables
  var_name <- paste0("df_predict_", i, "year")
  assign(var_name, df_predict)
}

#combine forecasting predictions for all years
df_predict_allyear <- rbind(df_predict_2year, df_predict_3year, df_predict_4year)
```

### Ploting forecasting of predictions for the first 2, 3, and 4 years
```{r}
################ PLOT FOR C580Y ################
ex <- pfk7_data %>% filter(is.finite(lrsmed_580y), nobs_c580y > numofobs)
ex_pt <- pfk7_data %>% filter(nobs_c580y > numofobs) %>%
  mutate(point_col = case_when(year >= min_year_c580y + 2 & year <= min_year_c580y + 2 ~ "#E69F00",
                               year > min_year_c580y + 2 & year <= min_year_c580y + 3 ~ "#56B4E9",
                                year > min_year_c580y + 3 & year <= min_year_c580y + 4 ~ "#0072B2",
                               year > min_year_c580y + 4 ~ "black")) 
df_pred <- df_predict_allyear %>% 
  filter(country %in% unique(ex$country), year >= min_year + pred_y, Locus == "C580Y")
prev_c580y_plot <- 
  ggplot() +
  geom_line(data=ex %>% mutate(N = n+c580y), aes(year, predict_stan_prev_c580y, color = "true"), linewidth = 1) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev_580y*100), color = ex_pt$point_col) +
  ggtitle("C580Y") +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(values=c("#E69F00", "#56B4E9", "#0072B2", "grey"), name = "Mutations", labels = c("2 years", "3 years", "4 years", "true")) + 
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.direction = "vertical",
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)
  ) +  labs(color = NULL)

################ PLOT FOR R539T ################
ex <- pfk7_data %>% filter(is.finite(lrsmed_539t), nobs_r539t > numofobs)
ex_pt <- pfk7_data %>% filter(nobs_r539t > numofobs) %>%
  mutate(point_col = case_when(year >= min_year_r539t + 2 & year <= min_year_r539t + 2 ~ "#E69F00",
                             year > min_year_r539t + 2 & year <= min_year_r539t + 3 ~ "#56B4E9",
                              year > min_year_r539t + 3 & year <= min_year_r539t + 4 ~ "#0072B2",
                             year > min_year_r539t + 4 ~ "black")) 
df_pred <- df_predict_allyear %>% 
  filter(country %in% unique(ex$country), year >= min_year +  pred_y, Locus == "R539T")
prev_r539t_plot <- 
  ggplot() +
  geom_line(data=ex %>% mutate(N = n+r539t), aes(year, predict_stan_prev_r539t, color = "true")) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev_539t*100), color = ex_pt$point_col) +
  ggtitle("R539T") +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(values=c("#E69F00", "#56B4E9", "#0072B2", "grey"), name = "Mutations", labels = c("2 years", "3 years", "4 years", "true")) + 
  theme(axis.line = element_line(), axis.text = element_text(size = 8), axis.title=element_text(size=12), legend.text=element_text(size=12), strip.text.x = element_text(size = 12), legend.title = element_text(size=12), legend.direction = "vertical", legend.position = "right", plot.title = element_text(hjust = 0.5)) +  labs(color=NULL)


################ PLOT FOR ALL KELCH ################
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed_all_kelch), nobs_kelch > numofobs)
ex_pt <- pfk7_data %>% 
  filter(nobs_kelch > numofobs) %>%
  mutate(point_col = case_when(year >= min_year_all_kelch + 2 & year <= min_year_all_kelch + 2 ~ "#E69F00",
                             year > min_year_all_kelch + 2 & year <= min_year_all_kelch + 3 ~ "#56B4E9",
                              year > min_year_all_kelch + 3 & year <= min_year_all_kelch + 4 ~ "#0072B2",
                             year > min_year_all_kelch + 4 ~ "black")) 
df_pred <- df_predict_allyear %>% 
  filter(country %in% unique(ex$country), year >= min_year +  pred_y, Locus == "all_kelch")  
prev_all_kelch_plot <- 
  ggplot() +
  geom_line(data=ex %>% mutate(N = n+all_kelch), aes(year, predict_stan_prev_all_kelch, color = "true")) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev_all_kelch*100), color = ex_pt$point_col) +
  ggtitle("PfK13") +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(values=c("#E69F00", "#56B4E9", "#0072B2", "grey"), name = "Mutations", labels = c("2 years", "3 years", "4 years", "true")) + 
  theme(axis.line = element_line(), axis.text = element_text(size = 8), axis.title=element_text(size=12), legend.text=element_text(size=12), strip.text.x = element_text(size = 12), legend.title = element_text(size=12), legend.direction = "vertical", legend.position = "right", plot.title = element_text(hjust = 0.5)) +  labs(color=NULL)
```

### Saving plots
```{r}
################ PLOT FOR C580Y ################
ggsave(
  "figures/predictions/SE_Asia/per_country/SEAsia_pred_C580Y_pred.png",
  prev_c580y_plot,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  "figures/predictions/SE_Asia/per_country/SEAsia_pred_C580Y_pred.pdf",
  prev_c580y_plot,
  width = 8,
  height = 5,
  dpi = 700
)

################ PLOT FOR R539T ################
ggsave(
  "figures/predictions/SE_Asia/per_country/SEAsia_pred_R539T_pred.png",
  prev_r539t_plot,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  "figures/predictions/SE_Asia/per_country/SEAsia_pred_R539T_pred.pdf",
  prev_r539t_plot,
  width = 8,
  height = 5,
  dpi = 700
)

################ PLOT FOR ALL KELCH ################
ggsave(
  "figures/predictions/SE_Asia/per_country/SEAsia_pred_Pfk13_pred.png",
  prev_all_kelch_plot,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  "figures/predictions/SE_Asia/per_country/SEAsia_pred_Pfk13_pred.pdf",
  prev_all_kelch_plot,
  width = 8,
  height = 5,
  dpi = 700
)
```

## Based on the first 2, 3, and 4 years with prevalence cut off per country
```{r}
pred_year <- c(2, 3, 4)
prev_cutoff <- 0.2

for (i in pred_year) {
  #------ Model prediction for C580Y ------
  data_c580y <- pfk7_data %>% 
    filter(nobs_c580y > numofobs, year >= min_year_c580y & year <= min_year_c580y + i)
  
  val <- data_c580y[data_c580y$year == data_c580y$min_year_c580y, ]
  selected_country <- val$country[val$prev_580y <= prev_cutoff]
  
  data_c580y <- data_c580y %>% 
    filter(country %in% selected_country)
  
  c580y_pred <- rstanarm::stan_glmer(
    lrsmed_580y ~ adj_year + (1 + adj_year | country),
    data = data_c580y,
    weights = wt_med_580y,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs_c580y > numofobs, is.finite(pfk7_data$lrsmed_580y), country %in% selected_country) %>%
    mutate(Locus = "C580Y") %>%
    group_by(country, Locus) %>%
    complete(year = seq(min(min_year_c580y) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, country, min_year_c580y, Locus) %>%
    mutate(min_year_c580y = replace(min_year_c580y, is.na(min_year_c580y), 0)) %>%
    group_by(country) %>%
    distinct(year, .keep_all = TRUE)
  
  new_data <- new_data %>%
    group_by(country, Locus) %>%
    mutate(adj_year = year - max(min_year_c580y),
           min_year = min_year_c580y) %>%
    select(!min_year_c580y) %>% 
    arrange(year)
  
  predictions <-
    rstanarm::posterior_predict(c580y_pred, type = "response", newdata = new_data) %>% colMeans
  new_data$predict <- predictions
  
  df_predict <- new_data
  
  #------ Model prediction for R539T ------
  data_r539t <- pfk7_data %>% 
    filter(nobs_r539t > numofobs, year >= min_year_r539t & year <= min_year_r539t + i)
  
  val <- data_r539t[data_r539t$year == data_r539t$min_year_r539t, ]
  selected_country <- val$country[val$prev_539t <= prev_cutoff]
  
  data_r539t <- data_r539t %>% 
    filter(country %in% selected_country)
  
  r539t_pred <- rstanarm::stan_glmer(
    lrsmed_539t ~ adj_year + (1 + adj_year | country),
    data = data_r539t,
    weights = wt_med_539t,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs_r539t > numofobs, is.finite(pfk7_data$lrsmed_539t), country %in% selected_country) %>% 
    mutate(Locus = "R539T") %>%
    group_by(country, Locus) %>%
    complete(year = seq(min(min_year_r539t) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, country, min_year_r539t, Locus) %>%
    mutate(min_year_r539t = replace(min_year_r539t, is.na(min_year_r539t), 0)) %>%
    group_by(country) %>%
    distinct(year, .keep_all = TRUE)
  
  new_data <- new_data %>%
    group_by(country, Locus) %>%
    mutate(adj_year = year - max(min_year_r539t),
           min_year = min_year_r539t) %>%
    select(!min_year_r539t) %>% 
    arrange(year)
  
  predictions <-
    rstanarm::posterior_predict(r539t_pred, type = "response", newdata = new_data) %>% colMeans
  new_data$predict <- predictions
  
  df_predict <- rbind(df_predict, new_data)
  
  #------ Model prediction for combined PfK13 mutations ------
  data_all_kelch <- pfk7_data %>% 
    filter(nobs_kelch > numofobs, year >= min_year_all_kelch & year <= min_year_all_kelch + i)
  
  val <- data_all_kelch[data_all_kelch$year == data_all_kelch$min_year_all_kelch, ]
  selected_country <- val$country[val$prev_all_kelch <= prev_cutoff]
  
  data_all_kelch <- data_all_kelch %>% 
    filter(country %in% selected_country)
  
  all_kelch_pred <- rstanarm::stan_glmer(
    lrsmed_all_kelch ~ adj_year + (1 + adj_year | country),
    data = data_all_kelch,
    weights = wt_med_all_kelch,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs_kelch > numofobs, is.finite(pfk7_data$lrsmed_all_kelch), country %in% selected_country) %>% 
    mutate(Locus = "all_kelch") %>%
    group_by(country, Locus) %>%
    complete(year = seq(min(min_year_all_kelch) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, country, min_year_all_kelch, Locus) %>% 
    mutate(min_year_all_kelch = replace(min_year_all_kelch, is.na(min_year_all_kelch), 0)) %>%
    group_by(country) %>%
    distinct(year, .keep_all = TRUE)
    
  new_data <- new_data %>%
    group_by(country, Locus) %>%
    mutate(adj_year = year - max(min_year_all_kelch),
           min_year = min_year_all_kelch) %>%
    select(!min_year_all_kelch) %>% 
    arrange(year)
  
  predictions <-
    rstanarm::posterior_predict(all_kelch_pred, type = "response", newdata = new_data) %>% colMeans
  new_data$predict <- predictions
  
  df_predict <- rbind(df_predict, new_data)
  
  df_predict <- df_predict %>% 
    group_by(country, Locus) %>% 
    mutate(min_year = replace_na(min_year, 0), min_year = max(min_year)) %>% 
    mutate(label = paste0(i, "year"),  pred_y = i)
  
  #Assigning df_predict to variables
  var_name <- paste0("df_predict_cutoff_", i, "year")
  assign(var_name, df_predict)
}

#combine forecasting predictions for all years
df_predict_cutoff_allyear <- rbind(df_predict_cutoff_2year, df_predict_cutoff_3year, df_predict_cutoff_4year)
```

### Plotting forecasting of predictions for the first 2, 3, and 4 years with prevalence cut off
```{r}
prev_cutoff_perc <- prev_cutoff *100

################ PLOT FOR C580Y ################
df_pred <- df_predict_cutoff_allyear %>% 
  filter(year >= min_year + pred_y, Locus == "C580Y") 
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed_580y), nobs_c580y > numofobs, country %in% unique(df_pred$country))
ex_pt <- pfk7_data %>% 
  filter(nobs_c580y > numofobs, country %in% unique(df_pred$country)) %>%
  mutate(point_col = case_when(year >= min_year_c580y + 2 & year <= min_year_c580y + 2 ~ "#E69F00",
                               year > min_year_c580y + 2 & year <= min_year_c580y + 3 ~ "#56B4E9",
                                year > min_year_c580y + 3 & year <= min_year_c580y + 4 ~ "#0072B2",
                               year > min_year_c580y + 4 ~ "black")) 

prev_c580y_plot <- ggplot() +
  geom_line(data=ex %>% mutate(N = n+c580y), aes(year, predict_stan_prev_c580y, color = "true"), linewidth = 1) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev_580y*100), color = ex_pt$point_col) +
  ggtitle(paste0("C580Y - ", prev_cutoff_perc, "% first year cutoff prevanlence")) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(values=c("#E69F00", "#56B4E9", "#0072B2", "grey"), name = "Mutations", labels = c("2 years", "3 years", "4 years", "true")) + 
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.direction = "vertical",
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)
  ) +  labs(color = NULL)

################ PLOT FOR R539T ################
df_pred <- df_predict_cutoff_allyear %>% 
  filter(year >= min_year +  pred_y, Locus == "R539T")  
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed_539t), nobs_r539t > numofobs, country %in% unique(df_pred$country))
ex_pt <- pfk7_data %>% 
  filter(nobs_r539t > numofobs, country %in% unique(df_pred$country)) %>%
  mutate(point_col = case_when(year >= min_year_r539t + 2 & year <= min_year_r539t + 2 ~ "#E69F00",
                             year > min_year_r539t + 2 & year <= min_year_r539t + 3 ~ "#56B4E9",
                              year > min_year_r539t + 3 & year <= min_year_r539t + 4 ~ "#0072B2",
                             year > min_year_r539t + 4 ~ "black")) 
prev_r539t_plot <- ggplot() +
  geom_line(data=ex %>% mutate(N = n+r539t), aes(year, predict_stan_prev_r539t, color = "true")) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev_539t*100), color = ex_pt$point_col) +
  ggtitle(paste0("R539T - ", prev_cutoff_perc, "% first year cutoff prevanlence")) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(values=c("#E69F00", "#56B4E9", "#0072B2", "grey"), name = "Mutations", labels = c("2 years", "3 years", "4 years", "true")) + 
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.direction = "vertical",
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)
  ) +  labs(color = NULL)

################ PLOT FOR ALL KELCH ################
df_pred <- df_predict_cutoff_allyear %>% 
  filter(year >= min_year +  pred_y, Locus == "all_kelch")  
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed_all_kelch), nobs_kelch > numofobs, country %in% unique(df_pred$country))
ex_pt <- pfk7_data %>% 
  filter(nobs_kelch > numofobs, country %in% unique(df_pred$country)) %>%
  mutate(point_col = case_when(year >= min_year_all_kelch + 2 & year <= min_year_all_kelch + 2 ~ "#E69F00",
                             year > min_year_all_kelch + 2 & year <= min_year_all_kelch + 3 ~ "#56B4E9",
                              year > min_year_all_kelch + 3 & year <= min_year_all_kelch + 4 ~ "#0072B2",
                             year > min_year_all_kelch + 4 ~ "black")) 
prev_all_kelch_plot <- ggplot() +
  geom_line(data=ex %>% mutate(N = n+all_kelch), aes(year, predict_stan_prev_all_kelch, color = "true")) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev_all_kelch*100), color = ex_pt$point_col) +
  ggtitle(paste0("PfK13 - ", prev_cutoff_perc, "% first year cutoff prevanlence")) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(values=c("#E69F00", "#56B4E9", "#0072B2", "grey"), name = "Mutations", labels = c("2 years", "3 years", "4 years", "true")) + 
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.direction = "vertical",
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)
  ) +  labs(color = NULL)
```

### Saving plots
```{r}
################ PLOT FOR C580Y ################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_cutoff_firstobs/SEAsia_pred_C580Y_",
    prev_cutoff_perc,
    "prev_pred.png"
  ),
  prev_c580y_plot,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_cutoff_firstobs/SEAsia_pred_C580Y_",
    prev_cutoff_perc,
    "prev_pred.pdf"
  ),
  prev_c580y_plot,
  width = 8,
  height = 5,
  dpi = 700
)

################ PLOT FOR R539T ################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_cutoff_firstobs/SEAsia_pred_R539T_",
    prev_cutoff_perc,
    "prev_pred.png"
  ),
  prev_r539t_plot,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_cutoff_firstobs/SEAsia_pred_R539T_",
    prev_cutoff_perc,
    "prev_pred.pdf"
  ),
  prev_r539t_plot,
  width = 8,
  height = 5,
  dpi = 700
)

################ PLOT FOR ALL KELCH ################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_cutoff_firstobs/SEAsia_pred_PfK13_",
    prev_cutoff_perc,
    "prev_pred.png"
  ),
  prev_all_kelch_plot,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_cutoff_firstobs/SEAsia_pred_PfK13_",
    prev_cutoff_perc,
    "prev_pred.pdf"
  ),
  prev_all_kelch_plot,
  width = 8,
  height = 5,
  dpi = 700
)
```

## Based on the first 2, 3, and 4 years with prevalence cut off averaged per country
```{r}
pred_year <- c(2, 3, 4)
prev_cutoff <- 0.2

for (i in pred_year) {
  #------ Model prediction for C580Y ------
  data_c580y <- pfk7_data %>% 
    filter(nobs_c580y > numofobs, year >= min_year_c580y & year <= min_year_c580y + i) %>%
    group_by(country) %>%
    filter(mean(prev_580y) <= 0.2) 
  
  c580y_pred <- rstanarm::stan_glmer(
    lrsmed_580y ~ adj_year + (1 + adj_year | country),
    data = data_c580y,
    weights = wt_med_580y,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs_c580y > numofobs, is.finite(pfk7_data$lrsmed_580y), country %in% data_c580y$country) %>% # this is for c580y model
    mutate(Locus = "C580Y") %>%
    group_by(country, Locus) %>%  # we group by country and Locus
    complete(year = seq(min(min_year_c580y) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, country, min_year_c580y, Locus) %>% # select just the columns needed for the model
    mutate(min_year_c580y = replace(min_year_c580y, is.na(min_year_c580y), 0)) %>%
    group_by(country) %>%
    distinct(year, .keep_all = TRUE)
  
  new_data <- new_data %>%
    group_by(country, Locus) %>%
    mutate(adj_year = year - max(min_year_c580y),
           min_year = min_year_c580y) %>%
    select(!min_year_c580y) %>% 
    arrange(year)
  
  predictions <-
    rstanarm::posterior_predict(c580y_pred, type = "response", newdata = new_data) %>% colMeans
  new_data$predict <- predictions
  
  df_predict <- new_data
  
  #------ Model prediction for R539T ------
  data_r539t <- pfk7_data %>% filter(nobs_r539t > numofobs, year >= min_year_r539t & year <= min_year_r539t + i) %>%
    group_by(country) %>%
    filter(mean(prev_539t) <= 0.2)

  r539t_pred <- rstanarm::stan_glmer(
    lrsmed_539t ~ adj_year + (1 + adj_year | country),
    data = data_r539t,
    weights = wt_med_539t,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs_r539t > numofobs, is.finite(pfk7_data$lrsmed_539t), country %in% data_r539t$country) %>% # this is for r539t model
    mutate(Locus = "R539T") %>%
    group_by(country, Locus) %>%  # we group by country and Locus
    complete(year = seq(min(min_year_r539t) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, country, min_year_r539t, Locus) %>% # select just the columns needed for the model
    mutate(min_year_r539t = replace(min_year_r539t, is.na(min_year_r539t), 0)) %>%
    group_by(country) %>%
    distinct(year, .keep_all = TRUE)
  
  new_data <- new_data %>%
    group_by(country, Locus) %>%
    mutate(adj_year = year - max(min_year_r539t),
           min_year = min_year_r539t) %>%
    select(!min_year_r539t) %>% 
    arrange(year)
  
  predictions <-
    rstanarm::posterior_predict(r539t_pred, type = "response", newdata = new_data) %>% colMeans
  new_data$predict <- predictions
  
  df_predict <- rbind(df_predict, new_data)
  
  #------ Model prediction for combined PfK13 mutations ------
  data_all_kelch <- pfk7_data %>% filter(nobs_kelch > numofobs, year >= min_year_all_kelch & year <= min_year_all_kelch + i) %>%
    group_by(country) %>%
    filter(mean(prev_all_kelch) <= 0.2)
  
  all_kelch_pred <- rstanarm::stan_glmer(
    lrsmed_all_kelch ~ adj_year + (1 + adj_year | country),
    data = data_all_kelch,
    weights = wt_med_all_kelch,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs_kelch > numofobs, is.finite(pfk7_data$lrsmed_all_kelch), country %in% data_all_kelch$country) %>% # this is for c469Y model
    mutate(Locus = "all_kelch") %>%
    group_by(country, Locus) %>% # we group by country and Locus
    complete(year = seq(min(min_year_all_kelch) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, country, min_year_all_kelch, Locus) %>% # select just the columns needed for the model
    mutate(min_year_all_kelch = replace(min_year_all_kelch, is.na(min_year_all_kelch), 0)) %>%
    group_by(country) %>%
    distinct(year, .keep_all = TRUE)
    
  
  new_data <- new_data %>%
    group_by(country, Locus) %>%
    mutate(adj_year = year - max(min_year_all_kelch),
           min_year = min_year_all_kelch) %>%
    select(!min_year_all_kelch) %>% 
    arrange(year)
  
  predictions <-
    rstanarm::posterior_predict(all_kelch_pred, type = "response", newdata = new_data) %>% colMeans
  new_data$predict <- predictions
  
  df_predict <- rbind(df_predict, new_data)
  
  df_predict <-
    df_predict %>% group_by(country, Locus) %>% mutate(min_year = replace_na(min_year, 0),
                                                        min_year = max(min_year)) %>% mutate(label = paste0(i, "year"),  pred_y = i)
  
  #Assigning df_predict to variables
  var_name <- paste0("df_predict_avg_", i, "year")
  assign(var_name, df_predict)
}

#combine forecasting predictions for all years
df_predict_avg_allyear <- rbind(df_predict_avg_2year, df_predict_avg_3year, df_predict_avg_4year)
```

### Plotting forecasting of predictions for the first 2, 3, and 4 years with avg of prevalence
```{r}
prev_cutoff_perc <- prev_cutoff *100

################ PLOT FOR C580Y ################
df_pred <- df_predict_avg_allyear %>% 
  filter(year >= min_year + pred_y, Locus == "C580Y") 
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed_580y), nobs_c580y > numofobs, country %in% unique(df_pred$country))
ex_pt <- pfk7_data %>% 
  filter(nobs_c580y > numofobs, country %in% unique(df_pred$country)) %>%
  mutate(point_col = case_when(year >= min_year_c580y + 2 & year <= min_year_c580y + 2 ~ "#E69F00",
                               year > min_year_c580y + 2 & year <= min_year_c580y + 3 ~ "#56B4E9",
                                year > min_year_c580y + 3 & year <= min_year_c580y + 4 ~ "#0072B2",
                               year > min_year_c580y + 4 ~ "black")) 
prev_c580y_plot <- 
  ggplot() +
  geom_line(data=ex %>% mutate(N = n+c580y), aes(year, predict_stan_prev_c580y, color = "true"), linewidth = 1) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev_580y*100), color = ex_pt$point_col) +
  ggtitle(paste0("C580Y - ", prev_cutoff_perc, "% avg prevanlence")) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    name = "Mutations",
    labels = c("2 years", "3 years", "4 years", "true")
  ) + 
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.direction = "vertical",
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)
  ) +  labs(color = NULL)


################ PLOT FOR R539T ################
df_pred <- df_predict_avg_allyear %>% 
  filter(year >= min_year +  pred_y, Locus == "R539T")  
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed_539t), nobs_r539t > numofobs, country %in% unique(df_pred$country))
ex_pt <- pfk7_data %>% 
  filter(nobs_r539t > numofobs, country %in% unique(df_pred$country)) %>%
  mutate(point_col = case_when(year >= min_year_r539t + 2 & year <= min_year_r539t + 2 ~ "#E69F00",
                             year > min_year_r539t + 2 & year <= min_year_r539t + 3 ~ "#56B4E9",
                              year > min_year_r539t + 3 & year <= min_year_r539t + 4 ~ "#0072B2",
                             year > min_year_r539t + 4 ~ "black")) 
prev_r539t_plot <- 
  ggplot() +
  geom_line(data=ex %>% mutate(N = n+r539t), aes(year, predict_stan_prev_r539t, color = "true")) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev_539t*100), color = ex_pt$point_col) +
  ggtitle(paste0("R539T - ", prev_cutoff_perc, "% avg prevanlence")) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    name = "Mutations",
    labels = c("2 years", "3 years", "4 years", "true")
  ) +
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.direction = "vertical",
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)
  ) +  labs(color = NULL)

################ PLOT FOR ALL KELCH ################
df_pred <- df_predict_avg_allyear %>% filter(year >= min_year +  pred_y, Locus == "all_kelch")  
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed_all_kelch), nobs_kelch > numofobs, country %in% unique(df_pred$country))
ex_pt <- pfk7_data %>% 
  filter(nobs_kelch > numofobs, country %in% unique(df_pred$country)) %>%
  mutate(point_col = case_when(year >= min_year_all_kelch + 2 & year <= min_year_all_kelch + 2 ~ "#E69F00",
                             year > min_year_all_kelch + 2 & year <= min_year_all_kelch + 3 ~ "#56B4E9",
                              year > min_year_all_kelch + 3 & year <= min_year_all_kelch + 4 ~ "#0072B2",
                             year > min_year_all_kelch + 4 ~ "black")) 
prev_all_kelch_plot <- 
  ggplot() +
  geom_line(data=ex %>% mutate(N = n+all_kelch), aes(year, predict_stan_prev_all_kelch, color = "true")) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev_all_kelch*100), color = ex_pt$point_col) +
   ggtitle(paste0("PfK13 - ", prev_cutoff_perc, "% avg prevanlence")) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    name = "Mutations",
    labels = c("2 years", "3 years", "4 years", "true")
  ) + 
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.direction = "vertical",
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)
  ) +  labs(color = NULL)
```

### Saving plots
```{r}
################ PLOT FOR C580Y ################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_avg/SEAsia_pred_C580Y_",
    prev_cutoff_perc,
    "avg_prev_pred.png"
  ),
  prev_c580y_plot,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_avg/SEAsia_pred_C580Y_",
    prev_cutoff_perc,
    "avg_prev_pred.pdf"
  ),
  prev_c580y_plot,
  width = 8,
  height = 5,
  dpi = 700
)

################ PLOT FOR R539T ################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_avg/SEAsia_pred_R539T_",
    prev_cutoff_perc,
    "avg_prev_pred.png"
  ),
  prev_r539t_plot,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_avg/SEAsia_pred_R539T_",
    prev_cutoff_perc,
    "avg_prev_pred.pdf"
  ),
  prev_r539t_plot,
  width = 8,
  height = 5,
  dpi = 700
)

################ PLOT FOR ALL KELCH ################
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_avg/SEAsia_pred_PfK13_",
    prev_cutoff_perc,
    "avg_prev_pred.png"
  ),
  prev_all_kelch_plot,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_avg/SEAsia_pred_PfK13_",
    prev_cutoff_perc,
    "avg_prev_pred.pdf"
  ),
  prev_all_kelch_plot,
  width = 8,
  height = 5,
  dpi = 700
)
```

# Metric of prediction
## Pf7 Data preprocessing
```{r}
d1 <-
  pfk7_data %>% select(
    country,
    year,
    min_year_c580y,
    c580y,
    nobs_c580y,
    n,
    predict_stan_c580y,
    predict_stan_prev_c580y) %>% 
  mutate(Locus = "C580Y") %>% 
  rename(
    x = c580y,
    nobs = nobs_c580y,
    min_year = min_year_c580y,
    predict_stan = predict_stan_c580y,
    predict_stan_prev = predict_stan_prev_c580y
  )
d2 <-
  pfk7_data %>% select(
    country,
    year,
    min_year_r539t,
    r539t,
    nobs_r539t,
    n,
    predict_stan_r539t,
    predict_stan_prev_r539t) %>% 
  mutate(Locus = "R539T") %>% 
  rename(
    x = r539t,
    nobs = nobs_r539t,
    min_year = min_year_r539t,
    predict_stan = predict_stan_r539t,
    predict_stan_prev = predict_stan_prev_r539t
  )
d3 <-
  pfk7_data %>% select(
    country,
    year,
    min_year_all_kelch,
    all_kelch,
    nobs_kelch,
    n,
    predict_stan_all_kelch,
    predict_stan_prev_all_kelch) %>% 
  mutate(Locus = "all_kelch") %>% 
  rename(
    x = all_kelch,
    nobs = nobs_kelch,
    min_year = min_year_all_kelch,
    predict_stan = predict_stan_all_kelch,
    predict_stan_prev = predict_stan_prev_all_kelch
  )

true <- rbind(d1, d2, d3)

corr_df_cutoff <- NULL
for(l in unique(df_predict_cutoff_allyear$label)) {
  pred <- df_predict_cutoff_allyear %>%
    filter(label == l) %>%
    arrange(label, Locus, country, year) %>%
    mutate(val = paste0(year, country, Locus, min_year)) %>%
    rename(p_pred = predict)
  true <- true %>%
    mutate(val = paste0(year, country, Locus, min_year)) %>%
    filter(val %in% pred$val)
  pred <- pred %>% filter(val %in% true$val)
  df <- cbind(true, pred$p_pred, pred$label)
  colnames(df)[ncol(df)-1] <- "p_pred"
  colnames(df)[ncol(df)] <- "label"
  corr_df_cutoff <- rbind(corr_df_cutoff, df)
}

true <- rbind(d1, d2, d3)
corr_df_avg <- NULL
for(l in unique(df_predict_avg_allyear$label)) {
  pred <- df_predict_avg_allyear %>%
    filter(label == l) %>%
    arrange(label, Locus, country, year) %>%
    mutate(val = paste0(year, country, Locus, min_year)) %>%
    rename(p_pred = predict)
  true <- true %>%
    mutate(val = paste0(year, country, Locus, min_year)) %>%
    filter(val %in% pred$val)
  pred <- pred %>% filter(val %in% true$val)
  df <- cbind(true, pred$p_pred, pred$label)
  colnames(df)[ncol(df)-1] <- "p_pred"
  colnames(df)[ncol(df)] <- "label"
  corr_df_avg <- rbind(corr_df_avg, df)
}

corr_df_cutoff <- corr_df_cutoff %>% 
  mutate(p_pred_prev = exp(p_pred) * 100 / (1 + exp(p_pred)))

```
### Plotting
```{r}
######## Correlation plot for 20% cutoff in first year ######## 
correlation_plot_cutoff <- ggplot(corr_df_cutoff %>% filter(is.finite(predict_stan_prev)), 
                                  aes(x = predict_stan_prev, y = p_pred_prev, color = country, group = country)) +
  geom_point() +
  geom_smooth(method=lm, se=FALSE) +
  stat_cor(aes(color = country), label.x = 40, , size = 2) +
  facet_wrap(~ Locus + label) +
  xlab("true") +
  ylab("predicted") +
  ggtitle("20% cutoff in first year") +
  theme_bw() +
  theme(
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.direction = "vertical",
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)
  ) +  labs(color = NULL)

######## Correlation plot for 20% avg ########
correlation_plot_avg <- ggplot(corr_df_avg %>% filter(is.finite(predict_stan_prev)),
                               aes(x = predict_stan_prev, y = exp(p_pred) * 100 / (1 + exp(p_pred)), color = country)) +
  geom_point() +
  geom_smooth(method=lm, se=FALSE) +
  stat_cor(aes(color = country), label.x = 30, , size = 2) +
  facet_wrap(~ Locus + label) +
  xlab("true") +
  ylab("predicted") +
  ggtitle("20% average across years") +
  theme_bw() +
  theme(
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.direction = "vertical",
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)
  ) +  labs(color = NULL)
```

### Saving plots
```{r}
######## Correlation plot for 20% cutoff in first year ######## 
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_cutoff_firstobs/SEAsia_correlation_",
    prev_cutoff_perc,
    "cutoff_prev.png"
  ),
  correlation_plot_cutoff,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_cutoff_firstobs/SEAsia_correlation_",
    prev_cutoff_perc,
    "cutoff_prev.pdf"
  ),
  correlation_plot_cutoff,
  width = 8,
  height = 5,
  dpi = 700
)

######## Correlation plot for 20% avg ########
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_avg/SEAsia_correlation_",
    prev_cutoff_perc,
    "avg_prev.png"
  ),
  correlation_plot_avg,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_avg/SEAsia_correlation_",
    prev_cutoff_perc,
    "avg_prev.pdf"
  ),
  correlation_plot_avg,
  width = 8,
  height = 5,
  dpi = 700
)
```

## R539T mutation
```{r}
correlation_plot_cutoff <- ggplot(corr_df_cutoff %>% filter(is.finite(predict_stan_prev), Locus == "R539T"), 
                                  aes(x = predict_stan_prev, y = p_pred_prev, color = country, group = country)) +
  geom_point() +
  geom_smooth(method=lm, se=FALSE) +
  #stat_cor(aes(color = country), label.x = 40, , size = 2) +
  facet_wrap(~ Locus + label) +
  xlab("true") +
  ylab("predicted") +
  ggtitle("20% cutoff in first year") +
  theme_bw() +
  theme(
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.direction = "vertical",
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)
  ) +  labs(color = NULL)

ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_cutoff_firstobs/SEAsia_correlation_R539T_",
    prev_cutoff_perc,
    "cutoff_prev.png"
  ),
  correlation_plot_cutoff,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_cutoff_firstobs/SEAsia_correlation_R539T_",
    prev_cutoff_perc,
    "cutoff_prev.pdf"
  ),
  correlation_plot_cutoff,
  width = 8,
  height = 5,
  dpi = 700
)

## Correlation plot for 20% avg
correlation_plot_avg <- ggplot(corr_df_avg %>% filter(is.finite(predict_stan_prev), Locus == "R539T"),
                               aes(x = predict_stan_prev, y = exp(p_pred) * 100 / (1 + exp(p_pred)), color = country)) +
  geom_point() +
  geom_smooth(method=lm, se=FALSE) +
  facet_wrap(~ Locus + label) +
  xlab("true") +
  ylab("predicted") +
  ggtitle("20% average across years") +
  theme_bw() +
  theme(
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    legend.title = element_text(size = 12),
    legend.direction = "vertical",
    legend.position = "right",
    plot.title = element_text(hjust = 0.5)
  ) +  labs(color = NULL)

ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_avg/SEAsia_correlation_R539T_",
    prev_cutoff_perc,
    "avg_prev.png"
  ),
  correlation_plot_avg,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(
    "figures/predictions/SE_Asia/per_country/20_avg/SEAsia_correlation_R539T_",
    prev_cutoff_perc,
    "avg_prev.pdf"
  ),
  correlation_plot_avg,
  width = 8,
  height = 5,
  dpi = 700
)
```
