---
title: "Kelch PfK7 Prediction for 2,3,4 years"
output: html_document
date: "2023-03-16"
---

```{r setup, include=FALSE}
library(lme4)
library(nlme)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(scales)
library(tidyverse)
library(cowplot)
library(tabulizer)
library(RColorBrewer)
library(tidyverse) # ggplot2, dplyr, tidyr, readr, purrr, tibble
library(rnaturalearth)
library(rnaturalearthdata)
library(sf) #see ubuntu issues here: https://rtask.thinkr.fr/installation-of-r-4-0-on-ubuntu-20-04-lts-and-tips-for-spatial-packages/
library(ggspatial)
library(scatterpie)
library(scales)
library (ggforce)
library (ggmap)
library(rstan)
library(gt)
## install.packages("rstan", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))

```

# Load data
```{r}
#load data
pfk7_data <- read.table("data/data-derived/pfk7_data.txt")
#set the limit of number of observations
numofobs <- 2

pfk7_data <- pfk7_data %>%
  group_by(District) %>%
  mutate(min_year_c580y = min(year[c580y>0]), min_year_r539t = min(year[r539t>0]), min_year_all_kelch = min(year[all_kelch>0])) %>%
  ungroup 
```

# Bayesian GMM with slopes and intercepts
```{r}
# Have a read through rstanarm vignettes and guides on how it works in comparison to lme4
# ---- Model for c580y -----
c580y_stanmod <- rstanarm::stan_glmer(
  lrsmed_580y ~ adj_year + (1 + adj_year | District),
  data = pfk7_data %>% filter(nobs_c580y > numofobs),
  weights = wt_med_580y,
  adapt_delta = 0.9975
)

vals <- summary(c580y_stanmod$stanfit)$summary[, 1]
vals <- vals[grep("^b", names(vals))]
ranef_c580y_stanmod <-
  data.frame("Intercepts" = vals[seq(1, length(vals), 2)],
             "Slopes" = vals[seq(2, length(vals), 2)])
ranef_c580y_stanmod$mutation <-
  rep("c580y", dim(ranef_c580y_stanmod)[1])

# ---- Model for r539t -----

r539t_stanmod <- rstanarm::stan_glmer(
  lrsmed_539t ~ adj_year + (1 + adj_year | District),
  data = pfk7_data %>% filter(nobs_r539t > numofobs),
  weights = wt_med_539t,
  adapt_delta = 0.9975
)

vals <- summary(r539t_stanmod$stanfit)$summary[, 1]
vals <- vals[grep("^b", names(vals))]
ranef_r539t_stanmod <-
  data.frame("Intercepts" = vals[seq(1, length(vals), 2)],
             "Slopes" = vals[seq(2, length(vals), 2)])
ranef_r539t_stanmod$mutation <-
  rep("r539t", dim(ranef_r539t_stanmod)[1])

# ---- Model for combined kelch -----

all_kelch_stanmod <- rstanarm::stan_glmer(
  lrsmed_all_kelch ~ adj_year + (1 + adj_year | District),
  data = pfk7_data %>% filter(nobs_kelch > numofobs),
  weights = wt_med_all_kelch,
  adapt_delta = 0.9975
)


vals <- summary(all_kelch_stanmod$stanfit)$summary[, 1]
vals <- vals[grep("^b", names(vals))]
ranef_all_kelch_stanmod <-
  data.frame("Intercepts" = vals[seq(1, length(vals), 2)],
             "Slopes" = vals[seq(2, length(vals), 2)])
ranef_all_kelch_stanmod$mutation <-
  rep("all_kelch", dim(ranef_all_kelch_stanmod)[1])

ranef_stanmod <-
  rbind(ranef_c580y_stanmod,
        ranef_all_kelch_stanmod,
        ranef_r539t_stanmod)
ranef_stanmod$site <-
  str_replace_all(rownames(ranef_stanmod), "\\[|\\]", "")
ranef_stanmod$site <-
  str_replace_all(ranef_stanmod$site, "\\s*\\([^\\)]+\\)", "")
ranef_stanmod$site <- str_remove(ranef_stanmod$site, "b District:")
ranef_stanmod$site <- str_remove(ranef_stanmod$site, "1")


``` 
## GMM posterior
```{r}
#  get model predictions for plotting
pfk7_data$predict_stan_c580y <- NA
pfk7_data$predict_stan_r539t <- NA
pfk7_data$predict_stan_all_kelch <- NA

pfk7_data$predict_stan_c580y[is.finite(pfk7_data$lrsmed_580y) & pfk7_data$nobs_c580y > numofobs] <-  rstanarm::posterior_predict(c580y_stanmod, type = "response") %>% colMeans
pfk7_data$predict_stan_r539t[is.finite(pfk7_data$lrsmed_539t) & pfk7_data$nobs_r539t > numofobs] <-  rstanarm::posterior_predict(r539t_stanmod, type = "response") %>% colMeans
pfk7_data$predict_stan_all_kelch[is.finite(pfk7_data$lrsmed_all_kelch) & pfk7_data$nobs_kelch > numofobs] <-  rstanarm::posterior_predict(all_kelch_stanmod, type = "response") %>% colMeans
```

## Obtain confidence interval of and posterior of posterior for each mutation
```{r}
#  get model predictions for plotting
pfk7_data$conf.low_c580y <- NA
pfk7_data$conf.high_c580y <- NA
pfk7_data$conf.low_r539t <- NA
pfk7_data$conf.high_r539t <- NA
pfk7_data$conf.low_all_kelch <- NA
pfk7_data$conf.high_all_kelch <- NA

c580y_conf <- rstanarm::posterior_predict(c580y_stanmod, type = "response") %>% apply(2, quantile, prob = (c(0.025, 0.975)))
r539t_conf <- rstanarm::posterior_predict(r539t_stanmod, type = "response") %>% apply(2, quantile, prob = (c(0.025, 0.975)))
all_kelch_conf <- rstanarm::posterior_predict(all_kelch_stanmod, type = "response") %>% apply(2, quantile, prob = (c(0.025, 0.975)))

# here just add predictions  for the c469Y rows
pfk7_data$conf.low_c580y[is.finite(pfk7_data$lrsmed_580y) & pfk7_data$nobs_c580y > numofobs] <- c580y_conf[1,]
pfk7_data$conf.low_r539t[is.finite(pfk7_data$lrsmed_539t) & pfk7_data$nobs_r539t > numofobs] <- r539t_conf[1,]
pfk7_data$conf.low_all_kelch[is.finite(pfk7_data$lrsmed_all_kelch) & pfk7_data$nobs_kelch > numofobs] <- all_kelch_conf[1,]

pfk7_data$conf.high_c580y[is.finite(pfk7_data$lrsmed_580y) & pfk7_data$nobs_c580y > numofobs] <- c580y_conf[2,]
pfk7_data$conf.high_r539t[is.finite(pfk7_data$lrsmed_539t) & pfk7_data$nobs_r539t > numofobs] <- r539t_conf[2,]
pfk7_data$conf.high_all_kelch[is.finite(pfk7_data$lrsmed_all_kelch) & pfk7_data$nobs_kelch > numofobs] <- all_kelch_conf[2,]
```

## Obtain GMM posterior for each mutation in prevalence scale
```{r}
# Plot the predictions in each site with only Bayesian
#convert to prevalence scale
#  get model predictions for plotting
pfk7_data$predict_stan_c580y <- NA
pfk7_data$predict_stan_r539t <- NA
pfk7_data$predict_stan_all_kelch <- NA

pfk7_data$predict_stan_c580y[is.finite(pfk7_data$lrsmed_580y) & pfk7_data$nobs_c580y > numofobs] <-  rstanarm::posterior_predict(c580y_stanmod, type = "response") %>% colMeans
pfk7_data$predict_stan_r539t[is.finite(pfk7_data$lrsmed_539t) & pfk7_data$nobs_r539t > numofobs] <-  rstanarm::posterior_predict(r539t_stanmod, type = "response") %>% colMeans
pfk7_data$predict_stan_all_kelch[is.finite(pfk7_data$lrsmed_all_kelch) & pfk7_data$nobs_kelch > numofobs] <-  rstanarm::posterior_predict(all_kelch_stanmod, type = "response") %>% colMeans

pfk7_data$predict_stan_prev_c580y <- exp(pfk7_data$predict_stan_c580y)*100/(1+exp(pfk7_data$predict_stan_c580y))
pfk7_data$predict_stan_prev_r539t <- exp(pfk7_data$predict_stan_r539t)*100/(1+exp(pfk7_data$predict_stan_r539t))
pfk7_data$predict_stan_prev_all_kelch <- exp(pfk7_data$predict_stan_all_kelch)*100/(1+exp(pfk7_data$predict_stan_all_kelch))

pfk7_data$conf.high_prev_c580y <- exp(pfk7_data$conf.high_c580y)*100/(1+exp(pfk7_data$conf.high_c580y))
pfk7_data$conf.high_prev_r539t <- exp(pfk7_data$conf.high_r539t)*100/(1+exp(pfk7_data$conf.high_r539t))
pfk7_data$conf.high_prev_all_kelch <- exp(pfk7_data$conf.high_all_kelch)*100/(1+exp(pfk7_data$conf.high_all_kelch))

pfk7_data$conf.low_prev_c580y <- exp(pfk7_data$conf.low_c580y)*100/(1+exp(pfk7_data$conf.low_c580y))
pfk7_data$conf.low_prev_r539t <- exp(pfk7_data$conf.low_r539t)*100/(1+exp(pfk7_data$conf.low_r539t))
pfk7_data$conf.low_prev_all_kelch <- exp(pfk7_data$conf.low_all_kelch)*100/(1+exp(pfk7_data$conf.low_all_kelch))
```

# Forecasting Selection 

## Based on the first 2, 3, and 4 years
```{r}
pred_year <- c(2, 3, 4)

for (i in pred_year) {
  #------ Model prediction for C580Y ------
  c580y_pred <- rstanarm::stan_glmer(
    lrsmed_580y ~ adj_year + (1 + adj_year | District),
    data = pfk7_data %>% filter(
      nobs_c580y > numofobs,
      year >= min_year_c580y & year <= min_year_c580y + i
    ),
    weights = wt_med_580y,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs_c580y > numofobs, is.finite(pfk7_data$lrsmed_580y)) %>% # this is for c469Y model
    mutate(Locus = "C580Y") %>%
    group_by(country, District, Locus) %>% # we group by the District and Locus
    complete(year = seq(min(min_year_c580y) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    #mutate(adj_year = year - min_year_c580y) %>%
    select(adj_year, year, country, min_year_c580y, District, Locus) %>% # select just the columns needed for the model
    mutate(min_year_c580y = replace(min_year_c580y, is.na(min_year_c580y), 0))
  
  new_data <- new_data %>%
    group_by(country, District, Locus) %>%
    mutate(adj_year = year - max(min_year_c580y),
           min_year = min_year_c580y) %>%
    select(!min_year_c580y)
  
  predictions <-
    rstanarm::posterior_predict(c580y_pred, type = "response", newdata = new_data) %>% colMeans
  new_data$predict <- predictions
  
  df_predict <- new_data
  
  #------ Model prediction for R539T ------
  
  r539t_pred <- rstanarm::stan_glmer(
    lrsmed_539t ~ adj_year + (1 + adj_year | District),
    data = pfk7_data %>% filter(
      nobs_r539t > numofobs,
      year >= min_year_r539t & year <= min_year_r539t + i
    ),
    weights = wt_med_539t,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs_r539t > numofobs, is.finite(pfk7_data$lrsmed_539t)) %>% # this is for r539t model
    mutate(Locus = "R539T") %>%
    group_by(country, District, Locus) %>%  # we group by the District and Locus
    complete(year = seq(min(min_year_r539t) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    #mutate(adj_year = year - min_year_c580y) %>%
    select(adj_year, year, country, min_year_r539t, District, Locus) %>% # select just the columns needed for the model
    mutate(min_year_r539t = replace(min_year_r539t, is.na(min_year_r539t), 0))
  
  new_data <- new_data %>%
    group_by(country, District, Locus) %>%
    mutate(adj_year = year - max(min_year_r539t),
           min_year = min_year_r539t) %>%
    select(!min_year_r539t)
  
  predictions <-
    rstanarm::posterior_predict(r539t_pred, type = "response", newdata = new_data) %>% colMeans
  new_data$predict <- predictions
  
  df_predict <- rbind(df_predict, new_data)
  
  #------ Model prediction for combined PfK13 mutations ------
  
  all_kelch_pred <- rstanarm::stan_glmer(
    lrsmed_all_kelch ~ adj_year + (1 + adj_year | District),
    data = pfk7_data %>% filter(
      nobs_kelch > numofobs,
      year >= min_year_all_kelch & year <= min_year_all_kelch + i
    ),
    weights = wt_med_580y,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs_kelch > numofobs, is.finite(pfk7_data$lrsmed_all_kelch)) %>% # this is for c469Y model
    mutate(Locus = "all_kelch") %>%
    group_by(country, District, Locus) %>% # we group by the District and Locus
    complete(year = seq(min(min_year_all_kelch) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    #mutate(adj_year = year - min_year_c580y) %>%
    select(adj_year, year, country, min_year_all_kelch, District, Locus) %>% # select just the columns needed for the model
    mutate(min_year_all_kelch = replace(min_year_all_kelch, is.na(min_year_all_kelch), 0))
  
  new_data <- new_data %>%
    group_by(country, District, Locus) %>%
    mutate(adj_year = year - max(min_year_all_kelch),
           min_year = min_year_all_kelch) %>%
    select(!min_year_all_kelch)
  
  predictions <-
    rstanarm::posterior_predict(all_kelch_pred, type = "response", newdata = new_data) %>% colMeans
  new_data$predict <- predictions
  
  df_predict <- rbind(df_predict, new_data)
  
  df_predict <-
    df_predict %>% group_by(District, Locus) %>% mutate(min_year = replace_na(min_year, 0),
                                                        min_year = max(min_year)) %>% mutate(label = paste0(i, "year"),  pred_y = i)
  
  #Assigning df_predict to variables
  var_name <- paste0("df_predict_", i, "year")
  assign(var_name, df_predict)
}

#combine forecasting predictions for all years
df_predict_allyear <- rbind(df_predict_2year, df_predict_3year, df_predict_4year)
```

### Ploting forecasting of predictions for the first 2, 3, and 4 years
```{r}
ex <- pfk7_data %>% filter(is.finite(lrsmed_580y), nobs_c580y > numofobs)
df_pred <- df_predict_allyear %>% filter(District %in% unique(ex$District), year >= min_year + pred_y, Locus == "C580Y") 
## PLOT FOR C580Y
prev_c580y_plot <- 
  ggplot() +
  geom_line(data=ex %>% mutate(N = n+c580y), aes(year, predict_stan_prev_c580y, color = "true"), linewidth = 1) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  #geom_vline(data=ex, aes(xintercept= min_year_c580y + pred_year), linetype = "dashed") +
  geom_point(data = ex, aes(x=year, y=prev_580y*100)) +
  ggtitle("C580Y") +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country + District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  theme(axis.line = element_line(), axis.text = element_text(size = 8), axis.title=element_text(size=12), legend.text=element_text(size=12), strip.text.x = element_text(size = 12), legend.title = element_text(size=12), legend.direction = "vertical", legend.position = "right", plot.title = element_text(hjust = 0.5)) +  labs(color=NULL)

ggsave("figures/predictions/SEAsia_pred_C580Y_pred.jpeg", prev_c580y_plot, width = 8, height = 5, dpi=700)

ex <- pfk7_data %>% filter(is.finite(lrsmed_539t), nobs_r539t > numofobs, year >= min_year_r539t)
df_pred <- df_predict_allyear %>% filter(District %in% unique(ex$District), year >= min_year +  pred_y, Locus == "R539T")  
prev_r539t_plot <- 
  ggplot() +
  geom_line(data=ex %>% mutate(N = n+r539t), aes(year, predict_stan_prev_r539t, color = "true")) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  #geom_vline(data=ex, aes(xintercept= min_year_r539t+ pred_year), linetype = "dashed") +
  geom_point(data = ex, aes(x=year, y=prev_539t*100)) +
  ggtitle("R539T") +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country + District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  theme(axis.line = element_line(), axis.text = element_text(size = 8), axis.title=element_text(size=12), legend.text=element_text(size=12), strip.text.x = element_text(size = 12), legend.title = element_text(size=12), legend.direction = "vertical", legend.position = "right", plot.title = element_text(hjust = 0.5)) +  labs(color=NULL)

ggsave("figures/predictions/SEAsia_pred_R539T_pred.jpeg", prev_r539t_plot, width = 8, height = 5, dpi=700)

ex <- pfk7_data %>% filter(is.finite(lrsmed_all_kelch), nobs_kelch > numofobs, year >= min_year_all_kelch)
df_pred <- df_predict_allyear %>% filter(District %in% unique(ex$District), year >= min_year +  pred_y, Locus == "all_kelch")  
prev_all_kelch_plot <- 
  ggplot() +
  geom_line(data=ex %>% mutate(N = n+all_kelch), aes(year, predict_stan_prev_all_kelch, color = "true")) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  #geom_vline(data=ex, aes(xintercept= min_year_all_kelch+ pred_year), linetype = "dashed") +
  geom_point(data = ex, aes(x=year, y=prev_all_kelch*100)) +
  ggtitle("PfK13") +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country + District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  theme(axis.line = element_line(), axis.text = element_text(size = 8), axis.title=element_text(size=12), legend.text=element_text(size=12), strip.text.x = element_text(size = 12), legend.title = element_text(size=12), legend.direction = "vertical", legend.position = "right", plot.title = element_text(hjust = 0.5)) +  labs(color=NULL)

ggsave("figures/predictions/SEAsia_pred_Pfk13_pred.jpeg", prev_all_kelch_plot, width = 8, height = 5, dpi=700)
```

## Based on the first 2, 3, and 4 years with prevalence cut off
```{r}
pred_year <- c(2, 3, 4)
prev_cutoff <- 0.2

for (i in pred_year) {
  #------ Model prediction for C580Y ------
  data_c580y <- pfk7_data %>% filter(nobs_c580y > numofobs,
                                     year >= min_year_c580y & year <= min_year_c580y + i)
  
  val <- data_c580y[data_c580y$year == data_c580y$min_year_c580y, ]
  selected_districts <- val$District[val$prev_580y <= prev_cutoff]
  
  data_c580y <-
    data_c580y %>% filter(District %in% selected_districts)
  
  c580y_pred <- rstanarm::stan_glmer(
    lrsmed_580y ~ adj_year + (1 + adj_year | District),
    data = data_c580y,
    weights = wt_med_580y,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs_c580y > numofobs, is.finite(pfk7_data$lrsmed_580y)) %>% # this is for c469Y model
    mutate(Locus = "C580Y") %>%
    group_by(country, District, Locus) %>% # we group by the District and Locus
    complete(year = seq(min(min_year_c580y) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    #mutate(adj_year = year - min_year_c580y) %>%
    select(adj_year, year, country, min_year_c580y, District, Locus) %>% # select just the columns needed for the model
    mutate(min_year_c580y = replace(min_year_c580y, is.na(min_year_c580y), 0))
  
  new_data <- new_data %>%
    group_by(country, District, Locus) %>%
    mutate(adj_year = year - max(min_year_c580y),
           min_year = min_year_c580y) %>%
    select(!min_year_c580y)
  
  predictions <-
    rstanarm::posterior_predict(c580y_pred, type = "response", newdata = new_data) %>% colMeans
  new_data$predict <- predictions
  
  df_predict <- new_data
  
  #------ Model prediction for R539T ------
  data_r539t <- pfk7_data %>% filter(nobs_r539t > numofobs,
                                     year >= min_year_r539t & year <= min_year_r539t + i)
  
  val <- data_r539t[data_r539t$year == data_r539t$min_year_r539t, ]
  selected_districts <- val$District[val$prev_539t <= prev_cutoff]
  
  data_r539t <-
    data_r539t %>% filter(District %in% selected_districts)
  
  r539t_pred <- rstanarm::stan_glmer(
    lrsmed_539t ~ adj_year + (1 + adj_year | District),
    data = data_r539t,
    weights = wt_med_539t,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs_r539t > numofobs, is.finite(pfk7_data$lrsmed_539t)) %>% # this is for r539t model
    mutate(Locus = "R539T") %>%
    group_by(country, District, Locus) %>%  # we group by the District and Locus
    complete(year = seq(min(min_year_r539t) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    #mutate(adj_year = year - min_year_c580y) %>%
    select(adj_year, year, country, min_year_r539t, District, Locus) %>% # select just the columns needed for the model
    mutate(min_year_r539t = replace(min_year_r539t, is.na(min_year_r539t), 0))
  
  new_data <- new_data %>%
    group_by(country, District, Locus) %>%
    mutate(adj_year = year - max(min_year_r539t),
           min_year = min_year_r539t) %>%
    select(!min_year_r539t)
  
  predictions <-
    rstanarm::posterior_predict(r539t_pred, type = "response", newdata = new_data) %>% colMeans
  new_data$predict <- predictions
  
  df_predict <- rbind(df_predict, new_data)
  
  #------ Model prediction for combined PfK13 mutations ------
  data_all_kelch<- pfk7_data %>% filter(nobs_kelch > numofobs,
                                     year >= min_year_all_kelch & year <= min_year_all_kelch + i)
  
  val <- data_all_kelch[data_all_kelch$year == data_all_kelch$min_year_all_kelch, ]
  selected_districts <- val$District[val$prev_all_kelch <= prev_cutoff]
  
  data_all_kelch <-
    data_all_kelch %>% filter(District %in% selected_districts)
  
  all_kelch_pred <- rstanarm::stan_glmer(
    lrsmed_all_kelch ~ adj_year + (1 + adj_year | District),
    data = data_all_kelch,
    weights = wt_med_580y,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs_kelch > numofobs, is.finite(pfk7_data$lrsmed_all_kelch)) %>% # this is for c469Y model
    mutate(Locus = "all_kelch") %>%
    group_by(country, District, Locus) %>% # we group by the District and Locus
    complete(year = seq(min(min_year_all_kelch) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    #mutate(adj_year = year - min_year_c580y) %>%
    select(adj_year, year, country, min_year_all_kelch, District, Locus) %>% # select just the columns needed for the model
    mutate(min_year_all_kelch = replace(min_year_all_kelch, is.na(min_year_all_kelch), 0))
  
  new_data <- new_data %>%
    group_by(country, District, Locus) %>%
    mutate(adj_year = year - max(min_year_all_kelch),
           min_year = min_year_all_kelch) %>%
    select(!min_year_all_kelch)
  
  predictions <-
    rstanarm::posterior_predict(all_kelch_pred, type = "response", newdata = new_data) %>% colMeans
  new_data$predict <- predictions
  
  df_predict <- rbind(df_predict, new_data)
  
  df_predict <-
    df_predict %>% group_by(District, Locus) %>% mutate(min_year = replace_na(min_year, 0),
                                                        min_year = max(min_year)) %>% mutate(label = paste0(i, "year"),  pred_y = i)
  
  #Assigning df_predict to variables
  var_name <- paste0("df_predict_", i, "year")
  assign(var_name, df_predict)
}

#combine forecasting predictions for all years
df_predict_allyear <- rbind(df_predict_2year, df_predict_3year, df_predict_4year)
```

### Plotting forecasting of predictions for the first 2, 3, and 4 years with prevalence cut off
```{r}
prev_cutoff_perc <- prev_cutoff *100
ex <- pfk7_data %>% filter(is.finite(lrsmed_580y), nobs_c580y > numofobs)
df_pred <- df_predict_allyear %>% filter(District %in% unique(ex$District), year >= min_year + pred_y, Locus == "C580Y") 
## PLOT FOR C580Y
prev_c580y_plot <- 
  ggplot() +
  geom_line(data=ex %>% mutate(N = n+c580y), aes(year, predict_stan_prev_c580y, color = "true"), linewidth = 1) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  #geom_vline(data=ex, aes(xintercept= min_year_c580y + pred_year), linetype = "dashed") +
  geom_point(data = ex, aes(x=year, y=prev_580y*100)) +
  ggtitle(paste0("C580Y - ", prev_cutoff_perc, "% prevanlence")) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country + District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  theme(axis.line = element_line(), axis.text = element_text(size = 8), axis.title=element_text(size=12), legend.text=element_text(size=12), strip.text.x = element_text(size = 12), legend.title = element_text(size=12), legend.direction = "vertical", legend.position = "right", plot.title = element_text(hjust = 0.5)) +  labs(color=NULL)

ggsave(paste0("figures/predictions/SEAsia_pred_C580Y_", prev_cutoff_perc, "prev_pred.jpeg"), prev_c580y_plot, width = 8, height = 5, dpi=700)

ex <- pfk7_data %>% filter(is.finite(lrsmed_539t), nobs_r539t > numofobs, year >= min_year_r539t)
df_pred <- df_predict_allyear %>% filter(District %in% unique(ex$District), year >= min_year +  pred_y, Locus == "R539T")  
prev_r539t_plot <- 
  ggplot() +
  geom_line(data=ex %>% mutate(N = n+r539t), aes(year, predict_stan_prev_r539t, color = "true")) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  #geom_vline(data=ex, aes(xintercept= min_year_r539t+ pred_year), linetype = "dashed") +
  geom_point(data = ex, aes(x=year, y=prev_539t*100)) +
  ggtitle(paste0("R539T - ", prev_cutoff_perc, "% prevanlence")) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country + District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  theme(axis.line = element_line(), axis.text = element_text(size = 8), axis.title=element_text(size=12), legend.text=element_text(size=12), strip.text.x = element_text(size = 12), legend.title = element_text(size=12), legend.direction = "vertical", legend.position = "right", plot.title = element_text(hjust = 0.5)) +  labs(color=NULL)

ggsave(paste0("figures/predictions/SEAsia_pred_R539T_", prev_cutoff_perc, "prev_pred.jpeg"), prev_c580y_plot, width = 8, height = 5, dpi=700)

ex <- pfk7_data %>% filter(is.finite(lrsmed_all_kelch), nobs_kelch > numofobs, year >= min_year_all_kelch)
df_pred <- df_predict_allyear %>% filter(District %in% unique(ex$District), year >= min_year +  pred_y, Locus == "all_kelch")  
prev_all_kelch_plot <- 
  ggplot() +
  geom_line(data=ex %>% mutate(N = n+all_kelch), aes(year, predict_stan_prev_all_kelch, color = "true")) + 
  geom_line(data=df_pred, aes(year, exp(predict)*100/(1+exp(predict)), group = label,color = label), linetype = "dashed") +
  #geom_vline(data=ex, aes(xintercept= min_year_all_kelch+ pred_year), linetype = "dashed") +
  geom_point(data = ex, aes(x=year, y=prev_all_kelch*100)) +
   ggtitle(paste0("PfK13 - ", prev_cutoff_perc, "% prevanlence")) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country + District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  theme(axis.line = element_line(), axis.text = element_text(size = 8), axis.title=element_text(size=12), legend.text=element_text(size=12), strip.text.x = element_text(size = 12), legend.title = element_text(size=12), legend.direction = "vertical", legend.position = "right", plot.title = element_text(hjust = 0.5)) +  labs(color=NULL)

ggsave(paste0("figures/predictions/SEAsia_pred_PfK13_", prev_cutoff_perc, "prev_pred.jpeg"), prev_c580y_plot, width = 8, height = 5, dpi=700)
```

