---
title: "Forecasting allele frequency SEA"
output: html_document
date: "2024-05-11"
---

```{r setup, include=FALSE}
library(cowplot)
library(dplyr)
library (ggforce)
library(ggplot2)
library(ggmap)
library(ggpubr)
library(ggspatial)
library(gt)
library(lme4)
library(Metrics)
library(nlme)
library(RColorBrewer)
library(rnaturalearth)
library(rnaturalearthdata)
library(rstan)
## install.packages("rstan", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))
library(scales)
library(scatterpie)
library(sf) #see ubuntu issues here: https://rtask.thinkr.fr/installation-of-r-4-0-on-ubuntu-20-04-lts-and-tips-for-spatial-packages/
library(tabulizer)
library(tidyverse)
library(tidyverse) # ggplot2, dplyr, tidyr, readr, purrr, tibble
```

#Load functions
```{r}
source("GLM_model_s_functions.R")
source("SEA_prediction_model_functions.R")
```
# Load data
```{r}
#set the limit of number of observations
numofobs <- 2
#load data
pfk7_data_unfiltered <- read.table("data/data-derived/pfk7_allele_frequency.txt") 

pfk7_data_filtered <- pfk7_data_unfiltered %>%
  filter(Locus != "other_K13") %>%
  group_by(Locus, District) %>%
  filter(nobs > numofobs) %>%
  arrange(Locus, District, year)

#----- C580Y -----
pfk7_data_580Y <- pfk7_data_filtered %>%
  filter(Locus == "C580Y",
         District %in% c("Preah Vihear", "Ratanakiri", "Tak"))

#----- K13 -----
pfk7_data_K13 <- pfk7_data_filtered %>%
  filter(Locus == "K13",
         District %in% c("Mandalay", "Preah Vihear", "Ratanakiri", "Tak"))

pfk7_C580Y_K13 <- rbind(pfk7_data_580Y, pfk7_data_K13)
```

# Bayesian GMM with slopes and intercepts
```{r}
# Have a read through rstanarm vignettes and guides on how it works in comparison to lme4
# ---- Model for c580y -----
C580Y <- GLM_model_mutant(pfk7_C580Y_K13, "C580Y", numofobs = 2)
c580y_stanmod <- C580Y$glmer
ranef_c580y_stanmod <- C580Y$ranef

# ---- Model for combined kelch -----
K13 <- GLM_model_mutant(pfk7_C580Y_K13, "K13", numofobs = 2)
K13_stanmod <- K13$glmer
ranef_K13_stanmod <- K13$ranef
``` 
## Posterior of the model
```{r}
#  get model predictions for plotting
pfk7_C580Y_K13$predict_stan <- NA

pfk7_C580Y_K13$predict_stan[is.finite(pfk7_C580Y_K13$lrsmed) & 
                                  pfk7_C580Y_K13$Locus == "C580Y" & 
                                  pfk7_C580Y_K13$nobs > numofobs] <- rstanarm::posterior_predict(c580y_stanmod, type = "response") %>% colMeans
pfk7_C580Y_K13$predict_stan[is.finite(pfk7_C580Y_K13$lrsmed) & 
                                  pfk7_C580Y_K13$Locus == "K13" & 
                                  pfk7_C580Y_K13$nobs > numofobs] <- rstanarm::posterior_predict(K13_stanmod, type = "response") %>% colMeans
```

## Convert prediction to allele frequency scale
```{r}
#convert confidence of forecasting into pervalence
pfk7_C580Y_K13 <- pfk7_C580Y_K13 %>%
  mutate(predict_stan_freq = exp(predict_stan)/(1+exp(predict_stan)))
```

# Forecasting allele frequency
## First year 50% cutoff based on the first 2, 3, and 4 years 
```{r}
pred_year <- c(2, 3, 4)
freq_cutoff <- 0.5

for (i in pred_year) {
  #------ Model prediction for C580Y ------
  forecast_data_C580Y <- prediction_model(pfk7_C580Y_K13, "C580Y", i, numofobs=2, freq_cutoff=0.5)

  #------ Model prediction for combined K13 mutations ------
  forecast_data_K13 <- prediction_model(pfk7_C580Y_K13, "K13", i, numofobs=2, freq_cutoff = 0.5)
  
  df_predict <- rbind(forecast_data_C580Y, forecast_data_K13)
  
  df_predict <- df_predict %>% 
    group_by(District, Locus) %>% 
    mutate(min_year = replace_na(min_year, 0), 
           min_year = max(min_year),
           label = paste0(i, "year"),  
           pred_y = i)
  
  #Assigning df_predict to variables
  var_name <- paste0("df_predict_cutoff_", i, "year")
  assign(var_name, df_predict)
}

#combine forecasting predictions for all years
df_predict_cutoff_allyear <- rbind(df_predict_cutoff_2year, df_predict_cutoff_3year, df_predict_cutoff_4year)
```

### Convert predictions to allele frequency scale
```{r}
df_predict_cutoff_allyear <- df_predict_cutoff_allyear %>%
  mutate(
    conf.high_freq = exp(conf.high)/(1+exp(conf.high)),
    conf.low_freq = exp(conf.low)/(1+exp(conf.low)),
    predict_freq = exp(predict)/(1+exp(predict)))
```

### SFigure 8: Plotting forecasting of predictions for the first 2, 3, and 4 years with allele frequency cut off
```{r}
################ PLOT FOR C580Y ################
prev_cutoff_c580y_plot <- plot_prediction(df_predict_cutoff_allyear, pfk7_C580Y_K13, "C580Y")

################ PLOT FOR ALL KELCH ################
prev_cutoff_K13_plot <- plot_prediction(df_predict_cutoff_allyear, pfk7_C580Y_K13, "K13")
```

##### Saving plots
```{r}
################ PLOT FOR C580Y ################
ggsave(
  paste0(
    "figures/supplement/Figure8_forecasting/forecasting/SEA_C580Y_prediction_cutoff",
    freq_cutoff,
    "freq.png"
  ),
  prev_cutoff_c580y_plot,
  width = 6,
  height = 4,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure8_forecasting/forecasting/SEA_C580Y_prediction_cutoff",
    freq_cutoff,
    "freq.pdf"
  ),
  prev_cutoff_c580y_plot,
  width = 6,
  height = 4,
  dpi = 700
)

################ PLOT FOR ALL KELCH ################
ggsave(
  paste0(
    "figures/supplement/Figure8_forecasting/forecasting/SEA_K13_prediction_cutoff",
    freq_cutoff,
    "freq.png"
  ),
  prev_cutoff_K13_plot,
  width = 6,
  height = 4,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure8_forecasting/forecasting/SEA_K13_prediction_cutoff",
    freq_cutoff,
    "freq.pdf"
  ),
  prev_cutoff_K13_plot,
  width = 6,
  height = 4,
  dpi = 700
)

write.table(df_predict_cutoff_allyear, paste0(
    "figures/supplement/Figure8_forecasting/forecasting/SEA_prediction_cutoff",
    freq_cutoff,
    "freq.txt"))
```

# Comparison to raw data
## Data preprocessing
```{r}
correlation_prediction_true <- correlation(pfk7_C580Y_K13, df_predict_cutoff_allyear, numofobs=2)
```                                            

## Supplement Figure 9: Plotting per district
```{r}
## Correlation plot for 50% cutoff in first year
correlation_plot_C580Y <- plot_correlation(correlation_prediction_true, "C580Y")
correlation_plot_K13 <- plot_correlation(correlation_prediction_true, "K13")
```

## Correlation table
```{r}
correlation_table <- correlation_prediction_true %>% 
  distinct(Locus, label, mae, bias, corr)
write.csv(correlation_table, 
            paste0("figures/supplement/Figure8_forecasting/correlation/SEA_correlation_table.csv"))
```

### Saving plots
```{r}
################# C580Y #################
ggsave(
  paste0(
    "figures/supplement/Figure8_forecasting/correlation/SEA_C580Y_correlation_cutoff_",
    freq_cutoff,
    "freq.png"
  ),
  correlation_plot_C580Y,
  width = 6,
  height = 4,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure8_forecasting/correlation/SEA_C580Y_correlation_cuttoff_",
    freq_cutoff,
    "freq.pdf"
  ),
  correlation_plot_C580Y,
  width = 6,
  height = 4,
  dpi = 700
)


################# K13 #################
ggsave(
  paste0(
    "figures/supplement/Figure8_forecasting/correlation/SEA_K13_correlation_cuttoff_",
    freq_cutoff,
    "freq.png"
  ),
  correlation_plot_K13,
  width = 6,
  height = 4,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure8_forecasting/correlation/SEA_K13_correlation_cuttoff_",
    freq_cutoff,
    "freq.pdf"
  ),
  correlation_plot_K13,
  width = 6,
  height = 4,
  dpi = 700
)
```

# Manuscript figures 
## Figure S7: Ratanakiri - Model Overview 
### Preprocessing
```{r}
df_Ratanakiri_pred <- df_predict_cutoff_allyear %>%
  filter(year <= min_year + pred_y,
         Locus == "K13",
         District == "Ratanakiri") %>%
  mutate(predict_prev = exp(predict)/(1 + exp(predict)))
df_Ratanakiri_forecasting <- df_predict_cutoff_allyear %>%
  filter(year >= min_year + pred_y, 
         District == "Ratanakiri", 
         Locus == "K13") %>%
  mutate(predicted_prev = exp(predict)/(1 + exp(predict)))
ex_pt <- pfk7_C580Y_K13 %>%
  filter(nobs > numofobs,
         District == "Ratanakiri",
         Locus == "K13") %>%
  mutate(point_col = case_when(year >= min_year & year <= min_year + 2 ~ "#E69F00",
                          year > min_year + 2 & year <= min_year + 3 ~ "#56B4E9",
                          year > min_year + 3 & year <= min_year + 4 ~ "#0072B2",
                          year > min_year + 4 ~ "black",
                          year < min_year ~ "black")) 
```

### Plotting
```{r}
prev_cutoff_K13_Ratanakiri_plot <- 
  ggplot() +
  geom_line(data = df_Ratanakiri_pred, aes(year, predict_freq, group = label, color = label)) +
  geom_line(data=df_Ratanakiri_forecasting, aes(year, exp(predict)/(1+exp(predict)), group = label, color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=freq, size = n), color = ex_pt$point_col) +
  labs(shape="Mutations", size = "Sample Size") +
  scale_x_continuous(breaks = seq(min(ex_pt$year), max(df_predict_cutoff_allyear$year), by = 2)) +
  theme_bw() +
  ylab("Allele frequency") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    labels = c("2 years", "3 years", "4 years", "true")
  ) + 
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8),
    strip.text.x = element_text(size = 8),
    legend.position = "none",
  ) +  labs(color = NULL)
```

### Saving
```{r}
ggsave(
  paste0(
    "figures/supplement/Figure7_forecasting_toy_example/Figure7_K13_Ratanakiri_",
    freq_cutoff,
    "freq_forecasting.png"
  ),
  prev_cutoff_K13_Ratanakiri_plot,
  width = 3.5,
  height = 3.5,
  dpi = 700
)

ggsave(
  paste0(
    "figures/supplement/Figure7_forecasting_toy_example/Figure7_K13_Ratanakiri_",
    freq_cutoff,
    "freq_forecasting.pdf"
  ),
  prev_cutoff_K13_Ratanakiri_plot,
  width = 3.25,
  height = 4,
  dpi = 700
)

write.csv(
  df_predict_cutoff_allyear %>%
    filter(District == "Ratanakiri", Locus == "K13") %>%
    mutate(predict_freq = round(predict_freq, 3)),
  "figures/supplement/Figure7_forecasting_toy_example/Figure7_Ratanakiri_forecasting.csv"
)
```

## Figure 5: Plotting forecasting of predictions for the first 2, 3, and 4 years with confidence intervals
```{r}
freq_cutoff <- 0.5
################ PLOT FOR C580Y ################
figure6_C580Y <- plot_forecasting_confidence(df_predict_cutoff_allyear, pfk7_C580Y_K13, "C580Y")

################ Plot K13 ################
figure6_K13 <- plot_forecasting_confidence(df_predict_cutoff_allyear, pfk7_C580Y_K13, "K13")
```

##### Saving plots
```{r}
fig6_width = 6
fig6_height = 4

ggsave(
  paste0(
    "figures/Figure4_forecasting/SEA/SEA_cutoff_C580Y_",
    freq_cutoff,
    "_freq_4year_pred.png"
  ),
  figure6_C580Y,
  width = fig6_width,
  height = fig6_height,
  dpi = 700
)
ggsave(
  paste0(
    "figures/Figure4_forecasting/SEA/SEA_cutoff_C580Y_",
    freq_cutoff,
    "_freq_4year_pred.pdf"
  ),
  figure6_C580Y,
  width = fig6_width,
  height = fig6_height,
  dpi = 700
)
ggsave(
  paste0(
    "figures/Figure4_forecasting/SEA/SEA_cutoff_K13_",
    freq_cutoff,
    "_freq_4year_pred.png"
  ),
  figure6_K13,
  width = fig6_width,
  height = fig6_height,
  dpi = 700
)
ggsave(
  paste0(
    "figures/Figure4_forecasting/SEA/SEA_cutoff_K13_",
    freq_cutoff,
    "_freq_4year_pred.pdf"
  ),
  figure6_K13,
  width = fig6_width,
  height = fig6_height,
  dpi = 700
)
```

### Get x% of data points within the 95% CrI
```{r}
pred_within_95CrI <- points_within_95CrI(df_predict_cutoff_allyear, pfk7_C580Y_K13)
  
write.csv(
  pred_within_95CrI,
  "figures/Figure4_forecasting/SEA/datapoints_within_95Crl.csv"
)
```

## Fixation values
```{r}
fix_0.95_allele_freq <- df_predict_cutoff_allyear %>% 
  filter(predict_freq >= 0.95)

fix_0.95_allele_freq_summary <- fix_0.95_allele_freq %>%
  select(District, country, year, min_year, Locus) %>%
  group_by(District, Locus) %>%
  filter(year == min(year)) %>% #obtain first fixated year
  ungroup %>%
  mutate(fixation =year - min_year) %>%
  group_by(Locus) %>%
  mutate(med = median(fixation),
         med_year = median(year),
         min_fixyear = min(year),
         max_fixyear = max(year))

write_csv(fix_0.95_allele_freq, "figures/Figure4_forecasting/SEA/fixation_95_all_data.csv")
write_csv(fix_0.95_allele_freq_summary, "figures/Figure4_forecasting/SEA/fixation_95_summary.csv")

fix_K13_0.9_allele_freq <- df_predict_cutoff_allyear  %>% 
  filter(predict_freq >= 0.9, Locus == "K13")

fix_K13_0.9_allele_freq_summary <- fix_K13_0.9_allele_freq %>%
  select(District, country, year, min_year, Locus) %>%
  group_by(District, Locus) %>%
  filter(year == min(year)) %>%
  ungroup %>%
  mutate(fixation =year - min_year) %>%
  group_by(Locus) %>%
  mutate(med = median(fixation),
         med_year = median(year),
         min_fixyear = min(year),
         max_fixyear = max(year))

write_csv(fix_0.95_allele_freq, "figures/Figure4_forecasting/SEA/K13_fixation_90_all_data.csv")
write_csv(fix_0.95_allele_freq_summary, "figures/Figure4_forecasting/SEA/K13_fixation_90_summary.csv")
```

## Underprediction analysis
```{r}
#obtain data that was predicted based on the first 5 years
predicted_4year <- df_predict_cutoff_allyear %>%
  select(adj_year, year, District, country, Locus, min_year, label, predict_freq) %>%
  filter(label == "4year") %>%
  arrange(country, District, Locus, year) %>%
  mutate(label = paste0(country, District, year, Locus))

#obtain true data 
observed_df_filtered <- pfk7_C580Y_K13 %>%
  select(adj_year, year, District, country, Locus, min_year, freq, n) %>%
  arrange(country, District, Locus, year) %>%
  mutate(label = paste0(country, District, year, Locus)) %>%
  filter(label %in% predicted_4year$label)

predicted_4year_filtered <-  predicted_4year %>%
  ungroup %>%
  filter(label %in% predicted_4year$label) %>%
  select(label, predict_freq)

observed_df_filtered  <- as.data.frame(observed_df_filtered)
predicted_4year_filtered <- as.data.frame(predicted_4year_filtered)

compare_df <- merge(x=observed_df_filtered, y=predicted_4year_filtered, by="label") %>%
  mutate(error = freq-predict_freq) %>%
  group_by(Locus) %>%
  mutate(weighted_mean_error = weighted.mean(error, n),
         median_error = median(error)) %>%
  ungroup %>%
  mutate(weighted_mean_error_overall = weighted.mean(error, n),
         median_error_overall = median(error))
  
write_csv(compare_df, "figures/Figure4_forecasting/SEA/underpredicted_allele_frequency_analysis.csv")

```
