---
title: "Pf7 Forecasting per district"
output: html_document
date: "2023-05-16"
---

```{r setup, include=FALSE}
library(cowplot)
library(dplyr)
library (ggforce)
library(ggplot2)
library(ggmap)
library(ggpubr)
library(ggspatial)
library(gt)
library(lme4)
library(Metrics)
library(nlme)
library(RColorBrewer)
library(rnaturalearth)
library(rnaturalearthdata)
library(rstan)
## install.packages("rstan", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))
library(scales)
library(scatterpie)
library(sf) #see ubuntu issues here: https://rtask.thinkr.fr/installation-of-r-4-0-on-ubuntu-20-04-lts-and-tips-for-spatial-packages/
library(tabulizer)
library(tidyverse)
library(tidyverse) # ggplot2, dplyr, tidyr, readr, purrr, tibble
```

# Load data
```{r}
#set the limit of number of observations
numofobs <- 2
#load data
pfk7_data <- read.table("data/data-derived/pfk7_data.txt") %>% filter(Locus != "other_PfK13")

pfk7_data2 <- pfk7_data %>% 
  group_by(Locus, District) %>%
  filter(nobs > numofobs) %>% #remove all distrcit where the first non-zero prevalence is larger than 50%
  arrange(Locus, District, year)

#----- C580Y -----
pfk7_data2_580Y <- pfk7_data2 %>%
  filter(Locus == "C580Y",
         District %in% c("Preah Vihear", "Ratanakiri", "Tak"))

#----- PfK13 -----
pfk7_data2_PfK13 <- pfk7_data2 %>%
  filter(Locus == "PfK13",
         District %in% c("Mandalay", "Preah Vihear", "Ratanakiri", "Tak"))

pfk7_data <- rbind(pfk7_data2_580Y, pfk7_data2_PfK13)
```

# Bayesian GMM with slopes and intercepts
```{r}
# Have a read through rstanarm vignettes and guides on how it works in comparison to lme4
# ---- Model for c580y -----
c580y_stanmod <- rstanarm::stan_glmer(
  lrsmed ~ adj_year + (1 + adj_year | District),
  data = pfk7_data %>% filter(Locus == "C580Y", nobs > numofobs),
  weights = wt_med, 
  adapt_delta = 0.9975
)

vals <- summary(c580y_stanmod$stanfit)$summary[, 1]
vals <- vals[grep("^b", names(vals))]
ranef_c580y_stanmod <-
  data.frame("Intercepts" = vals[seq(1, length(vals), 2)],
             "Slopes" = vals[seq(2, length(vals), 2)])
ranef_c580y_stanmod$mutation <- rep("C580Y", dim(ranef_c580y_stanmod)[1])

# ---- Model for combined kelch -----

all_kelch_stanmod <- rstanarm::stan_glmer(
  lrsmed ~ adj_year + (1 + adj_year | District),
  data = pfk7_data %>% filter(Locus == "PfK13", nobs > numofobs),
  weights = wt_med, 
  adapt_delta = 0.9975
)

vals <- summary(all_kelch_stanmod$stanfit)$summary[, 1]
vals <- vals[grep("^b", names(vals))]
ranef_all_kelch_stanmod <-
  data.frame("Intercepts" = vals[seq(1, length(vals), 2)],
             "Slopes" = vals[seq(2, length(vals), 2)])
ranef_all_kelch_stanmod$mutation <- rep("K13", dim(ranef_all_kelch_stanmod)[1])

ranef_stanmod <-
  rbind(ranef_c580y_stanmod,
        ranef_all_kelch_stanmod)
ranef_stanmod$site <- str_replace_all(rownames(ranef_stanmod), "\\[|\\]", "")
ranef_stanmod$site <- str_replace_all(ranef_stanmod$site, "\\s*\\([^\\)]+\\)", "")
ranef_stanmod$site <- str_remove(ranef_stanmod$site, "b District:")
ranef_stanmod$site <- str_remove(ranef_stanmod$site, "1")
``` 
## Posterior of the model
```{r}
#  get model predictions for plotting
pfk7_data$predict_stan <- NA

pfk7_data$predict_stan[is.finite(pfk7_data$lrsmed) & pfk7_data$Locus == "C580Y" & pfk7_data$nobs > numofobs] <-  rstanarm::posterior_predict(c580y_stanmod, type = "response") %>% colMeans
pfk7_data$predict_stan[is.finite(pfk7_data$lrsmed) & pfk7_data$Locus == "PfK13" & pfk7_data$nobs > numofobs] <-  rstanarm::posterior_predict(all_kelch_stanmod, type = "response") %>% colMeans
```

## Convert prediction to prevalence scale
```{r}
#convert confidence of forecasting into pervalence
pfk7_data <- pfk7_data %>%
  mutate(predict_stan_prev = exp(predict_stan)*100/(1+exp(predict_stan)))
```

# Forecasting Selection 
## First year 50% cutoff based on the first 2, 3, and 4 years 
```{r}
pred_year <- c(2, 3, 4)
prev_cutoff <- 0.5

for (i in pred_year) {
  #------ Model prediction for C580Y ------
  data_c580y <- pfk7_data %>% 
    filter(
      Locus == "C580Y",
      nobs > numofobs,
      year >= min_year & year <= min_year + i) 
  
  c580y_pred <- rstanarm::stan_glmer(
    lrsmed ~ adj_year + (1 + adj_year | District),
    data = data_c580y,
    weights = wt_med,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs > numofobs, 
           is.finite(lrsmed),
           Locus == "C580Y") %>%
    group_by(District, Locus) %>%
    complete(year = seq(min(min_year) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, District, country, min_year, Locus) %>%
    mutate(min_year = replace(min_year, is.na(min_year), 0)) 
  
  new_data <- new_data %>%
    group_by(District, Locus) %>%
    mutate(min_year = max(min_year),
      adj_year = year - min_year,
      country = unique(na.omit(country))) %>%
    arrange(Locus, District, year) %>%
    ungroup %>%
    group_by(Locus, District, year) %>%
    distinct(year, .keep_all = TRUE) %>%
    ungroup
  
  sampling <- rstanarm::posterior_predict(c580y_pred, type = "response", newdata = new_data)
  predictions <- sampling %>% colMeans
  conf_val <- sampling %>% apply(2, quantile, prob = (c(0.025, 0.975)))

  new_data <- new_data %>%
    mutate(predict = predictions,
           conf.low = conf_val[1,],
           conf.high = conf_val[2,])

  df_predict <- new_data

  
  #------ Model prediction for combined PfK13 mutations ------
  data_all_kelch <- pfk7_data %>% 
    filter(Locus == "PfK13",
      nobs > numofobs,
      year >= min_year & year <= min_year + i) 
  
  all_kelch_pred <- rstanarm::stan_glmer(
    lrsmed ~ adj_year + (1 + adj_year | District),
    data = data_all_kelch,
    weights = wt_med,
    adapt_delta = 0.9975
  )
  
  # forecasting
  new_data <- pfk7_data %>%
    filter(nobs > numofobs, 
           is.finite(lrsmed),
           Locus == "PfK13") %>%
    group_by(District, Locus) %>% 
    complete(year = seq(min(min_year) + i, 2023, 1)) %>% # this creates all the year values up to 2023
    ungroup() %>% 
    select(adj_year, year, country, District, min_year, Locus) %>%
    mutate(min_year = replace(min_year, is.na(min_year), 0))
  
  new_data <- new_data %>%
    group_by(District, Locus) %>%
    mutate(min_year = max(min_year),
      adj_year = year - min_year,
      country = unique(na.omit(country))) %>%
    arrange(Locus, country, District, year) %>%
    ungroup %>%
    group_by(Locus, District, year) %>%
    distinct(year, .keep_all = TRUE) %>%
    ungroup
  
  sampling <- rstanarm::posterior_predict(all_kelch_pred, type = "response", newdata = new_data)
  predictions <- sampling %>% colMeans
  conf_val <- sampling %>% apply(2, quantile, prob = (c(0.025, 0.975)))

  new_data <- new_data %>% 
    mutate(predict = predictions,
           conf.low = conf_val[1,],
           conf.high = conf_val[2,])
  
  df_predict <- rbind(df_predict, new_data)
  
  df_predict <- df_predict %>% 
    group_by(District, Locus) %>% 
    mutate(min_year = replace_na(min_year, 0), 
           min_year = max(min_year),
           label = paste0(i, "year"),  
           pred_y = i)
  
  #Assigning df_predict to variables
  var_name <- paste0("df_predict_cutoff_", i, "year")
  assign(var_name, df_predict)
}

#combine forecasting predictions for all years
df_predict_cutoff_allyear <- rbind(df_predict_cutoff_2year, df_predict_cutoff_3year, df_predict_cutoff_4year)
```

### Convert predictions to prevalence scale
```{r}
df_predict_cutoff_allyear <- df_predict_cutoff_allyear %>%
  mutate(
    conf.high_prev = exp(conf.high)*100/(1+exp(conf.high)),
    conf.low_prev = exp(conf.low)*100/(1+exp(conf.low)),
    predict_prev = exp(predict)*100/(1+exp(predict)))
```

### SFigure 8: Plotting forecasting of predictions for the first 2, 3, and 4 years with prevalence cut off
```{r}
################ PLOT FOR C580Y ################
prev_cutoff_perc <- prev_cutoff *100
df_pred <- df_predict_cutoff_allyear %>% 
  filter(year >= min_year + pred_y, Locus == "C580Y") 
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed), nobs > numofobs, District %in% unique(df_pred$District), Locus == "C580Y")
ex_pt <- pfk7_data %>% 
  filter(nobs > numofobs, District %in% unique(df_pred$District), Locus == "C580Y") %>% #, year >= min_year & year <= min_year+4
  mutate(point_col = case_when(year >= min_year & year <= min_year + 2 ~ "#E69F00",
                               year > min_year + 2 & year <= min_year + 3 ~ "#56B4E9",
                               year > min_year + 3 & year <= min_year + 4 ~ "#0072B2",
                               year > min_year + 4 ~ "black",
                               year < min_year ~ "black")) 
## PLOT FOR C580Y
prev_cutoff_c580y_plot <- 
  ggplot() +
  geom_line(data=ex, aes(year, predict_stan_prev, color = "true"), linewidth = 1) + 
  geom_line(data=df_pred, aes(year, predict_prev, group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev*100, size = n), color = ex_pt$point_col) +
  scale_size_binned(name = "Sample Size",range = c(0.2,2)) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~District, ncol = 2) +
  ylab("580Y Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    labels = c("2 years", "3 years", "4 years", "true"),
    guide = "none"
  ) + 
  theme(
      axis.line = element_line(),
      axis.text = element_text(size = 8),
      axis.title = element_text(size = 10),
      strip.text.x = element_text(size = 10),
      legend.title = element_text(size = 10),
      legend.text = element_text(size = 8),
      legend.position = "right",
      panel.spacing = unit(0.2, "lines")
    )

################ PLOT FOR ALL KELCH ################
df_pred <- df_predict_cutoff_allyear %>% 
  filter(year >= min_year +  pred_y, Locus == "PfK13")  
ex <- pfk7_data %>% 
  filter(is.finite(lrsmed), nobs > numofobs, District %in% unique(df_pred$District), Locus == "PfK13")
ex_pt <- pfk7_data %>% 
  filter(nobs > numofobs, District %in% unique(df_pred$District), Locus == "PfK13") %>% #, year >= min_year & year <= min_year+4
  mutate(point_col = case_when(year >= min_year & year <= min_year + 2 ~ "#E69F00",
                               year > min_year + 2 & year <= min_year + 3 ~ "#56B4E9",
                               year > min_year + 3 & year <= min_year + 4 ~ "#0072B2",
                               year > min_year + 4 ~ "black",
                               year < min_year ~ "black")) 
 prev_cutoff_all_kelch_plot <- ggplot() +
  geom_line(data=ex, aes(year, predict_stan_prev, color = "true")) + 
  geom_line(data=df_pred, aes(year, predict_prev, group = label,color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev*100, size = n), color = ex_pt$point_col) +
  scale_size_binned(name = "Sample Size",range = c(0.2,2)) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~District) +
  ylab("K13 Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    labels = c("2 years", "3 years", "4 years", "true"),
    guide = "none"
  ) + 
  theme(
      axis.line = element_line(),
      axis.text = element_text(size = 8),
      axis.title = element_text(size = 10),
      strip.text.x = element_text(size = 10),
      legend.title = element_text(size = 10),
      legend.text = element_text(size = 8),
      legend.position = "right",
      panel.spacing = unit(0.2, "lines")
    )
```

##### Saving plots
```{r}
################ PLOT FOR C580Y ################
ggsave(
  paste0(
    "figures/supplement/Figure8-ForecastingCorrelation/forecasting/SEAsia_cutoff_pred_C580Y_",
    prev_cutoff_perc,
    "prev_pred.png"
  ),
  prev_cutoff_c580y_plot,
  width = 6,
  height = 4,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure8-ForecastingCorrelation/forecasting/SEAsia_cutoff_pred_C580Y_",
    prev_cutoff_perc,
    "prev_pred.pdf"
  ),
  prev_cutoff_c580y_plot,
  width = 6,
  height = 4,
  dpi = 700
)

################ PLOT FOR ALL KELCH ################
ggsave(
  paste0(
    "figures/supplement/Figure8-ForecastingCorrelation/forecasting/SEAsia_cutoff_pred_PfK13_",
    prev_cutoff_perc,
    "prev_pred.png"
  ),
  prev_cutoff_all_kelch_plot,
  width = 6,
  height = 4,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure8-ForecastingCorrelation/forecasting/SEAsia_cutoff_pred_PfK13_",
    prev_cutoff_perc,
    "prev_pred.pdf"
  ),
  prev_cutoff_all_kelch_plot,
  width = 6,
  height = 4,
  dpi = 700
)

write.table(df_predict_cutoff_allyear, paste0(
    "figures/supplement/Figure8-ForecastingCorrelation/forecasting/SEAsia_cutoff_pred_C580Y_",
    prev_cutoff_perc,
    "predict_cutoff_allyears.txt"))
```

# Comparison to raw data
## Data preprocessing
```{r}
inital_true <- pfk7_data %>% 
  filter(nobs > numofobs)

corr_df_cutoff <- NULL
for(l in unique(df_predict_cutoff_allyear$label)) {
  #filter forecasting based on year (label)
  pred <- df_predict_cutoff_allyear %>%
    filter(label == l) %>%
    mutate(val = paste0(year, District, Locus, min_year)) %>%
    arrange(val) %>%
    rename(p_pred = predict) 
  #filter data points in true that are also in forecasted
  true <- inital_true
  true <- true %>%
    mutate(val = paste0(year, District, Locus, min_year)) %>%
    arrange(val) %>%
    filter(val %in% pred$val)
  #make sure districts match between true and forecasted
  pred <- pred %>% filter(val %in% true$val)
  df <- cbind(true, pred$p_pred, pred$label, pred$pred_y)
  colnames(df)[ncol(df)-2] <- "p_pred"
  colnames(df)[ncol(df)-1] <- "label"
  colnames(df)[ncol(df)] <- "pred_y"
  corr_df_cutoff <- rbind(corr_df_cutoff, df) %>% 
    filter(year > min_year + pred_y)
}

corr_df_cutoff <- corr_df_cutoff %>%
  mutate(p_pred_prev = exp(p_pred) * 100 / (1 + exp(p_pred)),
           t_pred_prev = prev*100) %>%
  group_by(Locus, label) %>%
  mutate(mae = round(mean(abs(t_pred_prev - p_pred_prev)), 2), #mean absolute error  -> mean(abs(true-prediction)
         bias = round(mean(t_pred_prev - p_pred_prev), 2), #mean bias -> mean(true - prediction)
         corr = round(cor(t_pred_prev, p_pred_prev), 2)) %>%
  select(country, District, year, Locus, p_pred_prev, t_pred_prev, mae, bias, corr, nobs, adj_year, val , label) %>%
  arrange(Locus, label)

```                                            

## Supplement Figure 9: Plotting per district
```{r}
## Correlation plot for 50% cutoff in first year
for (mu in unique(corr_df_cutoff$Locus)){
  correlation_raw_plot_cutoff <- corr_df_cutoff %>% filter(Locus == mu) %>%
    ggplot(aes(x = t_pred_prev, y = p_pred_prev, color = label, group = label)) +
    geom_point() +
    geom_abline(slope = 1, intercept = 0, color = "grey", linetype = "dashed") +
    facet_wrap(~ District) +
    theme_bw() +
    xlab("True") +
    ylab(paste(mu, "Prediction", sep=" ")) +
    scale_y_continuous(limits=c(0,100), breaks = c(0, 25, 50, 75, 100)) +
    scale_x_continuous(limits=c(0,100), breaks = c(0, 25, 50, 75, 100)) +
    scale_color_manual(
      values = c("#E69F00", "#56B4E9", "#0072B2"),
      labels = c("2 years", "3 years", "4 years")
    ) + 
    theme_bw() +
    ggpubr::theme_pubclean(base_size = 12) +
    theme(
      axis.line = element_line(),
      axis.text = element_text(size = 8),
      axis.title = element_text(size = 10),
      strip.text.x = element_text(size = 10),
      legend.position = "none",
      panel.spacing = unit(0.2, "lines")
    ) +  labs(color = NULL)
  
  #Assigning df_predict to variables
  var_name <- paste0(mu, "_correlation_raw_plot_cutoff")
  assign(var_name, correlation_raw_plot_cutoff)
}
```

## Correlation table
```{r}
correlation_table <- corr_df_cutoff %>% distinct(Locus, label, mae, bias, corr)
write.csv(correlation_table, 
            paste0("figures/supplement/Figure9-ForecastingCorrelation/correlation/SEAsia_correlation_table.csv"))
```

### Saving plots
```{r}
################# C580Y #################
ggsave(
  paste0(
    "figures/supplement/Figure9-ForecastingCorrelation/correlation/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_C580Y_correlation.png"
  ),
  C580Y_correlation_raw_plot_cutoff,
  width = 6,
  height = 4,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure9-ForecastingCorrelation/correlation/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_C580Y_correlation.pdf"
  ),
  C580Y_correlation_raw_plot_cutoff,
  width = 6,
  height = 4,
  dpi = 700
)


################# PfK13 #################
ggsave(
  paste0(
    "figures/supplement/Figure9-ForecastingCorrelation/correlation/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_PfK13_correlation.png"
  ),
  PfK13_correlation_raw_plot_cutoff,
  width = 6,
  height = 4,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure9-ForecastingCorrelation/correlation/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_PfK13_correlation.pdf"
  ),
  PfK13_correlation_raw_plot_cutoff,
  width = 6,
  height = 4,
  dpi = 700
)
```

# Manuscript figures 
## Figure 4: Pailin - Model Overview 
### Preprocessing
```{r}
df_Ratanakiri_pred <- df_predict_cutoff_allyear %>%
  filter(year <= min_year + pred_y,
         Locus == "PfK13",
         District == "Ratanakiri",
         pred_y == 4) %>%
  mutate(predict_prev = exp(predict) * 100 / (1 + exp(predict)))
df_Ratanakiri_forecasting <- df_predict_cutoff_allyear %>%
  filter(year >= min_year + pred_y, 
         District == "Ratanakiri", 
         Locus == "PfK13", 
         pred_y == 4) %>%
  mutate(predicted_prev = exp(predict) * 100 / (1 + exp(predict)))
ex <- pfk7_data %>%
  filter(is.finite(lrsmed),
         nobs > numofobs,
         District == "Ratanakiri",
         Locus == "PfK13")
ex_pt <- pfk7_data %>%
  filter(nobs > numofobs,
         District == "Ratanakiri",
         Locus == "PfK13") %>%
  mutate(point_col = case_when(year >= min_year & year <= min_year + 4 ~ "#E69F00",
                          year > min_year + 4 ~ "black",
                          year < min_year ~ "black")) 
```

### Plotting
```{r}
prev_cutoff_pfk13_Ratanakiri_plot <- 
  ggplot() +
  geom_line(data = df_Ratanakiri_pred, aes(year, predict_prev, group = label, color = label)) +
  geom_line(data=df_Ratanakiri_forecasting, aes(year, exp(predict)*100/(1+exp(predict)), group = label, color = label)) +
  geom_ribbon(data = df_Ratanakiri_forecasting, aes(ymin = conf.low_prev, ymax = conf.high_prev, x = year, color = label, group = label, fill = label), linetype = "dashed", alpha = 0.2) +
  geom_point(data = ex_pt, aes(x=year, y=prev*100, size = n), color = ex_pt$point_col) +
  labs(shape="Mutations", size = "Sample Size") +
  scale_x_continuous(breaks = seq(min(ex_pt$year), max(df_Ratanakiri_forecasting$year), by = 2)) +
  theme_bw() +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "grey"),
    labels = c("4 years", "true")
  ) + 
  scale_fill_manual(
    values = c("#E69F00", "grey"),
    labels = c("4 years", "true")
  ) + 
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8),
    strip.text.x = element_text(size = 8),
    legend.position = "none",
  ) +  labs(color = NULL)
```

### Saving
```{r}
ggsave(
  paste0(
    "figures/Figure4-ForecastingOverview/Figure4_PfK13_Ratanakiri_",
    prev_cutoff_perc,
    "prev_forecasting.png"
  ),
  prev_cutoff_pfk13_Ratanakiri_plot,
  width = 2.7,
  height = 3,
  dpi = 700
)

ggsave(
  paste0(
    "figures/Figure4-ForecastingOverview/Figure4_PfK13_Ratanakiri_",
    prev_cutoff_perc,
    "prev_forecasting.pdf"
  ),
  prev_cutoff_pfk13_Ratanakiri_plot,
  width = 2.7,
  height = 3.5,
  dpi = 700
)

write.csv(
  df_predict_cutoff_allyear %>%
    filter(District == "Ratanakiri", Locus == "PfK13") %>%
    mutate(predict_prev = round(predict_prev, 2)),
  "figures/Figure4-ForecastingOverview/Figure4-Ratanakiri-forecasting.csv"
)
```

## Figure S7: Pailin - Model Overview 
### Preprocessing
```{r}
df_Ratanakiri_pred <- df_predict_cutoff_allyear %>%
  filter(year <= min_year + pred_y,
         Locus == "PfK13",
         District == "Ratanakiri") %>%
  mutate(predict_prev = exp(predict) * 100 / (1 + exp(predict)))
df_Ratanakiri_forecasting <- df_predict_cutoff_allyear %>%
  filter(year >= min_year + pred_y, District == "Ratanakiri", Locus == "PfK13") %>%
  mutate(predicted_prev = exp(predict) * 100 / (1 + exp(predict)))
ex <- pfk7_data %>%
  filter(is.finite(lrsmed),
         nobs > numofobs,
         District == "Ratanakiri",
         Locus == "PfK13")
ex_pt <- pfk7_data %>%
  filter(nobs > numofobs,
         District == "Ratanakiri",
         Locus == "PfK13") %>%
  mutate(point_col = case_when(year >= min_year & year <= min_year + 2 ~ "#E69F00",
                          year > min_year + 2 & year <= min_year + 3 ~ "#56B4E9",
                          year > min_year + 3 & year <= min_year + 4 ~ "#0072B2",
                          year > min_year + 4 ~ "black",
                          year < min_year ~ "black")) 
```

### Plotting
```{r}
prev_cutoff_pfk13_Ratanakiri_plot <- 
  ggplot() +
  geom_line(data = df_Ratanakiri_pred, aes(year, predict_prev, group = label, color = label)) +
  geom_line(data=df_Ratanakiri_forecasting, aes(year, exp(predict)*100/(1+exp(predict)), group = label, color = label), linetype = "dashed") +
  geom_point(data = ex_pt, aes(x=year, y=prev*100, size = n), color = ex_pt$point_col) +
  labs(shape="Mutations", size = "Sample Size") +
  scale_x_continuous(breaks = seq(min(ex_pt$year), max(df_pred$year), by = 2)) +
  theme_bw() +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual(
    values = c("#E69F00", "#56B4E9", "#0072B2", "grey"),
    labels = c("2 years", "3 years", "4 years", "true")
  ) + 
  theme(
    axis.line = element_line(),
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 8),
    strip.text.x = element_text(size = 8),
    legend.position = "none",
  ) +  labs(color = NULL)
```

### Saving
```{r}
ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/Figure7_PfK13_Ratanakiri_",
    prev_cutoff_perc,
    "prev_forecasting.png"
  ),
  prev_cutoff_pfk13_Ratanakiri_plot,
  width = 2.7,
  height = 3,
  dpi = 700
)

ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/Figure7_PfK13_Ratanakiri_",
    prev_cutoff_perc,
    "prev_forecasting.pdf"
  ),
  prev_cutoff_pfk13_Ratanakiri_plot,
  width = 2.7,
  height = 3.5,
  dpi = 700
)

write.csv(
  df_predict_cutoff_allyear %>%
    filter(District == "Ratanakiri", Locus == "PfK13") %>%
    mutate(predict_prev = round(predict_prev, 2)),
  "figures/supplement/Figure8-Forecasting/Figure7-Pailin-forecasting.csv"
)
```

## Figure 5: Plotting forecasting of predictions for the first 2, 3, and 4 years with confidence intervals
```{r}
prev_cutoff_perc <- 50
################ PLOT FOR C580Y ################
C580Y_df_pred <- df_predict_cutoff_allyear %>% 
  filter(year >= min_year + pred_y, 
         pred_y == 4,
         Locus == "C580Y") %>%
  mutate(label = "pred",
         point_col = "#0072B2")
C580Y_df_true <- df_predict_cutoff_allyear %>% 
  filter(year <= min_year + pred_y, 
         pred_y == 4,
         Locus == "C580Y") %>%
  mutate(label = "true",
         point_col = "#0072B2")
C580Y_ex_pt <- pfk7_data %>% 
  filter(nobs > numofobs, 
         District %in% unique(C580Y_df_pred$District),
         Locus == "C580Y") %>%
  mutate(point_col = case_when(year >= min_year & year <= min_year + 4 ~ "#0072B2",
                          year > min_year + 4 ~ "black",
                          year < min_year ~ "black")) 

fig6_prev_cutoff_plot_C580Y <- 
  ggplot() +
  geom_point(data = C580Y_ex_pt, aes(x=year, y=prev*100, color = point_col, group = Locus)) +
  scale_size_binned(name = "Sample Size", range = c(0.2,2)) +
  geom_line(data = C580Y_df_true, aes(year, predict_prev, color = point_col, group = Locus)) + 
  geom_line(data = C580Y_df_pred, aes(year, predict_prev, color = point_col, group = Locus)) +
  geom_ribbon(data = C580Y_df_pred, aes(ymin = conf.low_prev, ymax = conf.high_prev, x = year, color = point_col, group = Locus, fill = point_col), linetype = "dashed", alpha = 0.2) +
  theme_bw() +
  facet_wrap(~District) +
  ylab("580Y Prevalence") +
  xlab("Year") +
  scale_color_manual(
    values = c("#0072B2", "black"),
    name = "Mutation") +
  scale_fill_manual(
    values = c("#0072B2", "black"),
    name = "Mutation") +
  ggpubr::theme_pubclean(base_size = 12) +
  theme(
      axis.line = element_line(),
      axis.text = element_text(size = 6),
      axis.title = element_text(size = 10),
      strip.text.x = element_text(size = 10),
      legend.title = element_text(size = 10),
      legend.text = element_text(size = 8),
      legend.position = "none",
      panel.spacing = unit(0.2, "lines")
    )

################ Plot PfK13 ################
PfK13_df_pred <- df_predict_cutoff_allyear %>% 
  filter(year >= min_year + pred_y, 
         pred_y == 4,
         Locus == "PfK13") %>%
  mutate(label = "pred",
         point_col = "#0072B2")
PfK13_df_true <- df_predict_cutoff_allyear %>% 
  filter(year <= min_year + pred_y, 
         pred_y == 4,
         Locus == "PfK13") %>%
  mutate(label = "true",
         point_col = "#0072B2")
PfK13_ex_pt <- pfk7_data %>% 
  filter(nobs > numofobs, 
         District %in% unique(PfK13_df_pred$District),
         Locus == "PfK13",
         District != "Pailin") %>%
  mutate(point_col = case_when(year >= min_year & year <= min_year + 4 ~ "#0072B2",
                          year > min_year + 4 ~ "black",
                          year < min_year ~ "black"))  

fig6_prev_cutoff_plot_PfK13 <- 
  ggplot() +
  geom_point(data = PfK13_ex_pt, aes(x=year, y=prev*100, color = point_col, group = Locus)) +
  scale_size_binned(name = "Sample Size", range = c(0.2,2)) +
  geom_line(data = PfK13_df_true, aes(year, predict_prev, color = point_col, group = Locus)) + 
  geom_line(data = PfK13_df_pred, aes(year, predict_prev, color = point_col, group = Locus)) +
  geom_ribbon(data = PfK13_df_pred, aes(ymin = conf.low_prev, ymax = conf.high_prev, x = year, color = point_col, group = Locus, fill = point_col), linetype = "dashed", alpha = 0.2) +
  theme_bw() +
  facet_wrap(~District) +
  ylab("K13 Prevalence") +
  xlab("Year") +
  scale_color_manual(
    values = c("#0072B2", "black"),
    name = "Mutation") +
  scale_fill_manual(
    values = c("#0072B2", "black"),
    name = "Mutation") +
  ggpubr::theme_pubclean(base_size = 12) +
  theme(
      axis.line = element_line(),
      axis.text = element_text(size = 6),
      axis.title = element_text(size = 10),
      strip.text.x = element_text(size = 10),
      legend.title = element_text(size = 10),
      legend.text = element_text(size = 8),
      legend.position = "none",
      panel.spacing = unit(0.2, "lines")
    )
```

##### Saving plots
```{r}
fig6_width = 6
fig6_height = 4

ggsave(
  paste0(
    "figures/Figure5-Forecasting/SE_Asia/SEAsia_cutoff_C580Y_",
    prev_cutoff_perc,
    "_prev_4year_pred.png"
  ),
  fig6_prev_cutoff_plot_C580Y,
  width = fig6_width,
  height = fig6_height,
  dpi = 700
)
ggsave(
  paste0(
    "figures/Figure5-Forecasting/SE_Asia/SEAsia_cutoff_C580Y_",
    prev_cutoff_perc,
    "_prev_4year_pred.pdf"
  ),
  fig6_prev_cutoff_plot_C580Y,
  width = fig6_width,
  height = fig6_height,
  dpi = 700
)
ggsave(
  paste0(
    "figures/Figure5-Forecasting/SE_Asia/SEAsia_cutoff_PfK13_",
    prev_cutoff_perc,
    "_prev_4year_pred.png"
  ),
  fig6_prev_cutoff_plot_PfK13,
  width = fig6_width,
  height = fig6_height,
  dpi = 700
)
ggsave(
  paste0(
    "figures/Figure5-Forecasting/SE_Asia/SEAsia_cutoff_PfK13_",
    prev_cutoff_perc,
    "_prev_4year_pred.pdf"
  ),
  fig6_prev_cutoff_plot_PfK13,
  width = fig6_width,
  height = fig6_height,
  dpi = 700
)
```

### Get x% of data points within the 95% CrI
```{r}
C580Y_df_pred <- df_predict_cutoff_allyear %>% 
  filter(year >= min_year + pred_y, 
         pred_y == 4,
         Locus == "C580Y") %>%
  mutate(label = "pred")

PfK13_df_pred <- df_predict_cutoff_allyear %>% 
  filter(year >= min_year + pred_y, 
         pred_y == 4,
         Locus == "PfK13") %>%
  mutate(label = "pred")

C580Y_ex_pt <- pfk7_data %>% 
  filter(nobs > numofobs, 
         District %in% unique(C580Y_df_pred$District),
         Locus == "C580Y")

PfK13_ex_pt <- pfk7_data %>% 
  filter(nobs > numofobs, 
         District %in% unique(C580Y_df_pred$District),
         Locus == "PfK13")

df_pred <- rbind(C580Y_df_pred, PfK13_df_pred)
ex_pt <- rbind(C580Y_ex_pt, PfK13_ex_pt)

pred_data <- df_pred %>% mutate(label = paste0(country, District, year, Locus))
true_data <- ex_pt %>% mutate(label = paste0(country, District, year, Locus))

true_prev <- true_data[true_data$label %in% pred_data$label,] %>% 
  mutate(prev = prev*100) %>% 
  select(prev)
pred_data_filter <- pred_data[pred_data$label %in% true_data$label,]
pred_data_filter <- cbind(pred_data_filter, true_prev$prev)
colnames(pred_data_filter)[15] <- "prev"

pred_data_filter <- pred_data_filter %>% 
  group_by(Locus) %>%
  mutate(val = case_when(prev >= conf.low_prev & prev <= conf.high_prev ~ "yes",
                          prev < conf.low_prev | prev > conf.high_prev ~ "no"),
         perc = sum(val == "yes")*100/(sum(val == "yes") + sum(val == "no")),
         num = sum(val == "yes"),
         den = sum(val == "yes") + sum(val == "no")) %>%
  distinct(perc, .keep_all = T) %>%
  select(Locus, perc, num, den) %>%
  ungroup 
  
write.csv(
  pred_data_filter,
  "figures/Figure5-Forecasting/SE_Asia/Datapoint%_95Crl.csv"
)
```
