---
title: "Supplemental figures"
output: html_document
date: "2024-05-13"
---

```{r setup, include=FALSE}
library(lme4)
library(nlme)
library(dplyr)
library(ggplot2)
library(ggpattern)
library(ggpubr)
library(scales)
library(tidyverse)
library(cowplot)
library(tabulizer)
library(RColorBrewer)
library(tidyverse) # ggplot2, dplyr, tidyr, readr, purrr, tibble
library(rnaturalearth)
library(rnaturalearthdata)
library(sf) #see ubuntu issues here: https://rtask.thinkr.fr/installation-of-r-4-0-on-ubuntu-20-04-lts-and-tips-for-spatial-packages/
library(ggspatial)
library(scatterpie)
library(scales)
library (ggforce)
library (ggmap)
library(rstan)
library(gt)
library(ggbreak) 
## install.packages("rstan", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))
```

# Load data
```{r}
#load data
df_uganda <- read.table("data/data-derived/Uganda_allele_frequency.txt")
df_comb_uganda <- read.table("data/data-derived/Uganda_mean_allele_frequency.txt")
df_pfk7 <- read.table("data/data-derived/pfk7_allele_frequency.txt")
df_pfk7_com <- read.table("data/data-derived/pfk7_allele_frequency_mean.txt")
df_comb_pfk7 <- read.table("data/data-derived/pfk7_allele_frequency_year_mean.txt")

#set the limit of number of observations
numofobs <- 2

fileLocManuscript <- "figures"
```

# Figure1: Overview of data plot Uganda with less than three observations --> data not included in analysis
```{r}
plot_overview_uganda <- df_uganda %>%
  filter(Locus != "K13") %>%
  arrange(desc(Locus)) %>%
  ggplot(aes(year, freq, group = Locus, color = Locus)) +
  geom_point(aes(size = n)) +
  scale_size_binned(name = "Sample Size",
                    range = c(0.2,2.5)) +
  labs(shape = "Mutations", 
       size = "Sample Size") +
  theme_bw() +
  facet_wrap( ~ District) +
  ylab("Allele frequency") +
  xlab("Year") +
  scale_color_manual(values = c("#D55E00",
                              "#0072B2",
                              "#009E73",
                              "#59386c",
                              "#F0E442"),
                   labels = c("675V",
                              "469F",
                              "469Y",
                              "441L",
                              "561H")) +
  ggpubr::theme_pubclean(base_size = 12) +
  theme(
    axis.line = element_line(),
    legend.title = element_text(size = 12),
    axis.text = element_text(size = 6),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    strip.text.x = element_text(size = 10),
    legend.position = "right", #c(0.94, 0.07)
  )
```

### Saving plot
```{r}
ggsave(
  paste0(fileLocManuscript, "/supplement/Figure1-Uganda-DataOverview/Uganda_dataoverview.pdf"),
  plot_overview_uganda,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(fileLocManuscript, "/supplement/Figure1-Uganda-DataOverview/Uganda_dataoverview.png"),
  plot_overview_uganda,
  width = 8,
  height = 5,
  dpi = 700
)
```

# Figure 2: Uganda Map for 2016-2020
## Download map components
```{r}
#load base map layers
admin8 <- ne_download(scale="large", type = "admin_1_states_provinces_lines",
                      category = "cultural", returnclass = "sf")
rivers8 <- ne_download(scale = 10, type = 'rivers_lake_centerlines',
                       category = 'physical', returnclass = "sf")
lakes8 <- ne_download(scale = "large", type = 'lakes',
                      category = 'physical', returnclass = "sf")
sov110 <- ne_download(scale="medium", type = "sovereignty",
                      category = "cultural", returnclass = "sf")
admin110 <- ne_download(scale="large", type = "populated_places",
                        category = "cultural", returnclass = "sf")
kampala <- data.frame(name="Kampala", long=32.5833, lat=0.31666)

pt.lim = data.frame(xlim = c(28.5, 35.5), ylim = c(4.25,-3))
pt.bbox <- st_bbox(c(xmin=pt.lim$xlim[1],
           xmax=pt.lim$xlim[2],
           ymin=pt.lim$ylim[1],
           ymax=pt.lim$ylim[2]))

#get uganda specific information
uganda <- ne_states(country="Uganda", returnclass = "sf") %>% 
  st_crop(pt.bbox) %>% 
  select(name, latitude, longitude) %>%
  arrange(name)
uganda$name[uganda$name == "Kabale"] <- "Rukiga"
uganda <- uganda %>% 
  filter(name %in% unique(df_comb_uganda$District)) %>% 
  na.omit() %>% arrange(name)
```

## Data Preprocessing
```{r}
pie_data <- df_comb_uganda %>% select(District, year, Locus, freq)
#add long and lat to dataframe for plotting
pie_data$lat <- NA
pie_data$long <- NA
for (i in unique(uganda$name)){
  pie_data$lat[pie_data$District == i] <- rep(uganda$latitude[uganda$name == i], sum((pie_data$District == i)))
  pie_data$long[pie_data$District == i] <- rep(uganda$longitude[uganda$name == i], sum((pie_data$District == i)))
}

pie_data <- pie_data %>%
  pivot_wider(values_from = freq, names_from = Locus) %>%
  #mutate(WT = 1-PfK13) %>%
  mutate(radius = K13) %>%
  filter(radius >0)

#rescale radius
minr<-min(pie_data$radius)  # min in the data original scale
maxr<-max(pie_data$radius)  # max in the data original scale
min_scale<-0.1  ## min in the new scale
max_scale<-0.45 ## max in the new scale
pie_data$radius_adj <- min_scale + (max_scale-min_scale)*pie_data$radius/(maxr-minr)
write.csv(pie_data, file = paste0(fileLocManuscript,"/supplement/Figure2_UgandaMap/Figure2_stas.csv"))
```

## Plotting
```{r}
# make plot with wild_type
pie_chart_size <- c(1, 4, 3, 2.5, 2, 2, 1.5)
count <- 0
for (y in 2016:2022){
  count <- count + 1
  pie_chart_df <- pie_data %>% filter(year == y)
  val <- 1
  map_uganda <- ggplot() +
  geom_sf(data=sov110, color='black', size=0.3, fill = ifelse(sov110$ADMIN == "Uganda", 'grey98', 'grey90')) +
  geom_sf(data=uganda, fill = "moccasin") +
  geom_sf(data=lakes8, color="grey40", fill ="aliceblue", size= 0.5) +
  geom_sf(data=admin8, color="grey80", size= 0.6) +
  geom_sf(data=admin110, color="grey80", size= 0.4) +
  annotation_scale(location = "bl", width_hint = 0.3, height = unit(0.1, "cm")) +
  annotation_north_arrow(location = "bl", which_north = "true",
                         pad_x = unit(0.25, "in"), pad_y = unit(0.15, "in"),
                         style = north_arrow_fancy_orienteering, height = unit(1, "cm"), width = unit(1, "cm")) +
  coord_sf(xlim = c(28.5, 35), ylim = c(4 ,-2), expand = TRUE) +
  annotate("text", x = 34.8, y = 0.5, label = "Kenya",
           color="grey50", size=4 , fontface="italic") +
  annotate("text", x = 29.4, y = 1.2, label = "Democratic Republic \n of the Congo",
           color="grey50", size=4 , fontface="italic") +
  annotate("text", x = 30.2, y = -1.7, label = "Rwanda",
           color="grey50", size=4 , fontface="italic") +
  annotate("text", x = 31.4, y = 3.956, label = "South Sudan",
           color="grey50", size=4 , fontface="italic") +
  annotate("text", x = 34.5, y = -2, label = "Tanzania",
           color="grey50", size=4 , fontface="italic") +
  theme_minimal() + 
  annotate(geom = "text", x = 31, y = -0.5, label = "Uganda", fontface = "bold", color = "black", size = 6) +
  annotate(geom = "text", x = 33, y = -1, label = "Lake Victoria", 
           fontface = "italic", color = "grey50", size = 5) +
  xlab("") +
  ylab("") +
  geom_scatterpie(data = pie_chart_df, 
                  aes(x=long, y=lat, group=District, r = radius_adj), 
                  cols=c("A675V", "C469F", "C469Y", "R561H", "P441L")) +
  geom_scatterpie_legend(pie_chart_df$radius_adj*val,
                         x=28.7, y=2.0,
                         labeller = function(x) round((x*0.5441068-0.1)/0.35 *100)) + #convert adjusted radius size back to the mutant/genotyped
    # geom_scatterpie_legend(pie_chart_df$radius_adj*val, 
    #                    x=28.7, y=2.0, 
    #                    labeller = function(x) round(x*100)) +
    scale_fill_manual(values = c("#D55E00",
                               "#0072B2",
                               "#009E73",
                               "#F0E442",
                               "#59386c"),
                      labels = c("675V",
                                "469F",
                                "469Y",
                                "561H",
                                "441L"),
                      name = "") +
  theme(legend.text=element_text(size=10), 
        axis.text = element_text(size = 10), 
        legend.position = c(0.085,0.89))
  
  ggsave(
  paste0(
    fileLocManuscript,
    paste0("/supplement/Figure2_UgandaMap/Figure2_MapUganda", y,".pdf")
  ),
  map_uganda,
  width = 6,
  height = 5.5,
  dpi = 700
  )
  ggsave(
    paste0(
      fileLocManuscript,
      paste0("/supplement/Figure2_UgandaMap/Figure2_MapUganda", y,".png")
    ),
    map_uganda,
    width = 6,
    height = 5.5,
    dpi = 700
  )
}

```


# Figure 3
## Figure 3A: SE Asia allele frequency
### allele frequency plot overview
```{r}
SEA_freq_plot <- df_comb_pfk7 %>%
  ggplot(aes(x = year, y = freq, fill=Locus, color = Locus)) +
  geom_bar(stat = "identity", position = position_dodge2(preserve = "single")) +
  theme_bw() +
  scale_color_manual("Mutations",
    values = c("#56B4E9",
               "#BBBBBB",
               "#009E73",
               "#E69F00"),
    labels = c("580Y",
               "K13",
               "other K13",
               "539T")) +
  scale_fill_manual("Mutations",
    values = c("#56B4E9",
               "#BBBBBB",
               "#009E73",
               "#E69F00"),
    labels = c("580Y",
               "K13",
               "other K13",
               "539T")) +
  xlab("Year") +
  ylab("Allele frequency") +
  scale_x_continuous("Year",  
                     breaks = seq(2001, 2018, 2)) +
  theme(legend.title=element_blank(), 
        axis.text = element_text(size = 10), 
        axis.title=element_text(size=12), 
        legend.text=element_text(size=10), 
        strip.text.x = element_text(size = 10), 
        legend.position = c(.2 , .99), 
        legend.justification = c("right", "top"), 
        legend.box.just = "right", 
        legend.margin = margin(1, 1, 1, 1))
```

### Saving plot
```{r}
ggsave(
  paste0(fileLocManuscript, "/supplement/Figure3_SEA_allele_frequency_map/SEAsia_prevalence.pdf"),
  SEA_freq_plot,
  width = 6,
  height = 6.25,
  dpi = 700
)
ggsave(
  paste0(fileLocManuscript, "/supplement/Figure3_SEA_allele_frequency_map/SEAsia_prevalence.png"),
  SEA_freq_plot,
  width = 6,
  height = 6.25,
  dpi = 700
)
```

## Figure 3B: SE Asia Map
### Download maps
```{r}
#load base map layers
admin8 <-
  ne_download(
    scale = "large",
    type = "admin_1_states_provinces_lines",
    category = "cultural",
    returnclass = "sf"
  )
rivers8 <- ne_download(
  scale = 10,
  type = 'rivers_lake_centerlines',
  category = 'physical',
  returnclass = "sf"
)
lakes8 <- ne_download(
  scale = "large",
  type = 'lakes',
  category = 'physical',
  returnclass = "sf"
)
sov110 <- ne_download(
  scale = "medium",
  type = "sovereignty",
  category = "cultural",
  returnclass = "sf"
)
admin110 <- ne_download(
  scale = "large",
  type = "populated_places",
  category = "cultural",
  returnclass = "sf"
)

pt.lim = data.frame(xlim = c(28.5, 35.5), ylim = c(4.25, -3))
pt.bbox <- st_bbox(c(
  xmin = pt.lim$xlim[1],
  xmax = pt.lim$xlim[2],
  ymin = pt.lim$ylim[1],
  ymax = pt.lim$ylim[2]
))
```

### Preprocessing - getting SE Asia specific boarder, country and water information
```{r}
#adjust names of Districts
SEA_map <- ne_states(country = unique(df_pfk7$country),
            returnclass = "sf") %>%
  #st_crop(pt.bbox) %>%
  select(name, admin, latitude, longitude) %>%
  arrange(name) %>% arrange(admin) %>%
  mutate(
    name = str_replace(name, "Batdâmbâng", "Battambang"),
    name = str_replace(name, "Kaôh Kong", "Koh Kong"),
    name = str_replace(name, "Krong Pailin", "Pailin"),
    name = str_replace(name, "Preah Vihéar", "Preah Vihear"),
    name = str_replace(name, "Pouthisat", "Pursat"),
    name = str_replace(name, "Si Sa Ket", "Sisakhet"),
    name = str_replace(name, "Rôtânôkiri", "Ratanakiri"),
    name = str_replace(name, "Attapu", "Attapeu"),
    name = str_replace(name, "Saravan", "Salavan"),
    name = str_replace(name, "Savannakhét", "Savannakhet"),
    name = str_replace(name, "Xékong", "Sekong"),
    name = str_replace(name, "Khánh Hòa", "Khanh Hoa"),
    name = str_replace(name, "Quàng Nam", "Quang Nam")
  )

#add Latitude for Districts that are not in the database
SEA_map$name[SEA_map$latitude == 9.33941] <- "Bac Lieu"
SEA_map$name[SEA_map$latitude == 11.6805] <- "Binh Phuoc"
SEA_map$name[SEA_map$latitude == 11.1284] <- "Binh Thuan"
SEA_map$name[SEA_map$latitude == 12.7691] <- "Dak Lak"
SEA_map$name[SEA_map$latitude == 12.1425] <- "Dak Nong"
SEA_map$name[SEA_map$latitude == 11.6242] <- "Ninh Thuan"
SEA_map$name[SEA_map$latitude == 16.7204] <- "Quang Tri"
SEA_map$name[SEA_map$latitude == 13.6662] <- "Stueng Traeng"

#filter districts that are in SE Asia
SEA_map <- SEA_map  %>% 
  filter(name %in% unique(df_pfk7$District)) %>% 
  na.omit() %>% 
  arrange(name)

#adjust districts that contain non 
r539t_district <- df_pfk7 %>% 
  filter(Locus == "R539T") %>% 
  distinct(District)

c580y_district <- df_pfk7 %>% 
  filter(Locus == "C580Y") %>% 
  distinct(District)

c580y_r539t_district <- r539t_district %>%
  filter(District %in% c580y_district$District)
c580y_district <- c580y_district %>%
  filter(!District %in% c580y_r539t_district$District)

c580y_r539t_district <- c580y_r539t_district$District
c580y_district <- c580y_district$District

allkelch_district <- df_pfk7 %>% 
  filter(Locus == "other_K13") %>% 
  distinct(District)
allkelch_district <- array(t(allkelch_district))
allkelch_district <- allkelch_district[!allkelch_district %in% c580y_r539t_district]

#label colors for map
SEA_map$color <- "not_enough_samples"
SEA_map$color[SEA_map$name %in% c580y_r539t_district] <- "r539t_c580y" #combined
SEA_map$color[SEA_map$name %in% c580y_district] <- "c580y" #combined
SEA_map$color[SEA_map$name %in% allkelch_district] <- "other K13" #only other kelch mutants

SEA_map_c580y <- SEA_map %>% filter(color == "c580y")
SEA_map_other <- SEA_map %>% filter(color == "other K13")
SEA_map_r539t_c580y <- SEA_map %>% filter(color == "r539t_c580y")
```

### Plotting
```{r}
# make plot with wild_type
map_SEAsia <- ggplot() +
  geom_sf(data = sov110,
          color = 'black',
          size = 0.3,
          fill = ifelse(sov110$ADMIN %in% c("Laos", "Thailand", "Cambodia", "Vietnam", "Myanmar"), 'grey98', 'grey90')) +
  geom_sf(data = SEA_map_c580y, 
          fill = "#56B4E9") +
  geom_sf(data = SEA_map_other, 
          fill = "#009E73") +
  geom_sf(data = SEA_map_r539t_c580y, 
          fill = "#E69F00") +
  geom_sf(data = lakes8,
          color = "grey40",
          fill = "aliceblue",
          size = 0.5) +
  geom_sf(data = admin8,
          color = "grey80", 
          size = 0.6) +
  geom_sf(data = admin110, 
          color = "grey80", 
          size = 0.4) +
  annotation_scale(location = "bl",
                   width_hint = 0.3,
                   height = unit(0.1, "cm")) +
  annotation_north_arrow(location = "bl",
                         which_north = "true",
                         pad_x = unit(0.25, "in"),
                         pad_y = unit(0.15, "in"),
                         style = north_arrow_fancy_orienteering,
                         height = unit(1, "cm"),
                         width = unit(1, "cm")) +
  coord_sf(xlim = c(111, 92.5),
           ylim = c(6.5, 28),
           expand = TRUE) +
  annotate("text", 
           x = 102.5, 
           y = 20,
           label = "Laos",
           color = "black",
           size = 4,
           fontface = "bold") +
  annotate("text",
           x = 101.5,
           y = 16,
           label = "Thailand",
           color = "black",
           size = 4,
           fontface = "bold") +
  annotate("text",
           x = 105.9,
           y = 12.8,
           label = "Cambodia",
           color = "black",
           size = 4,
           fontface = "bold") +
  annotate("text",
           x = 104.9,
           y = 21.5,
           label = "Vietnam",
           color = "black",
           size = 4,
           fontface = "bold") +
  annotate("text",
           x = 95.2,
           y = 16.9,
           label = "Myanmar",
           color = "black",
           size = 4,
           fontface = "bold") +
  annotate("text",
           x = 102,
           y = 24,
           label = "China",
           color = "grey50",
           size = 4,
           fontface = "italic") +
  theme_minimal() +
  xlab("") +
  ylab("") +
  theme(legend.text = element_text(size = 10),
    axis.text = element_text(size = 10),
    legend.position = c(0.86, 0.95)
  )
```

### Saving plot
```{r}
ggsave(
  paste0(
    fileLocManuscript,
    "/supplement/Figure3_SEA_allele_frequency_map/SEAsia_map.pdf"
  ),
  map_SEAsia,
  width = 5.625,
  height = 6.25,
  dpi = 700
)
ggsave(
  paste0(
    fileLocManuscript,
    "/supplement/Figure3_SEA_allele_frequency_map/SEAsia_map.png"
  ),
  map_SEAsia,
  width = 5.625,
  height = 6.25,
  dpi = 700
)
```

# Figure 4: Overview of data plot SE Asia (PfK7 data) - included in analysis
```{r}
#load data
pfk7_data_analysis <- df_pfk7 %>% 
  filter(Locus != "other_K13") %>%
  filter(!(Locus == "K13" & District == "Binh Phuoc" & year == 2005)) %>%
  group_by(Locus, District) %>%
  mutate(min_year = min(year[freq>0]))

pfk7_data_analysis <- pfk7_data_analysis %>% 
  group_by(Locus, District) %>%
  filter(min_year <= 2010,
         year >= min_year & year <= min_year + 4, #filter for the first five years,
         nobs > numofobs) %>% #remove all distrcit where the first non-zero prevalence is larger than 50%
  arrange(Locus, District, year) %>%
  mutate(point_format = 19)

pfk7_data_notanalysis <- df_pfk7 %>% 
  filter(Locus != "other_K13", 
         nobs > numofobs,
         is.finite(lrsmed)) %>%
  mutate(point_format = 1)

plot_overview_seAsia <- 
  ggplot() +
  geom_point(data = pfk7_data_analysis, aes(year, freq, group = Locus, color = Locus, size = n), shape = 19) + 
  geom_point(data = pfk7_data_notanalysis, aes(year, freq, group = Locus, color = Locus, size = n), shape = 1) + 
  scale_size_binned(name = "Sample Size", range = c(0.2,3)) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country+District) +
  ylab("Allele frequency") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual("Mutations",
    values = c("#56B4E9", "#E69F00", "#009E73"),
    labels = c("580Y", "K13", "539T")) +
  theme(
    axis.line = element_line(),
    legend.title = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 8),
    strip.text.x = element_text(size = 8),
    legend.position = "right",
    legend.box = "vertical"
  )
```

### Saving plot
```{r}
ggsave(
  paste0(fileLocManuscript, "/supplement/Figure4_SEA_data_overview/SEA_dataoverview.pdf"),
  plot_overview_seAsia,
  width = 7,
  height = 6,
  dpi = 700
)
ggsave(
  paste0(fileLocManuscript, "/supplement/Figure4_SEA_data_overview/SEA_dataoverview.png"),
  plot_overview_seAsia,
  width = 7,
  height = 6,
  dpi = 700
)
```


