---
title: "Supplement -Klech Selection Coefficient Modeling"
output: html_document
date: "2023-05-06"
---

```{r setup, include=FALSE}
library(lme4)
library(nlme)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(scales)
library(tidyverse)
library(cowplot)
library(tabulizer)
library(RColorBrewer)
library(tidyverse) # ggplot2, dplyr, tidyr, readr, purrr, tibble
library(rnaturalearth)
library(rnaturalearthdata)
library(sf) #see ubuntu issues here: https://rtask.thinkr.fr/installation-of-r-4-0-on-ubuntu-20-04-lts-and-tips-for-spatial-packages/
library(ggspatial)
library(scatterpie)
library(scales)
library (ggforce)
library (ggmap)
library(rstan)
library(gt)
library(ggbreak) 
## install.packages("rstan", repos = c("https://mc-stan.org/r-packages/", getOption("repos")))
```

# Load data
```{r}
#load data
df_uganda <- read.table("data/data-derived/Ugandan_data.txt")
df_pfk7 <- read.table("data/data-derived/pfk7_data.txt")
figure5_pfk7_data <- read.table("data/data-derived/supplement-figure5-pfk7_data.txt")
figure5_forecasting <- read.table("data/data-derived/supplement-figure5-forecasting.txt")
#set the limit of number of observations
numofobs <- 2

fileLocManuscript <- "figures"
```

# Figure1: Overview of data plot Uganda with more than two observations --> data included in analysis
```{r}
plot_overview_uganda <- df_uganda %>%
  filter(nobs > numofobs) %>% 
  ggplot(aes(year, med * 100, group = Locus, color = Locus)) +
  geom_point(aes(size = n)) +
  scale_size_binned(name = "Sample Size",range = c(0.2,2.5)) +
  labs(shape = "Mutations", 
       size = "Sample Size") +
  theme_bw() +
  facet_wrap( ~ District) +
  ylab("Prevalence") +
  xlab("Year") +
  scale_color_manual("Mutations",
    values = c("#D55E00", 
               "#0072B2", 
               "#009E73", 
               "#F0E442"),
    labels = c("675V", 
               "469F", 
               "469Y", 
               "561H")
  ) +
  ggpubr::theme_pubclean(base_size = 12) +
  theme(
    axis.line = element_line(),
    legend.title = element_text(size = 12),
    axis.text = element_text(size = 9),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    strip.text.x = element_text(size = 10),
    legend.position = c(0.85, 0.1),
    legend.box = "horizontal"
  )
```

### Saving plot
```{r}
ggsave(
  paste0(fileLocManuscript, "/supplement/Figure1-Uganda-DataOverview-Analysis/Uganda_dataoverview.pdf"),
  plot_overview_uganda,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(fileLocManuscript, "/supplement/Figure1-Uganda-DataOverview-Analysis/Uganda_dataoverview.png"),
  plot_overview_uganda,
  width = 8,
  height = 5,
  dpi = 700
)
```

# Figure2: Overview of data plot Uganda with less than three observations --> data not included in analysis
```{r}
plot_overview_uganda <- df_uganda %>%
  filter(nobs <= numofobs) %>% 
  ggplot(aes(year, med * 100, group = Locus, color = Locus)) +
  geom_point(aes(size = n)) +
  scale_size_binned(name = "Sample Size",
                    range = c(0.2,2.5)) +
  labs(shape = "Mutations", 
       size = "Sample Size") +
  theme_bw() +
  facet_wrap( ~ District) +
  ylab("Prevalence") +
  xlab("Year") +
  scale_color_manual("Mutations",
    values = c("#D55E00", 
               "#0072B2", 
               "#009E73", 
               "#F0E442"),
    labels = c("675V", 
               "469F", 
               "469Y", 
               "561H")
  ) +
  ggpubr::theme_pubclean(base_size = 12) +
  theme(
    axis.line = element_line(),
    legend.title = element_text(size = 12),
    axis.text = element_text(size = 9),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    strip.text.x = element_text(size = 10),
    legend.position = "right", #c(0.94, 0.07)
  )
```

### Saving plot
```{r}
ggsave(
  paste0(fileLocManuscript, "/supplement/Figure2-Uganda-DataOverview-NotAnalysis/Uganda_dataoverview.pdf"),
  plot_overview_uganda,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(fileLocManuscript, "/supplement/Figure2-Uganda-DataOverview-NotAnalysis/Uganda_dataoverview.png"),
  plot_overview_uganda,
  width = 8,
  height = 5,
  dpi = 700
)
```

# Figure 3: Uganda Map for 2016-2020
## Download map components
```{r}
#load base map layers
admin8 <- ne_download(scale="large", type = "admin_1_states_provinces_lines",
                      category = "cultural", returnclass = "sf")
rivers8 <- ne_download(scale = 10, type = 'rivers_lake_centerlines',
                       category = 'physical', returnclass = "sf")
lakes8 <- ne_download(scale = "large", type = 'lakes',
                      category = 'physical', returnclass = "sf")
sov110 <- ne_download(scale="medium", type = "sovereignty",
                      category = "cultural", returnclass = "sf")
admin110 <- ne_download(scale="large", type = "populated_places",
                        category = "cultural", returnclass = "sf")
kampala <- data.frame(name="Kampala", long=32.5833, lat=0.31666)

pt.lim = data.frame(xlim = c(28.5, 35.5), ylim = c(4.25,-3))
pt.bbox <- st_bbox(c(xmin=pt.lim$xlim[1],
           xmax=pt.lim$xlim[2],
           ymin=pt.lim$ylim[1],
           ymax=pt.lim$ylim[2]))

#get uganda specific information
uganda <- ne_states(country="Uganda", returnclass = "sf") %>% 
  st_crop(pt.bbox) %>% 
  select(name, latitude, longitude) %>%
  arrange(name)
uganda$name[uganda$name == "Kabale"] <- "Rukiga"
uganda <- uganda %>% 
  filter(name %in% unique(df_uganda$District)) %>% 
  na.omit() %>% arrange(name)
```

## Data Preprocessing
```{r}
#sum prevalence per Locus and District
pie_data <- df_uganda %>% 
  mutate(sum_district_locus = x) %>%
  select(year, District, Locus, sum_district_locus) %>% 
  distinct(District, Locus, year, .keep_all = TRUE) %>% 
  ungroup() 

#sum sample size for each District
all_genotyped <- df_uganda %>% 
  group_by(District, year) %>% 
  mutate(sum_district_locus = sum(n)) %>% 
  select(year, District, sum_district_locus) %>% 
  distinct(District, year, .keep_all = TRUE) %>% 
  ungroup() 

#add all genotyped data to dataframe as additional rows
pie_data <- pie_data %>% 
  add_row(year = all_genotyped$year, 
          District = all_genotyped$District,
          Locus = rep("AllGenotyped", length(all_genotyped$District)), 
          sum_district_locus = all_genotyped$sum_district_locus) %>% 
  arrange(District) %>% 
  ungroup

#add long and lat to dataframe for plotting
pie_data$lat <- NA
pie_data$long <- NA
for (i in unique(pie_data$District)){
  pie_data$lat[pie_data$District == i] <- rep(uganda$latitude[uganda$name == i], sum((pie_data$District == i)))
  pie_data$long[pie_data$District == i] <- rep(uganda$longitude[uganda$name == i], sum((pie_data$District == i)))
}

#initialize rows for each mutation and all genotyped
pie_data2 <- pie_data %>% select(year, District, lat, long) %>% distinct(year, District, .keep_all = TRUE)
pie_data2$A675V <- NA
pie_data2$C469Y <- NA
pie_data2$C469F <- NA
pie_data2$R561H <- NA
pie_data2$AllGenotyped <- NA

#obtain districts that obtain each mutation
C469Y_dist <- unique(df_uganda$District[df_uganda$Locus == "C469Y"])
A675V_dist <- unique(df_uganda$District[df_uganda$Locus == "A675V"])
C469F_dist <- unique(df_uganda$District[df_uganda$Locus == "C469F"])
R561H_dist <- unique(df_uganda$District[df_uganda$Locus == "R561H"])

#add prevalence for each mutation to dataframe
pie_data2$A675V[pie_data2$District %in% A675V_dist] <- pie_data$sum_district_locus[pie_data$Locus == "A675V"]
pie_data2$C469Y[pie_data2$District %in% C469Y_dist] <- pie_data$sum_district_locus[pie_data$Locus == "C469Y"]
pie_data2$C469F[pie_data2$District %in% C469F_dist] <- pie_data$sum_district_locus[pie_data$Locus == "C469F"]
pie_data2$R561H[pie_data2$District %in% R561H_dist] <- pie_data$sum_district_locus[pie_data$Locus == "R561H"]
pie_data2$AllGenotyped <- pie_data$sum_district_locus[pie_data$Locus == "AllGenotyped"]
pie_data2[is.na(pie_data2)] <- 0

pie_data2$radius <- (pie_data2$A675V + pie_data2$C469Y + pie_data2$C469F + pie_data2$R561H) / pie_data2$AllGenotyped

#rescale radius
minr<-min(pie_data2$radius)  # min in the data original scale
maxr<-max(pie_data2$radius)  # max in the data original scale
min_scale<-0.1  ## min in the new scale
max_scale<-0.4 ## max in the new scale
pie_data2$radius_adj <- min_scale+ (max_scale-min_scale)*pie_data2$radius/(maxr-minr)
```
## Plotting
```{r}
# make plot with wild_type
pie_chart_size <- c(6, 5, 4, 2.5, 2,2)
count <- 0
for (y in 2016:2021){
  count <- count + 1
  pie_chart_df <- pie_data2 %>% filter(year == y)
  val <- pie_chart_size[count]
  map <- ggplot() +
  geom_sf(data=sov110, color='black', size=0.3, fill = ifelse(sov110$ADMIN == "Uganda", 'grey98', 'grey90')) +
  geom_sf(data=uganda, fill = "moccasin") +
  geom_sf(data=lakes8, color="grey40", fill ="aliceblue", size= 0.5) +
  geom_sf(data=admin8, color="grey80", size= 0.6) +
  geom_sf(data=admin110, color="grey80", size= 0.4) +
  annotation_scale(location = "bl", width_hint = 0.3, height = unit(0.1, "cm")) +
  annotation_north_arrow(location = "bl", which_north = "true",
                         pad_x = unit(0.25, "in"), pad_y = unit(0.15, "in"),
                         style = north_arrow_fancy_orienteering, height = unit(1, "cm"), width = unit(1, "cm")) +
  coord_sf(xlim = c(28.5, 35), ylim = c(4 ,-2), expand = TRUE) +
  annotate("text", x = 34.8, y = 0.5, label = "Kenya",
           color="grey50", size=4 , fontface="italic") +
  annotate("text", x = 29.4, y = 1.2, label = "Democratic Republic \n of the Congo",
           color="grey50", size=4 , fontface="italic") +
  annotate("text", x = 30.2, y = -1.7, label = "Rwanda",
           color="grey50", size=4 , fontface="italic") +
  annotate("text", x = 31.4, y = 3.956, label = "South Sudan",
           color="grey50", size=4 , fontface="italic") +
  annotate("text", x = 34.5, y = -2, label = "Tanzania",
           color="grey50", size=4 , fontface="italic") +
  theme_minimal() + 
  annotate(geom = "text", x = 31, y = -0.5, label = "Uganda", fontface = "bold", color = "black", size = 6) +
  annotate(geom = "text", x = 33, y = -1, label = "Lake Victoria", 
           fontface = "italic", color = "grey50", size = 5) +
  xlab("") +
  ylab("") +
  geom_scatterpie(data = pie_chart_df, 
                  aes(x=long, y=lat, group=District, r = radius_adj), 
                  cols=c("A675V", "C469F", "C469Y", "R561H")) +
  geom_scatterpie_legend(pie_chart_df$radius*val, 
                         x=28.7, y=2.3, 
                         labeller = function(x) round(x * 100/val)) +
    scale_fill_manual(values = c("#D55E00", 
                                 "#0072B2", 
                                 "#009E73", 
                                 "#F0E442"), 
                      labels = c("675V", 
                                 "469F", 
                                 "469Y", 
                                 "561H"), 
                      name = "")  +
  theme(legend.text=element_text(size=10), 
        axis.text = element_text(size = 10), 
        legend.position = c(0.085,0.91))
  
    ggsave(
  paste0(
    fileLocManuscript,
    paste0("/supplement/Figure3-UgandaMap/Figure3_MapUganda", y,".pdf")
  ),
  map,
  width = 6,
  height = 5.5,
  dpi = 700
  )
  ggsave(
    paste0(
      fileLocManuscript,
      paste0("/supplement/Figure3-UgandaMap/Figure3_MapUganda", y,".png")
    ),
    map,
    width = 6,
    height = 5.5,
    dpi = 700
  )
}

```


# Figure 4
## Figure 4A: SE Asia Prevalence
### Prevalence plot overview
```{r}
prev_df <- df_pfk7 %>% 
  group_by(year, Locus) %>% 
  filter(Locus != "PfK13") %>%
  mutate(all_genotyped = sum(n), mut_sample = sum(x)) %>%
  distinct(all_genotyped, mut_sample) %>%
  mutate(prop_sample = mut_sample / all_genotyped) %>%
  ungroup

prev <- prev_df %>%
  ggplot(aes(x = year, y = prop_sample, fill = Locus)) +
  geom_col() +
  theme_bw() +
  scale_fill_manual("Mutations",
    values = c("#56B4E9", 
               "#E69F00", 
               "#009E73"),
    labels = c("580Y", 
               "other PfK13", 
               "539T")) +
  xlab("Year") +
  ylab("Allele frequency") +
  ylim(0,1) +
  scale_x_continuous(breaks = seq(1993, 2018, 3)) +
  theme(
    legend.title = element_blank(),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    strip.text.x = element_text(size = 10),
    legend.position = c(0.18, 0.9)
  )
```

### Saving plot
```{r}
ggsave(
  paste0(fileLocManuscript, "/supplement/Figure4-SEAsia-PrevMap/SEAsia_prevalence.pdf"),
  prev,
  width = 4.5,
  height = 6.25,
  dpi = 700
)
ggsave(
  paste0(fileLocManuscript, "/supplement/Figure4-SEAsia-PrevMap/SEAsia_prevalence.png"),
  prev,
  width = 4.5,
  height = 6.25,
  dpi = 700
)
```

## Figure 4B: SE Asia Map
### Download maps
```{r}
#load base map layers
admin8 <-
  ne_download(
    scale = "large",
    type = "admin_1_states_provinces_lines",
    category = "cultural",
    returnclass = "sf"
  )
rivers8 <- ne_download(
  scale = 10,
  type = 'rivers_lake_centerlines',
  category = 'physical',
  returnclass = "sf"
)
lakes8 <- ne_download(
  scale = "large",
  type = 'lakes',
  category = 'physical',
  returnclass = "sf"
)
sov110 <- ne_download(
  scale = "medium",
  type = "sovereignty",
  category = "cultural",
  returnclass = "sf"
)
admin110 <- ne_download(
  scale = "large",
  type = "populated_places",
  category = "cultural",
  returnclass = "sf"
)

pt.lim = data.frame(xlim = c(28.5, 35.5), ylim = c(4.25, -3))
pt.bbox <- st_bbox(c(
  xmin = pt.lim$xlim[1],
  xmax = pt.lim$xlim[2],
  ymin = pt.lim$ylim[1],
  ymax = pt.lim$ylim[2]
))
```

### Preprocessing - getting SE Asia specific boarder, country and water information
```{r}
#adjust names of Districts
SE_asia <-
  ne_states(country = unique(df_pfk7$country),
            returnclass = "sf") %>%
  #st_crop(pt.bbox) %>%
  select(name, admin, latitude, longitude) %>%
  arrange(name) %>% arrange(admin) %>%
  mutate(
    name = str_replace(name, "Batdâmbâng", "Battambang"),
    name = str_replace(name, "Kaôh Kong", "Koh Kong"),
    name = str_replace(name, "Krong Pailin", "Pailin"),
    name = str_replace(name, "Preah Vihéar", "Preah Vihear"),
    name = str_replace(name, "Pouthisat", "Pursat"),
    name = str_replace(name, "Si Sa Ket", "Sisakhet"),
    name = str_replace(name, "Rôtânôkiri", "Ratanakiri"),
    name = str_replace(name, "Attapu", "Attapeu"),
    name = str_replace(name, "Saravan", "Salavan"),
    name = str_replace(name, "Savannakhét", "Savannakhet"),
    name = str_replace(name, "Xékong", "Sekong"),
    name = str_replace(name, "Khánh Hòa", "Khanh Hoa"),
    name = str_replace(name, "Quàng Nam", "Quang Nam")
  )

#add Latitude for Districts that are not in the database
SE_asia$name[SE_asia$latitude == 9.33941] <- "Bac Lieu"
SE_asia$name[SE_asia$latitude == 11.6805] <- "Binh Phuoc"
SE_asia$name[SE_asia$latitude == 11.1284] <- "Binh Thuan"
SE_asia$name[SE_asia$latitude == 12.7691] <- "Dak Lak"
SE_asia$name[SE_asia$latitude == 12.1425] <- "Dak Nong"
SE_asia$name[SE_asia$latitude == 11.6242] <- "Ninh Thuan"
SE_asia$name[SE_asia$latitude == 16.7204] <- "Quang Tri"
SE_asia$name[SE_asia$latitude == 13.6662] <- "Stueng Traeng"

#filter districts that are in SE Asia
SE_asia <- SE_asia  %>% 
  filter(name %in% unique(df_pfk7$District)) %>% 
  na.omit() %>% 
  arrange(name)

#adjust districts that contain non 
r539t_district <- df_pfk7 %>% 
  filter(Locus == "R539T", is.finite(lrsmed), nobs > numofobs) %>% 
  distinct(District)
r539t_district <- array(t(r539t_district))

c580y_district <- df_pfk7 %>% 
  filter(Locus == "C580Y", is.finite(lrsmed), nobs > numofobs) %>% 
  distinct(District)
c580y_district <- array(t(c580y_district))

allkelch_district <- df_pfk7 %>% 
  filter(Locus == "other_PfK13", is.finite(lrsmed), nobs > numofobs) %>% 
  distinct(District)
allkelch_district <- array(t(allkelch_district))

#label colors for map
SE_asia$color <- "not_enough_samples"
SE_asia$color[SE_asia$name %in% r539t_district] <- "r539t" #combined
SE_asia$color[SE_asia$name %in% c580y_district] <- "c580y" #combined
SE_asia$color[SE_asia$name %in% allkelch_district] <- "other PfK13" #only other kelch mutants

#sum prevalence per Locus and District
pie_data <- df_pfk7 %>% 
  group_by(Locus, District) %>% 
  mutate(sum_district_locus = sum(x)) %>% 
  filter(Locus != "PfK13") %>%
  select(District, Locus, sum_district_locus) %>% 
  distinct(District, Locus, .keep_all = TRUE) %>% 
  ungroup() 
#sum sample size for each District
all_genotyped <- df_pfk7 %>% 
  group_by(District) %>% 
  mutate(sum_district_locus = sum(n)) %>% 
  select(District, sum_district_locus) %>% 
  distinct(District, .keep_all = TRUE) %>% 
  ungroup() 

#add wild-type to dataframe
pie_data <- pie_data %>% 
  add_row(District = unique(all_genotyped$District), 
          Locus = rep("AllGenotyped", dim(all_genotyped)[1]), 
          sum_district_locus = all_genotyped$sum_district_locus) %>% 
  arrange(District) %>% 
  ungroup

#add long and lat to dataframe for plotting
pie_data$lat <- NA
pie_data$long <- NA
for (i in unique(pie_data$District)) {
  pie_data$lat[pie_data$District == i] <-
    rep(SE_asia$latitude[SE_asia$name == i], sum((pie_data$District == i)))
  pie_data$long[pie_data$District == i] <-
    rep(SE_asia$longitude[SE_asia$name == i], sum((pie_data$District == i)))
}

#initialize rows for each mutation and WT
pie_data2 <- pie_data %>% 
  select(District, lat, long) %>% 
  distinct(District, .keep_all = TRUE)
pie_data2$c580y <- NA
pie_data2$r539t <- NA
pie_data2$other_PfK13 <- NA
pie_data2$AllGenotyped <- NA

#obtain districts that obtain each mutation
C580Y_dist <- unique(df_pfk7$District[df_pfk7$Locus == "C580Y"])
R539T_dist <- unique(df_pfk7$District[df_pfk7$Locus == "R539T"])
other_PfK13_dist <- unique(df_pfk7$District[df_pfk7$Locus == "other_PfK13"])

#add prevalence for each mutation to dataframe
pie_data2$c580y[match(C580Y_dist, pie_data2$District)] <- pie_data$sum_district_locus[pie_data$Locus == "C580Y"]
pie_data2$r539t[match(R539T_dist, pie_data2$District)] <- pie_data$sum_district_locus[pie_data$Locus == "R539T"]
pie_data2$other_PfK13[match(other_PfK13_dist, pie_data2$District)] <- pie_data$sum_district_locus[pie_data$Locus == "other_PfK13"]
pie_data2$AllGenotyped <- pie_data$sum_district_locus[pie_data$Locus == "AllGenotyped"]
pie_data2[is.na(pie_data2)] <- 0

pie_data2$radius <- (pie_data2$c580y + pie_data2$r539t + pie_data2$other_PfK13) / pie_data2$AllGenotyped
#rescale radius
minr <- min(pie_data2$radius)  # min in the data original scale
maxr <- max(pie_data2$radius)  # max in the data original scale

min_scale <- 0.3  ## min in the new scale
max_scale <- 0.7 ## max in the new scale

pie_data2$radius_adj <-
  min_scale + (max_scale - min_scale) * pie_data2$radius / (maxr - minr)
pie_data <- pie_data2
```

### Plotting
```{r}
# make plot with wild_type
map_SEAsia <- ggplot() +
  geom_sf(data = sov110,
          color = 'black',
          size = 0.3,
          fill = ifelse(sov110$ADMIN %in% c("Laos", "Thailand", "Cambodia", "Vietnam", "Myanmar"), 'grey98', 'grey90')) +
  geom_sf(data = SE_asia, 
          fill = "moccasin") +
  geom_sf(data = lakes8,
          color = "grey40",
          fill = "aliceblue",
          size = 0.5) +
  geom_sf(data = admin8,
          color = "grey80", 
          size = 0.6) +
  geom_sf(data = admin110, 
          color = "grey80", 
          size = 0.4) +
  annotation_scale(location = "bl",
                   width_hint = 0.3,
                   height = unit(0.1, "cm")) +
  annotation_north_arrow(location = "bl",
                         which_north = "true",
                         pad_x = unit(0.25, "in"),
                         pad_y = unit(0.15, "in"),
                         style = north_arrow_fancy_orienteering,
                         height = unit(1, "cm"),
                         width = unit(1, "cm")) +
  coord_sf(xlim = c(109, 92.5),
           ylim = c(6.5, 28),
           expand = TRUE) +
  annotate("text", 
           x = 102.5, 
           y = 20,
           label = "Laos",
           color = "black",
           size = 3 ,
           fontface = "bold") +
  annotate("text",
           x = 101.5,
           y = 16,
           label = "Thailand",
           color = "black",
           size = 3,
           fontface = "bold") +
  annotate("text",
           x = 105.9,
           y = 12.8,
           label = "Cambodia",
           color = "black",
           size = 3 ,
           fontface = "bold") +
  annotate("text",
           x = 104.9,
           y = 21.5,
           label = "Vietnam",
           color = "black",
           size = 3,
           fontface = "bold") +
  annotate("text",
           x = 95.2,
           y = 16.9,
           label = "Myanmar",
           color = "black",
           size = 3,
           fontface = "bold") +
  annotate("text",
           x = 102,
           y = 24,
           label = "China",
           color = "grey50",
           size = 4,
           fontface = "italic") +
  theme_minimal() +
  xlab("") +
  ylab("") +
  geom_scatterpie(data = pie_data,
    aes(x = long, y = lat, group = District, r = radius_adj),
    cols = c("c580y", "r539t", "other_PfK13")) +
  geom_scatterpie_legend(pie_data$radius_adj*2,
                         x = 106,
                         y = 24, labeller = function(x) round(100*(34*x/2 - 10.2))) +
  scale_fill_manual(values = c("#56B4E9", 
                               "#009E73", 
                               "#E69F00"), 
                    labels = c("580Y", 
                               "539T", 
                               "other PfK13"), 
                    name = "")  +
  theme(legend.text = element_text(size = 10),
    axis.text = element_text(size = 10),
    legend.position = c(0.86, 0.95)
  )
```

### Saving plot
```{r}
ggsave(
  paste0(
    fileLocManuscript,
    "/supplement/Figure4-SEAsia-PrevMap/SEAsia_map.pdf"
  ),
  map_SEAsia,
  width = 5.625,
  height = 6.25,
  dpi = 700
)
ggsave(
  paste0(
    fileLocManuscript,
    "/supplement/Figure4-SEAsia-PrevMap/SEAsia_map.png"
  ),
  map_SEAsia,
  width = 5.625,
  height = 6.25,
  dpi = 700
)
```

# Figure 5: Overview of data plot SE Asia (PfK7 data) - included in analysis
```{r}
plot_overview_seAsia_included <- df_pfk7 %>% 
  filter(Locus != "other_PfK13", is.finite(lrsmed), nobs > numofobs) %>% 
  ggplot(aes(year, prev*100, group = Locus, color = Locus)) +
  geom_point(aes(size = n)) + 
  scale_size_binned(name = "Sample Size", range = c(0.2,3)) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country+District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual("Mutations",
    values = c("#56B4E9", "#E69F00", "#009E73"),
    labels = c("580Y", "PfK13", "539T")) +
  theme(
    axis.line = element_line(),
    legend.title = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    strip.text.x = element_text(size = 10),
    legend.position = "right",
    legend.box = "vertical"
  )
```

### Saving plot
```{r}
ggsave(
  paste0(fileLocManuscript, "/supplement/Figure5-SEAsia-DataOverview-Ananlysis/SEAsia_dataoverview.pdf"),
  plot_overview_seAsia_included,
  width = 8,
  height = 5,
  dpi = 700
)
ggsave(
  paste0(fileLocManuscript, "/supplement/Figure5-SEAsia-DataOverview-Ananlysis/SEAsia_dataoverview.png"),
  plot_overview_seAsia_included,
  width = 8,
  height = 5,
  dpi = 700
)
```

# Figure 6: Overview of data plot SE Asia (PfK7 data)
```{r}
plot_overview_seAsia_notincluded <- df_pfk7 %>% 
  filter(Locus != "other_PfK13", nobs <= numofobs) %>% 
  ggplot(aes(year, prev*100, group = Locus, color = Locus)) +
  geom_point(aes(size = n)) + 
  scale_size_binned(name = "Sample Size",range = c(0.2,3)) +
  labs(shape="Mutations", size = "Sample Size") +
  theme_bw() +
  facet_wrap(~country+District) +
  ylab("Prevalence") +
  xlab("Year") +
  ggpubr::theme_pubclean(base_size = 12) +
  scale_color_manual("Mutations",
    values = c("#56B4E9", "#E69F00", "#009E73"),
    labels = c("580Y", "PfK13", "539T")
  ) +
  theme(
    axis.line = element_line(),
    legend.title = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    legend.text = element_text(size = 10),
    strip.text.x = element_text(size = 10),
    legend.position = "right",
    legend.box = "vertical"
  )
```

### Saving plot
```{r}
ggsave(
  paste0(fileLocManuscript, "/supplement/Figure6-SEAsia-DataOverview-NotAnanlysis/SEAsia_dataoverview.pdf"),
  plot_overview_seAsia_notincluded,
  width = 8,
  height = 8.5,
  dpi = 700
)
ggsave(
  paste0(fileLocManuscript, "/supplement/Figure6-SEAsia-DataOverview-NotAnanlysis/SEAsia_dataoverview.png"),
  plot_overview_seAsia_notincluded,
  width = 8,
  height = 8.5,
  dpi = 700
)
```

# Figure 8: Plotting forecasting of predictions for the first 2, 3, and 4 years with confidence values
```{r}
prev_cutoff_perc <- 50
plot_colors <- c("#E69F00", "#56B4E9", "#0072B2")
count <- 0
for(y in c(2, 3, 4)){
  count <- count + 1
  col <- plot_colors[count]
  ################ PLOT FOR C580Y ################
  df_pred <- figure5_forecasting %>% 
    filter(year >= min_year + y, 
           Locus == "C580Y",
           pred_y == y) 
  df_true <- figure5_forecasting %>% 
    filter(year <= min_year + y, 
           Locus == "C580Y",
           pred_y == y) %>%
    mutate(label = "true")
  ex_pt <- figure5_pfk7_data %>% 
    filter(nobs > numofobs, 
           District %in% unique(df_pred$District), 
           Locus == "C580Y")
  
  ## PLOT FOR C580Y
  prev_cutoff_c580y_plot <- 
    ggplot() +
    geom_point(data = ex_pt, aes(x=year, y=prev*100, color = "true")) +
    geom_line(data = df_true, aes(year, predict_prev, color = "true")) + 
    geom_line(data = df_pred, aes(year, predict_prev, color = "forecasting")) +
    geom_ribbon(data = df_pred, aes(ymin = conf.low_prev, ymax = conf.high_prev, x = year, color = "forecasting", fill = "forecasting"), linetype = "dashed", alpha = 0.2,  show.legend = FALSE) +
    theme_bw() +
    facet_wrap(~District) +
    ylab("C580Y Prevalence") +
    xlab("Year") +
    scale_color_manual(
      values = c(col, "grey"),
      labels = c("Forecasting",  "True"),
      name = "") +
    scale_fill_manual(
      values = c(col, "grey"),
      labels = c("Forecasting",  "True"),
      name = "") +
    guides(col = FALSE, fill = FALSE) +  
    ggpubr::theme_pubclean(base_size = 8) +
    theme(
        axis.line = element_line(),
        axis.text = element_text(size = 6),
        axis.title = element_text(size = 8),
        strip.text.x = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.text = element_text(size = 6),
        legend.position = "right",
        panel.spacing = unit(0.45, "lines")
      )
  
  var_name <- paste0("prev_cutoff_c580y_plot_", y, "year")
  assign(var_name, prev_cutoff_c580y_plot)
  
  ################ PLOT FOR R539T ################
  df_pred <- figure5_forecasting %>% 
    filter(year >= min_year +  pred_y, 
           Locus == "R539T",
           pred_y == y)  
  df_true <- figure5_forecasting %>% 
    filter(year <= min_year + y, 
           Locus == "R539T",
           pred_y == y) %>%
    mutate(label = "true")
  ex_pt <- figure5_pfk7_data %>% 
    filter(nobs > numofobs, 
           District %in% unique(df_pred$District),
           Locus == "R539T")
  
  ## PLOT FOR R539T
  prev_cutoff_r539t_plot <- 
    ggplot() +
    geom_point(data = ex_pt, aes(x=year, y=prev*100, color = "true")) +
    geom_line(data = df_true, aes(year, predict_prev, color = "true")) + 
    geom_line(data = df_pred, aes(year, predict_prev, color = "forecasting")) +
    geom_ribbon(data = df_pred, aes(ymin = conf.low_prev, ymax = conf.high_prev, x = year, color = "forecasting", fill = "forecasting"), linetype = "dashed", alpha = 0.2,  show.legend = FALSE) +
    theme_bw() +
    facet_wrap(~District) +
    ylab("R539T Prevalence") +
    xlab("Year") +
    guides(col = FALSE, fill = FALSE) + 
    ggpubr::theme_pubclean(base_size = 8) +
    scale_color_manual(
      values = c(col, "grey"),
      labels = c("Forecasting",  "True"),
      name = "") +
    scale_fill_manual(
      values = c(col, "grey"),
      labels = c("Forecasting",  "True"),
      name = "") + 
    theme(
        axis.line = element_line(),
        axis.text = element_text(size = 6),
        axis.title = element_text(size = 8),
        strip.text.x = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.text = element_text(size = 6),
        legend.position = "right",
        panel.spacing = unit(0.45, "lines")
      )
  var_name <- paste0("prev_cutoff_r539t_plot_", y, "year")
  assign(var_name, prev_cutoff_r539t_plot)
  
  ################ PLOT FOR ALL KELCH ################
  df_pred <- figure5_forecasting %>% 
    filter(year >= min_year +  y, 
           Locus == "PfK13",
           pred_y == y)  
  df_true <- figure5_forecasting %>% 
    filter(year <= min_year + y, 
           Locus == "PfK13",
           pred_y == y) %>%
    mutate(label = "true")
  ex_pt <- figure5_pfk7_data %>% 
    filter(nobs > numofobs, 
           District %in% unique(df_pred$District), 
           Locus == "PfK13") 
  
  ## PLOT FOR PfK13
   prev_cutoff_all_kelch_plot <- ggplot() +
    geom_point(data = ex_pt, aes(x=year, y=prev*100, color = "true")) +
    geom_line(data = df_true, aes(year, predict_prev,  color = "true")) + 
    geom_line(data = df_pred, aes(year, predict_prev, color = "forecasting")) +
     geom_ribbon(data = df_pred, aes(ymin = conf.low_prev, ymax = conf.high_prev, x = year, color = "forecasting", fill = "forecasting"), linetype = "dashed", alpha = 0.2,  show.legend = FALSE) +
    theme_bw() +
    facet_wrap(~District) +
    ylab("Pfk13 Prevalence") +
    xlab("Year") +
    guides(col = FALSE, fill = FALSE) + 
    ggpubr::theme_pubclean(base_size = 8) +
    scale_color_manual(
      values = c(col, "grey"),
      labels = c("Forecasting",  "True"),
      name = "") +
    scale_fill_manual(
      values = c(col, "grey"),
      labels = c("Forecasting",  "True"),
      name = "") +
    theme(
        axis.line = element_line(),
        axis.text = element_text(size = 6),
        axis.title = element_text(size = 8),
        strip.text.x = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.text = element_text(size = 6),
        legend.position = "right",
        panel.spacing = unit(0.45, "lines")
    )
    var_name <- paste0("prev_cutoff_all_kelch_plot_", y, "year")
    assign(var_name, prev_cutoff_all_kelch_plot)
 }
```

##### Saving plots
```{r}
################ PLOT FOR C580Y ################
ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/C580Y/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_C580Y_2year_pred.png"
  ),
  prev_cutoff_c580y_plot_2year,
  width = 4.25,
  height = 3,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/C580Y/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_C580Y_2year_pred.pdf"
  ),
  prev_cutoff_c580y_plot_2year,
  width = 4.25,
  height = 3,
  dpi = 700
)

ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/C580Y/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_C580Y_3year_pred.png"
  ),
  prev_cutoff_c580y_plot_3year,
  width = 4.25,
  height = 3,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/C580Y/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_C580Y_3year_pred.pdf"
  ),
  prev_cutoff_c580y_plot_3year,
  width = 4.25,
  height = 3,
  dpi = 700
)

ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/C580Y/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_C580Y_4year_pred.png"
  ),
  prev_cutoff_c580y_plot_4year,
  width = 4.25,
  height = 3,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/C580Y/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_C580Y_4year_pred.pdf"
  ),
  prev_cutoff_c580y_plot_4year,
  width = 4.25,
  height = 3,
  dpi = 700
)

################ PLOT FOR R539T ################
ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/R539T/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_R539T_2year_pred.png"
  ),
  prev_cutoff_r539t_plot_2year,
  width = 4.25,
  height = 3,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/R539T/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_R539T_2year_pred.pdf"
  ),
  prev_cutoff_r539t_plot_2year,
  width = 4.25,
  height = 3,
  dpi = 700
)

ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/R539T/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_R539T_3year_pred.png"
  ),
  prev_cutoff_r539t_plot_3year,
  width = 4.25,
  height = 3,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/R539T/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_R539T_3year_pred.pdf"
  ),
  prev_cutoff_r539t_plot_3year,
  width = 4.25,
  height = 3,
  dpi = 700
)

ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/R539T/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_R539T_4year_pred.png"
  ),
  width = 4.25,
  height = 3,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/R539T/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_R539T_4year_pred.pdf"
  ),
  prev_cutoff_r539t_plot_4year,
  width = 4.25,
  height = 3,
  dpi = 700
)

################ PLOT FOR ALL KELCH ################
ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/PfK13/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_PfK13_2year_pred.png"
  ),
  prev_cutoff_all_kelch_plot_2year,
  width = 4.25,
  height = 3,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/PfK13/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_PfK13_2year_pred.pdf"
  ),
  prev_cutoff_all_kelch_plot_2year,
  width = 4.25,
  height = 3,
  dpi = 700
)

ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/PfK13/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_PfK13_3year_pred.png"
  ),
  prev_cutoff_all_kelch_plot_3year,
  width = 4.25,
  height = 3,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/PfK13/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_PfK13_3year_pred.pdf"
  ),
  prev_cutoff_all_kelch_plot_3year,
  width = 4.25,
  height = 3,
  dpi = 700
)

ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/PfK13/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_PfK13_4year_pred.png"
  ),
  prev_cutoff_all_kelch_plot_4year,
  width = 4.25,
  height = 3,
  dpi = 700
)
ggsave(
  paste0(
    "figures/supplement/Figure8-Forecasting/PfK13/SEAsia_cutoff_",
    prev_cutoff_perc,
    "prev_PfK13_4year_pred.pdf"
  ),
  prev_cutoff_all_kelch_plot_4year,
  width = 4.25,
  height = 3,
  dpi = 700
)
```

